### 2022-05-20 stabfreencvem.tex
initial

\documentclass[10pt]{amsart}
%\input{/Dropbox/Math/TexDocument/mysetting.tex}
%\input{mysetting.tex}

\usepackage{amssymb}
\usepackage[leqno]{amsmath}
\usepackage{mathrsfs}
\usepackage{stmaryrd}
\usepackage{chemarrow}
\usepackage[norelsize]{algorithm2e}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[pdftex,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=blue,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
%\usepackage[dvips,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=red,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[all]{xy}
\usepackage{tikz}
\usetikzlibrary{arrows}

\usepackage{multirow}
\usepackage[hyperpageref]{backref}

% comments
%\newcommand{\LC}[1]{\textcolor{cyan}{#1}}
\newcommand{\LC}[1]{\textcolor{red}{#1}}
\newcommand{\XH}[1]{\textcolor{red}{#1}}
%\usepackage[pdftex,colorlinks=true,citecolor=myBlue,linkcolor=myBlue]{hyperref}

  \newcounter{mnote}
  \setcounter{mnote}{0}
  \newcommand{\mnote}[1]{\addtocounter{mnote}{1}
    \ensuremath{{}^{\bullet\arabic{mnote}}}
    \marginpar{\footnotesize\em\color{red}\ensuremath{\bullet\arabic{mnote}}#1}}
  \let\oldmarginpar\marginpar
    \renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%
    {\raggedright\footnotesize #1}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{alg}[theorem]{Algorithm}

\newcommand{\dx}{\,{\rm d}x}
\newcommand{\dd}{\,{\rm d}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\mcal}{\mathcal}

\DeclareMathOperator*{\img}{img}
%\DeclareMathOperator*{\span}{span}
\newcommand{\curl}{\operatorname{curl}}
\renewcommand{\div}{\operatorname{div}}
%\renewcommand{\grad}{\operatorname{grad}}
\newcommand{\grad}{\operatorname{grad}}
\DeclareMathOperator*{\tr}{tr}
\DeclareMathOperator*{\rot}{rot}
\DeclareMathOperator*{\var}{Var}
\newcommand{\dev}{\operatorname{dev}}
\newcommand{\sym}{\operatorname{sym}}
\newcommand{\skw}{\operatorname{skw}}
\newcommand{\spn}{\operatorname{spn}}
\numberwithin{equation}{section}

\begin{document}
\title[Stabilization-Free Nonconforming VEM]{Stabilization-Free Nonconforming Virtual Element Method}
%\author{Long Chen}%
%\address{Department of Mathematics, University of California at Irvine, Irvine, CA 92697, USA}%
%\email{chenlong@math.uci.edu}%
% \author{Xuehai Huang}%
% \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
% \email{huang.xuehai@sufe.edu.cn}%

%\thanks{The first author was supported by.}
%\thanks{
%The first author was supported by the National Science Foundation (NSF) DMS-1418934, and
%in part by the Sea Poly Project of Beijing Overseas Talents and the National Natural Science Foundation of China Project 11671159.}
% \thanks{This work was supported by the National Natural Science Foundation of China Projects 12171300 and 11771338, the Natural Science Foundation of Shanghai 21ZR1480500, and the Fundamental Research Funds for the Central Universities 2019110066.}

% \subjclass[2010]{
% %65N55;   %% Multigrid methods; domain decomposition
% %65F10;   %%  Iterative methods for linear systems
% 65N30;   %%  Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods;
% 65N12;   %%  Stability and convergence of numerical methods;
% 65N22;   %%  Solution of discretized equations
% %65N15;   %%  Error bounds
% }

% \begin{abstract}
% \end{abstract}

% \keywords{Nonconforming finite element Stokes complex, quad-curl problem, error analysis, decoupling, fast solver}

\maketitle

\tableofcontents

\section{Preliminaries}

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. 
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$, where $\mathbb{K}$ is the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

For $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of $\boldsymbol x$ corresponding to vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit outward normal vector to $\partial F$.

Let $\{\mathcal {T}_h\}$ denote a family of partitions
of $\Omega$ into nonoverlapping simple polytopes with $h:=\max\limits_{K\in \mathcal {T}_h}h_K$
and $h_K:=\mbox{diam}(K)$.
Denote by $\mathcal F_h$ and $\mathcal F_h^i$ the set of all $(d-1)$-dimensional faces and interior $(d-1)$-dimensional faces of the partition $\mathcal T_h$.
Set $\mathcal F_h^{\partial}=\mathcal F_h\backslash\mathcal F_h^i$.
For any $F\in\mathcal{F}_h$,
let $h_F$ be its diameter and fix a unit normal vector $\boldsymbol{n}_F$.
For a piecewise smooth function $v$, define 
$$
\|v\|_{1,h}^2:=\sum_{K\in\mathcal T_h}\|v\|_{1,K}^2,\quad |v|_{1,h}^2:=\sum_{K\in\mathcal T_h}|v|_{1,K}^2.
$$

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For $F\in\mathcal F_h$ and smooth vector function $\boldsymbol{v}$, define surface divergence
$$
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
$$

\subsection{Mesh conditions}
We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
\begin{itemize}
 \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq n-1$ is star-shaped with a uniformly bounded chunkiness parameter.

 \item[(A2)] There exists a quasi-uniform simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
\end{itemize}

For $K\in \mathcal T_h$, let $\boldsymbol{x}_K$ be the center of  the largest ball contained in $K$.
Throughout this paper, we use
``$\lesssim\cdots $" to mean that ``$\leq C\cdots$", where
$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $n$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.

For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
$$
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
$$
Denote $
\mathcal{F}^i(\mathcal T_K):=\mathcal{F}(\mathcal T_K)\backslash\mathcal{F}^{\partial}(\mathcal T_K)$ and $\mathcal{E}^i(\mathcal T_K):=\mathcal{E}(\mathcal T_K)\backslash\mathcal{E}^{\partial}(\mathcal T_K).
$

%Note that (A1) and (A2) imply ${\rm diam}(F) \eqsim {\rm diam} (K)$ for all $F\in \mathcal F^r(K), 1\leq r\leq n-1$.
%For a star-shaped domain $D$,

\section{$H(\div)$-Conforming Macro Finite Element}

In this section we will construct $H(\div)$-conforming macro finite element in arbitrary dimension.
\subsection{$H(\div)$-conforming finite element}
For each polygon $K\in \mathcal T_h$ and $k\geq2$, let 
$$
\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
$$ 
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose DoFs are given by (cf. \cite{ChenHuang2021divdiv})
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
\end{align}
Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.

We also need the lowest order Raviart-Thomas (RT) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}
$$
\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
$$
Define $\mathring{\boldsymbol{V}}^{RT}(K):=\boldsymbol{V}^{RT}(K)\cap \boldsymbol{H}_0(\div, K)$.

\subsection{Finite element for differential $(d-2)$-form}
Now recall the finite element for differential $(d-2)$-form, i.e. $H\Lambda^{d-2}$-conforming finite element in \cite{ArnoldFalkWinther2006,Arnold2018}. We will present the finite element for differential $(d-2)$-form using the proxy of the differential form rather than the differential form itself as in \cite{ArnoldFalkWinther2006,Arnold2018}.

By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}

\begin{lemma}\label{lem:skwgrad}
For $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ satisfying $(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\boldsymbol{0}$, it holds $\boldsymbol{w}=\boldsymbol{0}$.
\end{lemma}
\begin{proof}
Since
\begin{equation*}%\label{eq:20220224}  
(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\frac{1}{2}(\nabla\boldsymbol{w})\boldsymbol{x}-\frac{1}{2}(\nabla\boldsymbol{w})^{\intercal}\boldsymbol{x}=\frac{1}{2}\nabla(\boldsymbol{w}\cdot\boldsymbol{x})-\frac{1}{2}(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w},
\end{equation*}
we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which implies $\boldsymbol{w}=\boldsymbol{0}$.
\end{proof}

\begin{lemma}
The polynomial complex
\begin{equation}\label{eq:polycomplex1}
\mathbb R\xrightarrow{}\mathbb P_k(T)\xrightarrow{\nabla}\mathbb P_{k-1}(T;\mathbb R^d)\xrightarrow{\skw\nabla}\mathbb P_{k-2}(T;\mathbb K)
\end{equation}
is exact.
\end{lemma}
\begin{proof}
Clearly \eqref{eq:polycomplex1} is a complex. It suffices to prove $\mathbb P_{k-1}(T;\mathbb R^d)\cap\ker(\skw\nabla)\subseteq\nabla\mathbb P_{k}(T)$.

For $\boldsymbol{v}\in\mathbb P_{k-1}(T;\mathbb R^d)\cap\ker(\skw\nabla)$, by decomposition \eqref{eq:Pkvectordecomp}, there exist $q\in \mathbb P_k(T)$ and $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ such that $\boldsymbol{v}=\nabla q+\boldsymbol{w}$. 
By $\skw\nabla\boldsymbol{v}=\boldsymbol{0}$, we get $\skw\nabla\boldsymbol{w}=\boldsymbol{0}$. 
Apply Lemma~\ref{lem:skwgrad} to derive $\boldsymbol{w}=\boldsymbol{0}$. Thus $\boldsymbol{v}=\nabla q\in\nabla\mathbb P_k(T)$.
\end{proof}

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T,\mathbb K)\cap\ker(\boldsymbol{x})\big).
\end{equation}
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
$$
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
$$
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T,\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
$$
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
$$
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

% \begin{lemma}
% The polynomial complex
% \begin{equation}\label{eq:polycomplex2}
% \mathbb P_{k-2}(K;\mathbb K)\xrightarrow{\boldsymbol{\tau}\boldsymbol{x}}\mathbb P_{k-1}(K;\mathbb R^d) \xrightarrow{\boldsymbol{v}\cdot\boldsymbol{x}} \mathbb P_k(K)\xrightarrow{\pi_0}\mathbb R
% \end{equation}
% is exact, where $\pi_0q=q(0)$.
% \end{lemma}
% \begin{proof}
% Clearly \eqref{eq:polycomplex2} is a complex, and $\mathbb P_{k-1}(K;\mathbb R^d)\cdot\boldsymbol{x}=\mathbb P_k(K)\cap\ker(\pi_0)$. It suffices to prove $\mathbb P_{k-1}(K;\mathbb R^d)\cap\ker(\cdot\boldsymbol{x})\subseteq\mathbb P_{k-2}(K;\mathbb K)\boldsymbol{x}$.
% \end{proof}

 By \eqref{eq:Pkskwtensordecomp} and \eqref{eq:20220324-1}, it follows
\begin{equation}\label{eq:20220324-2}
\dim\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})=\dim\mathbb P_{k-2}(T;\mathbb K)+\dim\nabla\mathbb P_k(T)- \dim\mathbb P_{k-1}(T;\mathbb R^d).
\end{equation}

With the decomposition \eqref{eq:Pkskwtensordecomp} and $\mathbb P_{k-1}(F;\mathbb R^{d-1})=\nabla_FP_k(F)\oplus\mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}$, we are ready to define the finite element for differential $(d-2)$-form. Take $\mathbb P_k(T;\mathbb K)$ as the space of shape functions. The degrees of freedom are given by
\begin{align}
((\boldsymbol{n}_1^e)^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_2^e, q)_e, & \quad q\in \mathbb P_k(e), e\in\mathcal E(T), \label{eq:-2formfemdof1} \\
(\div_F(\boldsymbol{\tau}\boldsymbol{n}), q)_F, & \quad q\in \mathbb P_{k-1}(F)/\mathbb R, F\in\mathcal F(T), \label{eq:-2formfemdof21} \\
(\boldsymbol{\tau}\boldsymbol{n}, \boldsymbol{q})_F, & \quad \boldsymbol{q}\in \mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}, F\in\mathcal F(T), \label{eq:-2formfemdof22} \\
(\div\boldsymbol{\tau}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}, \label{eq:-2formfemdof31} \\
(\boldsymbol{\tau}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x}). \label{eq:-2formfemdof32}
\end{align}
In DoF \eqref{eq:-2formfemdof1}, $\boldsymbol{n}_1^e$ and  $\boldsymbol{n}_2^e$ are two unit normal vectors of $e$ satisfying $\boldsymbol{n}_1^e\cdot\boldsymbol{n}_2^e=0$. 
\begin{lemma}\label{lem:normalskwtensor}
For $e\in\mathcal E(T)$, let $\tilde{\boldsymbol{n}}_1$ and  $\tilde{\boldsymbol{n}}_2$ be another two unit normal vectors of $e$ satisfying $\tilde{\boldsymbol{n}}_1\cdot\tilde{\boldsymbol{n}}_2=0$. Then
$$
\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=\pm\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}).
$$
\end{lemma}
\begin{proof}
Notice that there exists an orthonormal matrix $H\in\mathbb R^{2\times2}$ such that 
$(\tilde{\boldsymbol{n}}_1, \tilde{\boldsymbol{n}}_2)=(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)H$.
Then
\begin{align*}
2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})&=\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal}-\tilde{\boldsymbol{n}}_2\tilde{\boldsymbol{n}}_1^{\intercal}=(\tilde{\boldsymbol{n}}_1, \tilde{\boldsymbol{n}}_2)\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}\begin{pmatrix}
\tilde{\boldsymbol{n}}_1^{\intercal} \\
\tilde{\boldsymbol{n}}_2^{\intercal}  
\end{pmatrix}
\\
&=(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)H\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}H^{\intercal}(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)^{\intercal}.
\end{align*}
By direct computation, $H\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}H^{\intercal}={\rm det}(H)\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}$. Hence
$$
2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=2{\rm det}(H)\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}),
$$
which ends the proof.
\end{proof}

\begin{lemma}\label{lem:-2formfemfaceunisolvence}
Let $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$ and $F\in\mathcal F(T)$.
Assume the degrees of freedom \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof22} on $F$ vanish. 
Then $\boldsymbol{\tau}\boldsymbol{n}|_F=\boldsymbol{0}$.
\end{lemma}
\begin{proof}
Due to \eqref{eq:-2formfemdof1},  we get $(\boldsymbol{n}_1^e)^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_2^e|_e=0$ on each $e\in\mathcal E(F)$, which together with Lemma~\ref{lem:normalskwtensor} indicates $\boldsymbol{n}_{F,e}^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_F|_e=0$. By the unisolvence of BDM element on face $F$, cf. DoFs \eqref{BDMdof1}-\eqref{BDMdof3}, it follows from DoFs \eqref{eq:-2formfemdof21}-\eqref{eq:-2formfemdof22} that $\boldsymbol{\tau}\boldsymbol{n}|_F=\boldsymbol{0}$.
\end{proof}

\begin{lemma}\label{lem:PkKbubblecharac}
For $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$, $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$, if and only if 
\begin{equation}\label{eq:PkKbubblecharac}
\boldsymbol{\tau}=\sum_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
\end{equation}
for some $q_{ij}\in\mathbb P_{k-2}(T)$. Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ is the basis of $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
$$
\boldsymbol{N}_{ij}:\skw({\boldsymbol n_l\boldsymbol n_m^{\intercal}})=\delta_{il}\delta_{jm},\quad 1\leq i<j\leq d,\; 1\leq l<m\leq d.
$$
\end{lemma}
\begin{proof}
For $1\leq l\leq d$ but $l\neq i, j$, by the definition of $\boldsymbol{N}_{ij}$, it holds $\boldsymbol{N}_{ij}\boldsymbol{n}_l=\boldsymbol{0}$. Hence for $
\boldsymbol{\tau}=\sum\limits_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
$, obviously we have $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$.

On the other side, assume $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$. Express $\boldsymbol{\tau}$ as 
$$
\boldsymbol{\tau}=\sum_{1\leq i<j\leq d}p_{ij}\boldsymbol{N}_{ij},
$$
where $p_{ij}=\boldsymbol{n}_i^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_j\in\mathbb P_{k}(T)$.
Therefore $p_{ij}|_{F_i}=p_{ij}|_{F_j}=0$, which ends the proof.
\end{proof}

\begin{lemma}
The degrees of freedom \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32} are uni-solvent for $\mathbb P_k(T;\mathbb K)$.
\end{lemma}
\begin{proof}
By $\mathbb P_{k-1}(F;\mathbb R^{d-1})=\nabla_FP_k(F)\oplus\mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}$,
the number of degrees of freedom \eqref{eq:-2formfemdof21}-\eqref{eq:-2formfemdof22} is
$
(d^2+d){k+d-2\choose k-1} - (d+1){k+d-1\choose k}.
$
Using \eqref{eq:Pkvectordecomp} and \eqref{eq:20220324-2},
the number of degrees of freedom \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32} is
\begin{align*}
&\frac{1}{2}(d^2+d){k+d-2\choose k} + (d^2+d){k+d-2\choose k-1} - (d+1){k+d-1\choose k} \\
&+ \frac{1}{2}(d^2+d){k+d-2\choose k-2}+{k+d\choose k}-(d+1){k+d-1\choose k-1} =\frac{1}{2}(d^2-d){k+d\choose k},
\end{align*}
which equals to $\dim\mathbb P_k(T;\mathbb K)$.

Assume $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$ and all the degrees of freedom \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32} vanish. 
It holds from Lemma~\ref{lem:-2formfemfaceunisolvence} that $\boldsymbol{\tau}\boldsymbol{n}|_{\partial T}=\boldsymbol{0}$. Noting that $\boldsymbol{\tau}$ is antisymmetric,  we also have $\boldsymbol{n}^{\intercal}\boldsymbol{\tau}|_{\partial T}=\boldsymbol{0}$. On each $F\in\mathcal F(T)$, it holds
\begin{equation}\label{eq:20220324-3}
\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}=\div(\boldsymbol{n}^{\intercal}\boldsymbol{\tau})= \div_F(\boldsymbol{n}^{\intercal}\boldsymbol{\tau})+\partial_n(\boldsymbol{n}^{\intercal}\boldsymbol{\tau}\boldsymbol{n})=\div_F(\boldsymbol{n}^{\intercal}\boldsymbol{\tau}).
\end{equation}
Hence $\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}|_{\partial T}=0$. 
Thanks to DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element, we acquire from DoF \eqref{eq:-2formfemdof31} that $\div\boldsymbol{\tau}=\boldsymbol{0}$, which together with DoF \eqref{eq:-2formfemdof32} and decomposition \eqref{eq:Pkskwtensordecomp} gives
$$
(\boldsymbol{\tau}, \boldsymbol{q})_T=0  \quad \forall~\boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K).
$$
Applying Lemma~\ref{lem:PkKbubblecharac}, $\boldsymbol{\tau}$ has the expression as in \eqref{eq:PkKbubblecharac}. Taking $\boldsymbol{q}=q_{ij}\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})$ in the last equation for $1\leq i<j\leq d$, we get $q_{ij}=0$. Thus $\boldsymbol{\tau}=\boldsymbol{0}$.
\end{proof}

For polygon $K\in \mathcal T_h$, define local finite element space for differential $(d-2)$-form  
\begin{align*}  
\boldsymbol{V}_{k}^{d-2}(K):=\{\boldsymbol{\tau}\in\bs L^2(K;\mathbb K)&: \boldsymbol{\tau}|_{T}\in \mathbb P_{k}(T;\mathbb K) \textrm{ for each } T\in\mathcal T_K, \\
&\;\;\textrm{ all the DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof22} are single-valued}\}.
\end{align*}
Thanks to Lemma~\ref{lem:-2formfemfaceunisolvence}, space $\boldsymbol{V}_{k}^{d-2}(K)$ is $H\Lambda^{d-2}$-conforming.
Define $\mathring{\boldsymbol{V}}_{k}^{d-2}(K):=\boldsymbol{V}_{k}^{d-2}(K)\cap \mathring{H}\Lambda^{d-2}(K)$, where $\mathring{H}\Lambda^{d-2}(K)$ is the subspace of $H\Lambda^{d-2}(K)$ with homogeneous boundary condition.
Notice that
 $\boldsymbol{V}_{k}^{d-2}(K)$ is the Lagrange element space for $d=2$,
and $\boldsymbol{V}_{k}^{d-2}(K)$ is the second kind N\'ed\'elec element space for $d=3$ \cite{Nedelec:1986family}.

% To figure out degrees of freedom for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$,
Recall the local finite element de Rham complexes in \cite{ArnoldFalkWinther2006,Arnold2018}.
For completeness, we will prove the exactness of these complexes.

\begin{lemma}
Let $k\geq2$. Finite element complexes
\begin{equation}\label{eq:localBDMfemderhamcomplex}
\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{BDM}(K)\xrightarrow{\div} V_{k-2}^{L^2}(K)\to0,    
\end{equation}
\begin{equation}\label{eq:localRTfemderhamcomplex}
\boldsymbol{V}_{1}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}^{RT}(K)\xrightarrow{\div} V_{0}^{L^2}(K)\to0,    
\end{equation}
\begin{equation}\label{eq:localBDMfemderhamcomplex0}
\mathring{\boldsymbol{V}}_{k}^{d-2}(K)\xrightarrow{\div\skw}\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)\xrightarrow{\div} \mathring{V}_{k-2}^{L^2}(K)\to0,    
\end{equation}
\begin{equation}\label{eq:localRTfemderhamcomplex0}
\mathring{\boldsymbol{V}}_{1}^{d-2}(K)\xrightarrow{\div\skw}\mathring{\boldsymbol{V}}^{RT}(K)\xrightarrow{\div} \mathring{V}_{0}^{L^2}(K)\to0,    
\end{equation}
are exact, where $\mathring{V}_{k-2}^{L^2}(K):=V_{k-2}^{L^2}(K)/\mathbb R$, and
$$
V_{k-2}^{L^2}(K):=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for each } T\in\mathcal T_K\}.
$$
\end{lemma}
\begin{proof}
We only prove complex \eqref{eq:localBDMfemderhamcomplex}, since the argument for the rest complexes is similar. Clearly \eqref{eq:localBDMfemderhamcomplex} is a complex. We refer to \cite[Section 4]{ChenHuang2021divX} for the proof of $\div\boldsymbol{V}_{k-1}^{BDM}(K)=V_{k-2}^{L^2}(K)$.

Next prove $\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)=\div\skw\boldsymbol{V}_{k}^{d-2}(K)$. For $\boldsymbol{v}\in\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$, by Theorem 1.1 in \cite{CostabelMcIntosh2010}, there exists $\boldsymbol{\tau}\in\boldsymbol{H}^1(K;\mathbb K)$ satisfying $\div\boldsymbol{\tau}=\div\skw\boldsymbol{\tau}=\boldsymbol{v}$. Let $\boldsymbol{\sigma}\in \boldsymbol{V}_{k}^{d-2}(K)$ be the nodal interpolation of $\boldsymbol{\tau}$ based on DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32}. Thanks to DoF \eqref{eq:-2formfemdof1}, it follows from the integration by parts that
$$
(\div_F(\boldsymbol{\sigma}\boldsymbol{n}), 1)_F=(\boldsymbol{v}, 1)_F\quad\forall~F\in\mathcal F(\mathcal T_K),
$$
which together with \eqref{eq:20220324-3} and DoF \eqref{eq:-2formfemdof21} that
$$
(\boldsymbol{n}^{\intercal}\div\boldsymbol{\sigma}, q)_F = (\div_F(\boldsymbol{\sigma}\boldsymbol{n}), q)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F\quad\forall~q\in \mathbb P_{k-1}(F),F\in\mathcal F(\mathcal T_K).
$$
Therefore, due to DoF \eqref{eq:-2formfemdof31} and the fact $\div\div\boldsymbol{\sigma}=\div\boldsymbol{v}=0$,
we acquire from the unisolvence of DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element that $\boldsymbol{v}=\div\boldsymbol{\sigma} \in \div\skw\boldsymbol{V}_{k}^{d-2}(K)$.
\end{proof}

Note that $\div\skw=\curl$ for $d=2,3$.
For $k\geq1$, by finite element complexes \eqref{eq:localBDMfemderhamcomplex}-\eqref{eq:localRTfemderhamcomplex0}, we have
\begin{equation}\label{eq:20220324-4}
\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)-1.
\end{equation}
% \begin{align*}  
% \dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F(\mathcal T_K)+ \left(d{k+d-2\choose d}-{k+d-1\choose d}\right)\#\mathcal T_K, \\
% \dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^i(\mathcal T_K)+ \left(d{k+d-2\choose d}-{k+d-1\choose d}\right)\#\mathcal T_K+1,
% \end{align*}

\subsection{$H(\div)$-conforming macro finite element}
For each polygon $K\in \mathcal T_h$, 
define shape function space
$$
\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
$$
for $k\geq 2$, and $$
\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{RT}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
$$
Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{RT}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$ for $k\geq2$.

In the following lemma we present a direct sum decomposition of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.

\begin{lemma}
For $k\geq1$,
it holds
\begin{equation}\label{eq:Vdivlocaldecomp}
\boldsymbol{V}_{k-1}^{\rm div}(K)=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
\end{equation}
Then the complex
\begin{equation*}
\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
\end{equation*}
is exact.
\end{lemma}
\begin{proof}
We only prove the case $k\geq2$, as the proof for case $k=1$ is similar.
Since $\div:(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\to\mathbb P_{k-2}(K)$ is bijective \cite[Lemma 3.1]{ChenHuang2021divdiv}, we have $\div\skw \boldsymbol{V}_{k}^{d-2}(K)\cap(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)=\{\boldsymbol{0}\}$. Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \boldsymbol{V}_{k-1}^{\rm div}(K)$.

On the other side, for $\boldsymbol{\phi}\in \boldsymbol{V}_{k-1}^{\rm div}(K)$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e. $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$. Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$. Thus \eqref{eq:Vdivlocaldecomp} follows.
\end{proof}

Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \label{Vdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
    (\boldsymbol{\phi}, \bs q)_K & \quad\forall~\bs q\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)=\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vdivdof3}
\end{align}
% where $\mathring{\boldsymbol{V}}_{k-1}^{\rm div}(K):=\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\boldsymbol{H}_0(\div, K)$.
% where $\mathcal E^{\partial}(\mathcal T_K):=\{e\in\mathcal E(\mathcal T_K): e\subset\partial K\}$.
% DoF \eqref{Vdivdof3} will disappear when $\mathcal T_K=\{K\}$ is a simplex.
\begin{lemma}
The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
\end{lemma}
\begin{proof}
By \eqref{eq:20220324-4} and \eqref{eq:Vdivlocaldecomp},
the number of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is
\begin{align*}
&\quad {k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\boldsymbol{V}_{k-1}^{\rm div}(K).
\end{align*}
% By \eqref{eq:Vdivlocaldecomp},
% the number of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} equals to $\dim\boldsymbol{V}_{k-1}^{\rm div}(K)$.

Assume $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish. By the vanishing DoF~\eqref{Vdivdof1}, $\boldsymbol{\phi}\in \boldsymbol{H}_0(\div, K)$ and $\div\boldsymbol{\phi}\in L_0^2(K)$. Then it follows from the vanishing DoF~\eqref{Vdivdof2} that $\div\boldsymbol{\phi}=0$. 
Thanks to the exactness of complexes \eqref{eq:localBDMfemderhamcomplex0}-\eqref{eq:localRTfemderhamcomplex0}, $\boldsymbol{\phi}\in\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$. Therefore $\boldsymbol{\phi}=\boldsymbol{0}$ holds from the vanishing DoF~\eqref{Vdivdof3}.
\end{proof}

\begin{remark}\rm
When $K$ is a simplex and $\mathcal T_K=\{K\}$, thanks to DoF \eqref{BDMdof3} for the BDM element, DoF \eqref{Vdivdof3} can be replaced by 
$$
(\boldsymbol{\phi}, \bs q)_K \quad\forall~\bs q\in \mathbb P_{k-3}(K;\mathbb K)\boldsymbol{x}
$$
for $k\geq3$.
And DoF \eqref{Vdivdof3} disappears for $k=1$ and $k=2$.
\end{remark}

% \begin{lemma}
% For $p\in V_{1}^{\grad}(K)$, it holds
% \begin{equation}\label{eq:V1gradKprop}
% \|\curl p\|_{0,K}\lesssim \sup_{w\in\mathring{V}_{1}^{\grad}(K)}\frac{(\curl p, \curl w)_K}{\|\curl w\|_{0,K}} +\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|(\curl p)\cdot\boldsymbol{n}\|_{0,e}.
% \end{equation}
% \end{lemma}
% \begin{proof}
% Take a vertex $\delta_0\in\mathcal V^{\partial}(\mathcal T_K)$. Without loss of generality, assume $p(\delta_0)=0$. Let $\tilde p\in V_{1}^{\grad}(K)$ satisfy $\tilde p|_{\partial K}=p|_{\partial K}$ and $\tilde p(\delta)=0$ for all $\delta\in\mathcal V^{i}(\mathcal T_K)$. Then $p-\tilde p\in\mathring{V}_{1}^{\grad}(K)$, and
% \begin{align*}
% \|\curl (p-\tilde p)\|_{0,K}&= \sup_{w\in\mathring{V}_{1}^{\grad}(K)}\frac{(\curl(p-\tilde p), \curl w)_K}{\|\curl w\|_{0,K}} \\
% &\lesssim \|\curl\tilde p\|_{0,K}+\sup_{w\in\mathring{V}_{1}^{\grad}(K)}\frac{(\curl p, \curl w)_K}{\|\curl w\|_{0,K}}.
% \end{align*}
% By the triangle inequality, the last inequality implies
% \begin{equation}\label{eq:20220203}
% \|\curl p\|_{0,K}\lesssim \|\curl\tilde p\|_{0,K}+\sup_{w\in\mathring{V}_{1}^{\grad}(K)}\frac{(\curl p, \curl w)_K}{\|\curl w\|_{0,K}}.
% \end{equation}

% On the other side, applying the inverse inequality and the scaling argument,
% \begin{align*}
% \|\curl\tilde p\|_{0,K}^2&\lesssim \sum_{\tau\in\mathcal T_K}h_{\tau}^{-2}\|\tilde p\|_{0,\tau}^2\eqsim \sum_{\delta\in\mathcal V^{\partial}(\mathcal T_K)} \tilde p^2(\delta)=\sum_{\delta\in\mathcal V^{\partial}(\mathcal T_K)} (p(\delta)-p(\delta_0))^2 \\
% &\lesssim \sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e\|(\curl p)\cdot\boldsymbol{n}\|_{0,e}^2.
% \end{align*}
% Therefore \eqref{eq:V1gradKprop} follows from \eqref{eq:20220203} and the last inequality.
% \end{proof}

Next we consider the norm equivalence of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.

\begin{lemma}
For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
\begin{equation}\label{eq:Vkm1divnormequivalence}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
\end{lemma}
\begin{proof}
By the inverse inequality \cite[Lemma 10]{Huang2020} and the trace inequality \cite[(2.18)]{BrennerSung2018}, we have
\begin{align*}
&\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
&\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
\end{align*}

Next we focus on the proof of the other side. Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$. Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{BDM}(K)$ such that $\boldsymbol{\phi}_1\cdot\boldsymbol{n}|_{\partial K}=\boldsymbol{\phi}\cdot\boldsymbol{n}_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ in the interior of $K$ vanish. We have
\begin{equation}\label{eq:20220324-5}
\|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
\end{equation}
$$
\|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\quad\forall~T\in\mathcal T_K.
$$
Then let $w\in H^1(K)/\mathbb R$ be the solution of 
$$
\begin{cases}
-\Delta w= \div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\quad\textrm{ in } K, \\
\;\;\partial_nw=0\qquad\qquad\quad\;\;\,\textrm{ on } \partial K.
\end{cases}
$$
The weak formulation is
$$
(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)/\mathbb R.
$$
Obviously we have
$$
\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
$$
Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}. Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$. We have
\begin{equation}\label{eq:20220324-6}
\div\boldsymbol{\phi}_2=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1),
\end{equation}
\begin{equation}\label{eq:20220324-7}
\|\boldsymbol{\phi}_2\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$. Hence
\begin{align*}  
\|\boldsymbol{\phi}\|_{0,K}&\lesssim \|\boldsymbol{\phi}_1\|_{0,K}+\|\boldsymbol{\phi}_2\|_{0,K}+\|\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\|_{0,K} \\
&\lesssim \|\boldsymbol{\phi}_1\|_{0,K}+\|\boldsymbol{\phi}_2\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} \\
&\lesssim \|\boldsymbol{\phi}_1\|_{0,K}+\|\boldsymbol{\phi}_2\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}}.
\end{align*}
Finally \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.
\end{proof}

\section{Stabilization free virtual element method}

In this section we will develop a stabilization free virtual element method for the second order elliptic problem
\begin{equation}\label{eq:ellipitc2ndproblem}
\begin{cases}
-\Delta u + \alpha u=f & \textrm{ in } \Omega,\\
\qquad\qquad u=0&\textrm{ on } \partial\Omega,
\end{cases}
\end{equation}
where $\Omega\subseteq\mathbb R^d$ is a bounded polygon, $f\in L^2(\Omega)$ and $\alpha$ is a positive constant. The weak formulation of problem \eqref{eq:ellipitc2ndproblem} is to find $u\in H_0^1(\Omega)$ such that
\begin{equation}\label{eq:ellipitc2ndproblemweakform}
a(u,v)=(f,v)\quad\forall~v\in H_0^1(\Omega),
\end{equation}
where the bilinear form $a(u, v):=(\nabla_h u, \nabla_h v)+\alpha(u,v)$ with $\nabla_h$ being the piecewise counterpart of $\nabla$ with respect to $\mathcal T_h$.

% In this section we will construct an $H(\div)$-conforming macro finite element, and then establish a norm equivalence of the gradient of the $H^1$-conforming virtual element space, which is vital in devising a stabilization free virtual element method.

\subsection{$H^1$-nonconforming virtual element}

Recall the $H^1$-nonconforming virtual element in \cite{ChenHuang2020ncvem,Huang2020,AyusodeDiosLipnikovManzini2016}.
The degrees of freedom are given by
\begin{align}
\frac{1}{|F|}(v, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
\frac{1}{|K|}(v, q)_K & \quad\forall~q\in\mathbb P_{k-2}(K). \label{eq:vemdof2}
\end{align}

To define the space of shape functions, we need a local $H^1$ projection operator $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be the solution of the problem %\mnote{ define $Q_0^F$}
\begin{align}
(\nabla\Pi_k^Kv, \nabla q)_K&=(\nabla v, \nabla q)_K\quad  \forall~q\in \mathbb P_k(K), \label{eq:projlocal2d1}\\
\int_{\partial K}\Pi_k^Kv\,{\rm d}s&=\int_{\partial K}v\,{\rm d}s. \label{eq:projlocal2d2}
% \sum_{F\in\mathcal F(K)}Q_0^F(\Pi_k^Kv)&=\sum_{F\in\mathcal F(K)}Q_0^Fv.\label{eq:projlocal2d2}
\end{align}
It holds
\begin{equation}\label{eq:localproj2dprop1}
\Pi_k^Kq=q \quad\forall~q\in\mathbb P_k(K).    
\end{equation}

With the help of operator $\Pi_k^K$, the space of shape functions is defined as
\begin{align*}
V_k(K):=\{v\in H^1(K) &: \Delta v\in\mathbb P_{k}(K),\, \partial_nv|_F\in\mathbb P_{k-1}(F)\textrm{ for each face }F\in\mathcal F(K), \\
&\qquad\qquad\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
\end{align*}
where $\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
Due to \eqref{eq:localproj2dprop1}, it holds $\mathbb P_k(K)\subseteq V_k(K)$.
DoFs~\eqref{eq:vemdof1}-\eqref{eq:vemdof2} are uni-solvent for the shape function space $V_k(K)$.

For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using only DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, and the $L^2$ projection
\begin{equation}\label{eq:QKPik}  
Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv
\end{equation}
is also computable using only DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}.

We will prove the inverse inequality and the norm equivalence for the virtual element space $V_k(K)$.
\begin{lemma}\label{lem:veminverse}
It holds the inverse inequality
\begin{equation}\label{eq:veminverse}
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}\quad\forall~v\in V_k(K).  
\end{equation}
\end{lemma}
\begin{proof}
Apply the integration by parts to get
$$
|v|_{1,K}^2=-(\Delta v,v)_K+(\partial_nv,v)_{\partial K}\leq\|\Delta v\|_{0,K}\|v\|_{0,K}+\|\partial_nv\|_{0,\partial K}\|v\|_{0,\partial K}.
$$
By $h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}$, i.e. (A.3)-(A.4) in \cite{ChenHuang2020ncvem}, we obtain
$$
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
$$
which together with the multiplicative trace inequality yields \eqref{eq:veminverse}.
\end{proof}

\begin{lemma}
For $v\in V_k(K)$, we have
\begin{align}
\|\Pi_k^Kv\|_{0,K}^2+h_K^2|\Pi_k^Kv|_{1,K}^2&\lesssim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2, \label{eq:VEMnormequivalencePiK}\\
\|Q_k^Kv\|_{0,K}^2&\lesssim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2. \label{eq:VEMnormequivalenceQK}
\end{align}
\end{lemma}
\begin{proof}
We get from \eqref{eq:projlocal2d1} and the integration by parts that
\begin{align*}
|\Pi_k^Kv|_{1,K}^2&=(\nabla v, \nabla\Pi_k^Kv)_K=-(v, \Delta\Pi_k^Kv)_K+(v, \partial_n(\Pi_k^Kv))_{\partial K} \\
&=-(Q_{k-2}^Kv, \Delta\Pi_k^Kv)_K+\sum_{F\in\mathcal F(K)}(Q_{k-1}^Fv, \partial_n(\Pi_k^Kv))_{F} \\
&\leq\|Q_{k-2}^Kv\|_{0,K}\|\Delta\Pi_k^Kv\|_{0,K}+\sum_{F\in\mathcal F(K)}\|Q_{k-1}^Fv\|_{0,F}\|\partial_n(\Pi_k^Kv)\|_{0,F},
\end{align*}
which combined with the inverse inequality for polynomials implies
$$%\label{eq:VEMnormequivalencePiK}
h_K^2|\Pi_k^Kv|_{1,K}^2\lesssim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2. 
$$
Thanks to the Poincar\'e-Friedrichs inequality \cite[(2.15)]{BrennerSung2018} and \eqref{eq:projlocal2d2},
\begin{align*}  
\|\Pi_k^Kv\|_{0,K}^2&\lesssim h_K|\Pi_k^Kv|_{1,K}^2+h_K^{2-d}\left|\int_{\partial K}v\,{\rm d}s\right|^2 \\
&=h_K^2|\Pi_k^Kv|_{1,K}^2+h_K^{2-d}\left|\sum_{F\in\mathcal F(K)}\int_{F}Q_{0}^Fv\,{\rm d}s\right|^2 \\
&\lesssim h_K^2|\Pi_k^Kv|_{1,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{0}^Fv\|_{0,F}^2.
\end{align*}
Hence \eqref{eq:VEMnormequivalencePiK} follows from the last two inequalities.

Finally \eqref{eq:VEMnormequivalenceQK} holds from \eqref{eq:QKPik} and \eqref{eq:VEMnormequivalencePiK}.
\end{proof}

\begin{lemma}
It holds the norm equivalence
\begin{equation}\label{eq:Vknormequivalence}
h_K^2|v|_{1,K}^2\lesssim\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2 \quad\forall~v\in V_k(K).
\end{equation}  
\end{lemma}
\begin{proof}
Since $\Delta v\in\mathbb P_{k}(K)$ and $\partial_nv|_F\in\mathbb P_{k-1}(F)$, we get from the integration by parts that
\begin{align*}
|v|_{1,K}^2&=-(\Delta v,Q_k^Kv)_K+\sum_{F\in\mathcal F(K)}(\partial_nv,Q_{k-1}^Fv)_{F} \\
&\leq\|\Delta v\|_{0,K}\|Q_k^Kv\|_{0,K}+\sum_{F\in\mathcal F(K)}\|\partial_nv\|_{0,F}\|Q_{k-1}^Fv\|_{0,F}.
\end{align*}
Applying the similar argument as in Lemma \ref{lem:veminverse}, we obtain
$$
h_K^2|v|_{1,K}^2\lesssim \|Q_k^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2.
$$
Then it follows from \eqref{eq:VEMnormequivalenceQK} that
$$
\|v\|_{0,K}^2\lesssim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2.
$$
The other side $\|Q_{k-2}^Kv\|_{0,K}^2+\sum\limits_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2\lesssim \|v\|_{0,K}^2$ holds from the trace inequality and the inverse inequality \eqref{eq:veminverse}.
\end{proof}

\subsection{Local inf-sup condition and norm equivalence}
With the help of the macro element space $\boldsymbol{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$. Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\boldsymbol{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
\begin{lemma}
It holds the inf-sup condition
\begin{equation}\label{eq:localdiscreteinfsup}    
\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
\end{equation}
Consequently
\begin{equation}\label{eq:gradVknormequivalence}  
\|Q_K^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
\end{equation}
\end{lemma}
\begin{proof}
Clearly the norm equivalence \eqref{eq:gradVknormequivalence} follows from the local inf-sup condition~\eqref{eq:localdiscreteinfsup}. We will focus on the proof of \eqref{eq:localdiscreteinfsup}.
Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
Based on DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3}, take $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ such that
\begin{align*}
(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F&=h_K^{-1}(v, q)_F  \quad\quad\,\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \\
(\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \\
(\boldsymbol{\phi}, \bs q)_K&=0  \qquad\qquad\qquad\forall~\bs q\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K). 
\end{align*}
Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F^{\partial}(\mathcal T_K)$. By $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$. Apply the integration by parts to get
\begin{align*}
(\boldsymbol{\phi}, \nabla v)_K&=-(\div\boldsymbol{\phi}, v)_K + (\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K} \\
&=-(\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi}), v)_K+\sum_{F\in\mathcal F(K)}(\boldsymbol{\phi}\cdot\boldsymbol{n}, Q_{k-1}^Fv)_{F} \\
&=h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2.
\end{align*}
By the norm equivalence \eqref{eq:Vknormequivalence}, we get
\begin{equation}\label{eq:20220204}
\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2\lesssim (\boldsymbol{\phi}, \nabla v)_K.
\end{equation}

On the other hand, it follows from the integration by parts that
\begin{align*}
\|Q_0^K(\div\boldsymbol{\phi})\|_{0,K}&\lesssim h_{K}^{d/2}\big|Q_0^K(\div\boldsymbol{\phi})\big|\lesssim h_{K}^{-d/2}\big|(\div\boldsymbol{\phi},1)_{K}\big|=h_{K}^{-d/2}\big|(\boldsymbol{\phi}\cdot\boldsymbol{n},1)_{\partial K}\big| \\
&\lesssim \sum_{F\in\mathcal E^{\partial}(\mathcal T_K)}h_F^{-1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{align*}
Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence},
we acquire
\begin{align*}
\|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}^2.    
\end{align*}
Then we obtain from the norm equivalence \eqref{eq:Vknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
$$
\|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|v\|_{0,K}\lesssim \|\nabla v\|_{0,K}.    
$$
Finally we conclude \eqref{eq:localdiscreteinfsup} from \eqref{eq:20220204} and the last inequality.
\end{proof}

\subsection{Discrete method}
Define global nonconforming virtual element space
\begin{align*}
V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
&\qquad\; \textrm{DoF \eqref{eq:vemdof1} is single-valued for $F\in\mathcal F_h^i$, and vanishes for $F\in \mathcal F_h^{\partial}$}\}.
\end{align*}
We have the discrete Poincar\'e inequality (cf. \cite[(4.16)]{ChenHuang2020ncvem})
\begin{equation}\label{eq:vempoincareineqlty}
\|v_h\|_0\lesssim |v_h|_{1,h} \quad\forall~v_h\in V_h.
\end{equation}
Introduce discrete spaces
\begin{align*}
\boldsymbol{V}_{h}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^2): \boldsymbol{\phi}_h|_K\in \boldsymbol{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
\mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
\end{align*}
with non-negative integer $l$.
For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^2)$, let $Q_h^{\div}\boldsymbol{\phi}\in\boldsymbol{V}_{h}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:vem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation}
where the discrete bilinear form 
$$
a_h(u_h, v_h):=(Q_h^{\div}\nabla_h u_h, Q_h^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
$$

\begin{remark}\rm
By introducing $\boldsymbol{\phi}_h=Q_h^{\div}\nabla_h u_h$, the virtual element method \eqref{eq:vem} can be rewritten as the following mixed virtual element method: find $\boldsymbol{\phi}_h\in\boldsymbol{V}_{h}^{\rm div}$ and $u_h\in V_h$ such that
\begin{equation*}
\begin{aligned}
(\boldsymbol{\phi}_h, \boldsymbol{\psi}_h) - (\boldsymbol{\psi}_h, \nabla_h u_h)&=0 \quad\quad\quad\quad\;\;\forall~\boldsymbol{\psi}_h\in\boldsymbol{V}_{h}^{\rm div},\\
(\boldsymbol{\phi}_h, \nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h)&=(f, Q_hv_h)\quad\forall~v_h\in V_h.
\end{aligned}
\end{equation*}
\end{remark}

It follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that 
\begin{equation}\label{eq:ahbounedness}
a_h(u_h, v_h)\lesssim |u_h|_{1,h}|v_h|_{1,h}\quad\forall~u_h,v_h\in H_0^1(\Omega)+V_h.
\end{equation}  
\begin{lemma}
It holds the coercivity
\begin{equation}\label{eq:ahcoercivity}
|v_h|_{1,h}^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
\end{equation}  
\end{lemma}
\begin{proof}
Due to \eqref{eq:gradVknormequivalence}, we have
$$
\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_K^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
$$
which implies the coercivity \eqref{eq:ahcoercivity}.
\end{proof}

\begin{theorem}
The stabilization free virtual element method \eqref{eq:vem} is uni-solvent.
\end{theorem}
\begin{proof}
Thanks to the boundedness \eqref{eq:ahbounedness} and the coercivity \eqref{eq:ahcoercivity}, we conclude the result from the Lax-Milgram lemma \cite{LaxMilgram1954}.
\end{proof}

\subsection{A priori error analysis}
\begin{theorem}
Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:vem}. Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
\begin{equation}\label{eq:errorestimateH1}
|u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
\end{equation}
\end{theorem}
\begin{proof}
Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
$$
a(u,v_h-u_h)+(f, v_h-u_h)\lesssim h^k|u|_{k+1}|v_h-u_h|_{1,h}.
$$
Then 
\begin{align*}
&\quad \,a(u,v_h-u_h)-(f, Q_h(v_h-u_h)) \\
&=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h) \\
&=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h}.
\end{align*}
By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
\begin{align*}
&\quad a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\\
&=(Q_h^{\div}\nabla_h v_h, Q_h^{\div}\nabla_h(v_h-u_h))-(\nabla u, \nabla_h(v_h-u_h))\\
&\quad +\alpha(Q_hv_h, Q_h(v_h-u_h))-\alpha(u, v_h-u_h) \\
&=(Q_h^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
&\lesssim (\|\nabla u-Q_h^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
\end{align*}
Summing the last two inequlities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
\begin{align*}
|v_h-u_h|_{1,h}^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h} \\
&\quad + (\|\nabla u-Q_h^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
\end{align*}
which implies
$$
|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_h^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
$$
Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_h^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
\begin{align*}    
\|\nabla u-Q_h^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_h^{\div}\nabla_h u\|_0+\|Q_h^{\div}(\nabla u-\nabla_h v_h)\|_0\\
&= \|\nabla u-Q_h^{k-1}\nabla u-Q_h^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
&\quad+\|Q_h^{\div}(\nabla u-\nabla_h v_h)\|_0 \\
&\leq \|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_{1,h}.
\end{align*}
Similarly, we have
$$
\|u-Q_hv_h\|_0\leq \|u-Q_hu\|_0+\|Q_h(u-v_h)\|_0\leq \|u-Q_hu\|_0+\|u-v_h\|_0.
$$
By combining the last three inequalities, we obtain
$$
|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|u-v_h\|_{1,h},
$$
which together with the triangle inequality yields
$$
|u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\inf_{v_h\in V_h}\|u-v_h\|_{1,h}.
$$
At last, \eqref{eq:errorestimateH1} follows from the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
\end{proof}

\section{A posteriori error analysis}

\bibliographystyle{abbrv}
\bibliography{./paper}
\end{document}

### 2022-05-28 stabfreevem.tex
rename the tex file

--- 2022-05-20 stabfreencvem.tex
@@
 \begin{document}
-\title[Stabilization-Free Nonconforming VEM]{Stabilization-Free Nonconforming Virtual Element Method}
+\title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
 %\author{Long Chen}%
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:Vkm1divnormequivalence}
 For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
@@
 
-\section{Stabilization free virtual element method}
-
-In this section we will develop a stabilization free virtual element method for the second order elliptic problem
+Let 
+$$
+\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
+$$
+Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
+\begin{align}
+    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
+    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
+    (\boldsymbol{\phi}, \bs q)_K & \quad\forall~\bs q\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
+\end{align}
+For later use, let $Q_{K,k-1}^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+Introduce discrete spaces
+\begin{align*}
+\mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
+\mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
+\end{align*}
+with non-negative integer $l$.
+For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_{h,k-1}^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_{h,k-1}^{\div}\boldsymbol{\phi})|_K=Q_{K,k-1}^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$.
+For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$.
+For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$.
+And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.
+
+As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
+\begin{corollary}
+For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+\begin{equation}\label{eq:Vkm1divnormequiv}
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation}
+\end{corollary}
+
+\section{Stabilization-free nonconforming virtual element method}
+
+% In this section we will develop a stabilization-free nonconforming virtual element method for the second order elliptic 
+% problem \eqref{eq:ellipitc2ndproblem}.
+
+In this section we will develop a stabilization-free nonconforming virtual element method for the second order elliptic problem
 \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 where the bilinear form $a(u, v):=(\nabla_h u, \nabla_h v)+\alpha(u,v)$ with $\nabla_h$ being the piecewise counterpart of $\nabla$ with respect to $\mathcal T_h$.
-
-% In this section we will construct an $H(\div)$-conforming macro finite element, and then establish a norm equivalence of the gradient of the $H^1$-conforming virtual element space, which is vital in devising a stabilization free virtual element method.
 
@@
 \subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\boldsymbol{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$.
-Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\boldsymbol{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$. 
+% Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
 \begin{lemma}
@@
 \begin{equation}\label{eq:localdiscreteinfsup}    
-\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
+\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
 \end{equation}
@@
 \begin{equation}\label{eq:gradVknormequivalence}  
-\|Q_K^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
+\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
 \end{equation}
@@
 Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
-Based on DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3}, take $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ such that
-\begin{align*}
-(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F&=h_K^{-1}(v, q)_F  \quad\quad\,\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \\
+Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
+\begin{align*}
+(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F&=h_K^{-1}(v, q)_F  \quad\quad\,\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \\
 (\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \\
@@
 \end{align*}
-Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F^{\partial}(\mathcal T_K)$.
+Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$.
 By $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
@@
 \begin{equation}\label{eq:20220204}
-\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2\lesssim (\boldsymbol{\phi}, \nabla v)_K.
+\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2= (\boldsymbol{\phi}, \nabla v)_K.
 \end{equation}
@@
 \|Q_0^K(\div\boldsymbol{\phi})\|_{0,K}&\lesssim h_{K}^{d/2}\big|Q_0^K(\div\boldsymbol{\phi})\big|\lesssim h_{K}^{-d/2}\big|(\div\boldsymbol{\phi},1)_{K}\big|=h_{K}^{-d/2}\big|(\boldsymbol{\phi}\cdot\boldsymbol{n},1)_{\partial K}\big| \\
-&\lesssim \sum_{F\in\mathcal E^{\partial}(\mathcal T_K)}h_F^{-1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+&\lesssim \sum_{F\in\mathcal F(K)}h_F^{-1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{align*}
@@
 \begin{align*}
-\|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
-&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
+\|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
+&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
 &\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}^2.    
@@
 \end{equation}
-Introduce discrete spaces
-\begin{align*}
-\boldsymbol{V}_{h}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^2): \boldsymbol{\phi}_h|_K\in \boldsymbol{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
-\mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
-\end{align*}
-with non-negative integer $l$.
-For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^2)$, let $Q_h^{\div}\boldsymbol{\phi}\in\boldsymbol{V}_{h}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$.
+% Introduce discrete spaces
+% \begin{align*}
+% \mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
+% \mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
+% \end{align*}
+% with non-negative integer $l$.
+% For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_h^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$.
 For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$.
@@
 $$
-a_h(u_h, v_h):=(Q_h^{\div}\nabla_h u_h, Q_h^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
+a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
 $$
@@
 \begin{remark}\rm
-By introducing $\boldsymbol{\phi}_h=Q_h^{\div}\nabla_h u_h$, the virtual element method \eqref{eq:vem} can be rewritten as the following mixed virtual element method: find $\boldsymbol{\phi}_h\in\boldsymbol{V}_{h}^{\rm div}$ and $u_h\in V_h$ such that
+By introducing $\boldsymbol{\phi}_h=Q_{h,k-1}^{\div}\nabla_h u_h$, the virtual element method \eqref{eq:vem} can be rewritten as the following mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k-1}^{\rm div}$ and $u_h\in V_h$ such that
 \begin{equation*}
 \begin{aligned}
-(\boldsymbol{\phi}_h, \boldsymbol{\psi}_h) - (\boldsymbol{\psi}_h, \nabla_h u_h)&=0 \quad\quad\quad\quad\;\;\forall~\boldsymbol{\psi}_h\in\boldsymbol{V}_{h}^{\rm div},\\
+(\boldsymbol{\phi}_h, \boldsymbol{\psi}_h) - (\boldsymbol{\psi}_h, \nabla_h u_h)&=0 \quad\quad\quad\quad\;\;\forall~\boldsymbol{\psi}_h\in\mathbb{V}_{h,k-1}^{\rm div},\\
 (\boldsymbol{\phi}_h, \nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h)&=(f, Q_hv_h)\quad\forall~v_h\in V_h.
@@
 $$
-\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_K^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
 $$
@@
 
-\subsection{A priori error analysis}
+\subsection{Error analysis}
 \begin{theorem}
@@
 &\quad a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\\
-&=(Q_h^{\div}\nabla_h v_h, Q_h^{\div}\nabla_h(v_h-u_h))-(\nabla u, \nabla_h(v_h-u_h))\\
+&=(Q_{h,k-1}^{\div}\nabla_h v_h, Q_{h,k-1}^{\div}\nabla_h(v_h-u_h))-(\nabla u, \nabla_h(v_h-u_h))\\
 &\quad +\alpha(Q_hv_h, Q_h(v_h-u_h))-\alpha(u, v_h-u_h) \\
-&=(Q_h^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
-&\lesssim (\|\nabla u-Q_h^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
+&=(Q_{h,k-1}^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
+&\lesssim (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
 \end{align*}
@@
 &\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h} \\
-&\quad + (\|\nabla u-Q_h^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
+&\quad + (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
 \end{align*}
@@
 $$
-|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_h^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
-$$
-Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_h^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
-\begin{align*}    
-\|\nabla u-Q_h^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_h^{\div}\nabla_h u\|_0+\|Q_h^{\div}(\nabla u-\nabla_h v_h)\|_0\\
-&= \|\nabla u-Q_h^{k-1}\nabla u-Q_h^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
-&\quad+\|Q_h^{\div}(\nabla u-\nabla_h v_h)\|_0 \\
+|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_{h,k-1}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
+$$
+Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k-1}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
+\begin{align*}    
+\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_{h,k-1}^{\div}\nabla_h u\|_0+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0\\
+&= \|\nabla u-Q_h^{k-1}\nabla u-Q_{h,k-1}^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
+&\quad+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0 \\
 &\leq \|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_{1,h}.
@@
 
-\section{A posteriori error analysis}
+\section{Stabilization-free conforming virtual element method}
+
+In this section we will develop a stabilization-free conforming virtual element method for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+% \begin{equation}\label{eq:ellipitc2ndproblem}
+% \begin{cases}
+% -\Delta u + \alpha u=f & \textrm{ in } \Omega,\\
+% \qquad\qquad u=0&\textrm{ on } \partial\Omega,
+% \end{cases}
+% \end{equation}
+% where $\Omega\subseteq\mathbb R^d$ is a bounded polygon, $f\in L^2(\Omega)$ and $\alpha$ is a positive constant.
+The weak formulation of problem \eqref{eq:ellipitc2ndproblem} is to find $u\in H_0^1(\Omega)$ such that
+% \begin{equation}\label{eq:ellipitc2ndproblemweakform}
+% a(u,v)=(f,v)\quad\forall~v\in H_0^1(\Omega),
+% \end{equation}
+% where the bilinear form $a(u, v):=(\nabla_h u, \nabla_h v)+\alpha(u,v)$ with $\nabla_h$ being the piecewise counterpart of $\nabla$ with respect to $\mathcal T_h$.
+
+% In this section we will construct an $H(\div)$-conforming macro finite element, and then establish a norm equivalence of the gradient of the $H^1$-conforming virtual element space, which is vital in devising a stabilization free virtual element method.
+
+\subsection{$H^1$-conforming virtual element}
+
+Recall the $H^1$-conforming virtual element in \cite{Huang2021,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+The degrees of freedom are given by
+\begin{align}
+v(\delta) & \quad\forall~\delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
+\frac{1}{|e|}(v, q)_e & \quad\forall~q\in\mathbb P_{k-2}(e), e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
+\frac{1}{|K|}(v, q)_K & \quad\forall~q\in\mathbb P_{k-2}(K). \label{eq:cfmvemdof3}
+\end{align}
+
+To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
+\begin{align}
+(\nabla\Pi_k^Kv, \nabla q)_K&=(\nabla v, \nabla q)_K\quad  \forall~q\in \mathbb P_k(K),\label{eq:projlocal1}\\
+\sum_{\delta\in\mathcal V(K)}(\Pi_k^Kv)(\delta)&=\sum_{\delta\in\mathcal V(K)}v(\delta).\label{eq:projlocal2}
+\end{align}
+It holds 
+\begin{equation}\label{eq:localprojprop1}
+\Pi_k^Kq=q \quad\forall~q\in\mathbb P_k(K).    
+\end{equation}
+
+% The shape function space $V_k(K)$ is defined recursively with respect to the dimension of $K$. 
+% When $K$ is a line segment, $V_k(K)$ is defined exactly as the polynomial space $\mathbb P_k(K)$.
+% Assume $V_k(K)$ has been defined on the $l$-dimensional polytope $K$ for $l=1,\ldots, d-1$. 
+% Then for  $d$-dimensional polytope $K$, define
+Now define
+\begin{align*}
+V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
+&\qquad\qquad\qquad\qquad\qquad\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
+\end{align*}
+where $\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+It holds $\mathbb P_k(K)\subseteq V_k(K)$.
+
+For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}, and the $L^2$ projection
+\begin{equation}\label{eq:cfmvemQKPik}  
+Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv
+\end{equation}
+is also computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}. 
+We have the norm equivalence of the virtual element space (cf. \cite[Lemma 4.7]{Huang2021} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$,
+\begin{equation}\label{eq:cfmVknormequivalence}
+h_K^2|v|_{1,K}^2\lesssim\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2 + \sum_{\delta\in \mathcal V(K)}h_K^2|v(\delta)|^2+\sum_{e\in\mathcal E(K)}h_K\|Q_{k-2}^ev\|_{0,e}^2.
+\end{equation}
+
+\subsection{Local inf-sup condition and norm equivalence}
+With the help of the macro element space $\mathbb{V}_{k}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$. 
+% Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+\begin{lemma}
+It holds the inf-sup condition
+\begin{equation}\label{eq:cfmlocaldiscreteinfsup}    
+\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
+\end{equation}
+Consequently
+\begin{equation}\label{eq:cfmgradVknormequivalence}  
+\|Q_{K,k}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
+\end{equation}
+\end{lemma}
+\begin{proof}
+Clearly the norm equivalence \eqref{eq:cfmgradVknormequivalence} follows from the local inf-sup condition~\eqref{eq:cfmlocaldiscreteinfsup}.
+We will focus on the proof of \eqref{eq:cfmlocaldiscreteinfsup}.
+Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
+Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$ such that
+\begin{align*}
+(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_e&=h_K^{-1}(v, q)_e  \quad\quad\,\forall~q\in\mathbb P_{k}(e) \textrm{ on each }  e\in\mathcal E(K), \\
+(\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{k-2}(K)/\mathbb P_{0}(K), \\
+(\boldsymbol{\phi}, \bs q)_K&=0  \qquad\qquad\qquad\forall~\bs q\in \curl\mathring{V}_{k+1}^{\grad}(K). 
+\end{align*}
+Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}=h_K^{-1}v|_{\partial K}$.
+By $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
+Apply the integration by parts to get
+\begin{align*}
+(\boldsymbol{\phi}, \nabla v)_K&=(\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K}-(\div\boldsymbol{\phi}, v)_K=(\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K}-(\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi}), v)_K \\
+&=h_K^{-1}\|v\|_{0,\partial K}^2+h_K^{-2}(Q_{k-2}^Kv, v)_K=h_K^{-1}\|v\|_{0,\partial K}^2+h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2.
+\end{align*}
+By the norm equivalence \eqref{eq:cfmVknormequivalence} and the inverse inequality, we get
+\begin{equation}\label{eq:20220528}
+\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+h_K^{-1}\|v\|_{0,\partial K}^2 + \sum_{\delta\in \mathcal V(K)}|v(\delta)|^2\lesssim (\boldsymbol{\phi}, \nabla v)_K.
+\end{equation}
+
+On the other hand, it follows from the integration by parts that
+\begin{align*}
+\|Q_0^K(\div\boldsymbol{\phi})\|_{0,K}&\lesssim h_{K}\big|Q_0^K(\div\boldsymbol{\phi})\big|\lesssim h_{K}^{-1}\big|(\div\boldsymbol{\phi},1)_{K}\big|=h_{K}^{-1}\big|(\boldsymbol{\phi}\cdot\boldsymbol{n},1)_{\partial K}\big| \\
+&\lesssim h_{K}^{-1}\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e}.
+\end{align*}
+Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence},
+we acquire
+\begin{align*}
+\|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e} \\
+&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e} \\
+&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +h_K^{-1/2}\|v\|_{0,\partial K}.    
+\end{align*}
+Then we obtain from the norm equivalence \eqref{eq:cfmVknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
+\begin{align*}
+\|\boldsymbol{\phi}\|_{0,K}
+&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{\delta\in \mathcal V(K)}|v(\delta)|+\sum_{e\in\mathcal E(K)}h_K^{-1/2}\|Q_{k-2}^ev\|_{0,e} \\
+&\lesssim h_K^{-1}\|v\|_{0,K}\lesssim \|\nabla v\|_{0,K}.    
+\end{align*}
+Finally we conclude \eqref{eq:cfmlocaldiscreteinfsup} from \eqref{eq:20220528} and the last inequality.
+\end{proof}
+
+\subsection{Discrete method}
+Define the global conforming virtual element space
+$$
+V_h:=\{v_h\in H_0^1(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h\}.
+$$
+
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+\begin{equation}\label{eq:cfmvem}
+a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
+\end{equation}
+where the discrete bilinear form 
+$$
+a_h(u_h, v_h):=(Q_{h,k}^{\div}\nabla u_h, Q_{h,k}^{\div}\nabla v_h)+\alpha(Q_hu_h, Q_hv_h).
+$$
+
+\begin{remark}\rm
+By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the virtual element method \eqref{eq:cfmvem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
+\begin{equation*}
+\begin{aligned}
+(\boldsymbol{\phi}_h, \boldsymbol{\psi}_h) - (\boldsymbol{\psi}_h, \nabla u_h)&=0 \quad\quad\quad\quad\;\;\forall~\boldsymbol{\psi}_h\in\mathbb{V}_{h,k}^{\rm div},\\
+(\boldsymbol{\phi}_h, \nabla v_h)+\alpha(Q_hu_h, Q_hv_h)&=(f, Q_hv_h)\quad\forall~v_h\in V_h.
+\end{aligned}
+\end{equation*}
+\end{remark}
+
+It is obvious that 
+\begin{equation}\label{eq:cfmahbounedness}
+a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
+\end{equation}  
+\begin{lemma}
+It holds the coercivity
+\begin{equation}\label{eq:cfmahcoercivity}
+|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+\end{equation}  
+\end{lemma}
+\begin{proof}
+Due to \eqref{eq:cfmgradVknormequivalence}, we have
+$$
+\sum_{K\in\mathcal T_h}\|\nabla v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+$$
+which implies the coercivity \eqref{eq:cfmahcoercivity}.
+\end{proof}
+
+\begin{theorem}
+The stabilization free virtual element method \eqref{eq:cfmvem} is uni-solvent.
+\end{theorem}
+\begin{proof}
+Thanks to the boundedness \eqref{eq:cfmahbounedness} and the coercivity \eqref{eq:cfmahcoercivity}, we conclude the result from the Lax-Milgram lemma \cite{LaxMilgram1954}.
+\end{proof}
+
+\subsection{Error analysis}
+\begin{theorem}
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:cfmvem}.
+Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$.
+Then
+\begin{equation}\label{eq:cfmerrorestimateH1}
+|u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
+\end{equation}
+\end{theorem}
+\begin{proof}
+Take any $v_h\in V_h$. By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
+\begin{align*}
+|v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
+&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
+&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
+\end{align*}
+By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$,
+\begin{align*}
+&\quad a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\\
+&=(Q_{h,k}^{\div}\nabla v_h, Q_{h,k}^{\div}\nabla(v_h-u_h))-(\nabla u, \nabla(v_h-u_h))\\
+&\quad +\alpha(Q_hv_h, Q_h(v_h-u_h))-\alpha(u, v_h-u_h) \\
+&=(Q_{h,k}^{\div}\nabla v_h-\nabla u, \nabla(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
+&\leq \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\alpha\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
+\end{align*}
+Combining the last two inequalities gives
+$$
+|v_h-u_h|_1\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0+h\|f-Q_hf\|_0.
+$$
+Since $\mathbb P_{k-1}(K;\mathbb R^2)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
+\begin{align*}    
+\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0&\leq \|\nabla u-Q_{h,k}^{\div}\nabla u\|_0+\|Q_{h,k}^{\div}(\nabla u-\nabla v_h)\|_0\\
+&= \|\nabla u-Q_h^{k-1}\nabla u-Q_{h,k}^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
+&\quad+\|Q_{h,k}^{\div}(\nabla u-\nabla v_h)\|_0 \\
+&\leq \|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_1.
+\end{align*}
+Similarly, we have
+$$
+\|u-Q_hv_h\|_0\leq \|u-Q_hu\|_0+\|Q_h(u-v_h)\|_0\leq \|u-Q_hu\|_0+\|u-v_h\|_0.
+$$
+By combining the last three inequalities, we obtain from the Poincar\'e inequality that
+$$
+|v_h-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0,
+$$
+which together with the triangle inequality yields
+$$
+|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
+$$
+By the arbitrariness of $v_h\in V_h$, we derive
+$$
+|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
+$$
+At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
+\end{proof}
 

### 2022-05-29 stabfreevem.tex
some revisions

@@
 
-% \begin{abstract}
-% \end{abstract}
+\begin{abstract}
+Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions.
+
+\end{abstract}
 
@@
 
-\section{Preliminaries}
+\section{Introduction}
+
+Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon.
+We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on smiliar stabilization-free virtual element methods for plane elasticity problem.
+The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
+the analysis is rather elaborate. 
+This motives us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.
+
+The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
+In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
+A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}.
+And a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+Some numerical results are shown in Section \ref{sec:numericalexamps}.
+
+\section{Preliminaries}\label{sec:prelim}
 
@@
 
-For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+For $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
 For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
@@
 and $h_K:=\mbox{diam}(K)$.
-Denote by $\mathcal F_h$ and $\mathcal F_h^i$ the set of all $(d-1)$-dimensional faces and interior $(d-1)$-dimensional faces of the partition $\mathcal T_h$.
-Set $\mathcal F_h^{\partial}=\mathcal F_h\backslash\mathcal F_h^i$.
+Denote by $\mathcal F_h^r$ the set of all $(d-r)$-dimensional faces of the partition $\mathcal T_h$ for $r=1,\ldots,d$.
+Set $\mathcal F_h:=\mathcal F_h^1$ for simplicity.
+Let $\mathcal F_h^{\partial}$ be the subset of $\mathcal F_h$ including all $(d-1)$-dimensional faces on $\partial\Omega$.
 For any $F\in\mathcal{F}_h$,
@@
 For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
-For $F\in\mathcal F_h$ and smooth vector function $\boldsymbol{v}$, define surface divergence
+For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
+On face $F\in\mathcal F_h$, define surface divergence
 $$
@@
 $$
+For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.
 
@@
 \begin{itemize}
- \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq n-1$ is star-shaped with a uniformly bounded chunkiness parameter.
+ \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter.
 
@@
 ``$\lesssim\cdots $" to mean that ``$\leq C\cdots$", where
-$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $n$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
+$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
 which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.
@@
 $$
-Denote $
-\mathcal{F}^i(\mathcal T_K):=\mathcal{F}(\mathcal T_K)\backslash\mathcal{F}^{\partial}(\mathcal T_K)$ and $\mathcal{E}^i(\mathcal T_K):=\mathcal{E}(\mathcal T_K)\backslash\mathcal{E}^{\partial}(\mathcal T_K).
-$
-
-%Note that (A1) and (A2) imply ${\rm diam}(F) \eqsim {\rm diam} (K)$ for all $F\in \mathcal F^r(K), 1\leq r\leq n-1$.
-%For a star-shaped domain $D$,
-
-\section{$H(\div)$-Conforming Macro Finite Element}
-
-In this section we will construct $H(\div)$-conforming macro finite element in arbitrary dimension.
-\subsection{$H(\div)$-conforming finite element}
-For each polygon $K\in \mathcal T_h$ and $k\geq2$, let 
+
+Hereafter we use $T$ to represent a simplex, and $K$ to denote a general polytope.
+
+\section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
+
+In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
+\subsection{$H(\div)$-conforming finite elements}
+For polygon $K\in \mathcal T_h$ and $k\geq2$, let 
 $$
@@
 $$ 
-be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose DoFs are given by (cf. \cite{ChenHuang2021divdiv})
+be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
 \begin{align}
@@
 
-By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have
+By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have the decomposition
 \begin{equation}\label{eq:Pkvectordecomp}  
@@
 \begin{equation}\label{eq:Pkskwtensordecomp}  
-\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T,\mathbb K)\cap\ker(\boldsymbol{x})\big).
+\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big).
 \end{equation}
@@
 $$
-By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T,\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
+By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
 Due to complex \eqref{eq:polycomplex1},
@@
 Hence $\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}|_{\partial T}=0$. 
-Thanks to DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element, we acquire from DoF \eqref{eq:-2formfemdof31} that $\div\boldsymbol{\tau}=\boldsymbol{0}$, which together with DoF \eqref{eq:-2formfemdof32} and decomposition \eqref{eq:Pkskwtensordecomp} gives
+Thanks to DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element, we acquire from DoF \eqref{eq:-2formfemdof31} and $\div\div\boldsymbol{\tau}=0$ that $\div\boldsymbol{\tau}=\boldsymbol{0}$, which together with DoF \eqref{eq:-2formfemdof32} and decomposition \eqref{eq:Pkskwtensordecomp} gives
 $$
@@
 
-For polygon $K\in \mathcal T_h$, define local finite element space for differential $(d-2)$-form  
+For polygon $K\in \mathcal T_h$, define the local finite element space for differential $(d-2)$-form  
 \begin{align*}  
@@
 $$
-(\div_F(\boldsymbol{\sigma}\boldsymbol{n}), 1)_F=(\boldsymbol{v}, 1)_F\quad\forall~F\in\mathcal F(\mathcal T_K),
+(\div_F(\boldsymbol{\sigma}\boldsymbol{n}), 1)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, 1)_F\quad\forall~F\in\mathcal F(\mathcal T_K),
 $$
@@
 \end{align}
+
+As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
+\begin{corollary}
+For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+\begin{equation}\label{eq:Vkm1divnormequiv}
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation}
+\end{corollary}
+
 For later use, let $Q_{K,k-1}^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
@@
 
-As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
-\begin{corollary}
-For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
-\begin{equation}\label{eq:Vkm1divnormequiv}
-\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\end{equation}
-\end{corollary}
-
-\section{Stabilization-free nonconforming virtual element method}
+\section{Stabilization-free nonconforming virtual element method}\label{sec:stabfreencfmvem}
 
@@
 
-In this section we will develop a stabilization-free nonconforming virtual element method for the second order elliptic problem
+In this section we will develop a stabilization-free nonconforming virtual element method for the second order elliptic problem in arbitrary dimension
 \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 \end{equation}
-where $\Omega\subseteq\mathbb R^d$ is a bounded polygon, $f\in L^2(\Omega)$ and $\alpha$ is a positive constant.
+where $\Omega\subseteq\mathbb R^d$ is a bounded polygon, $f\in L^2(\Omega)$ and $\alpha$ is a nonnegative constant.
 The weak formulation of problem \eqref{eq:ellipitc2ndproblem} is to find $u\in H_0^1(\Omega)$ such that
@@
 \subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$. 
+With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$, which is vitally important to design stabilization-free virtual element methods.
 % Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
-\begin{lemma}
+\begin{lemma}\label{lem:gradVknormequivalence}
 It holds the inf-sup condition
@@
 Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$.
-By $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
+Since $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
 Apply the integration by parts to get
@@
 \end{align*}
-Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence},
+Employing the norm equivalence \eqref{eq:Vkm1divnormequiv},
 we acquire
@@
 \subsection{Discrete method}
-Define global nonconforming virtual element space
+Define the global nonconforming virtual element space
 \begin{align*}
 V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
-&\qquad\; \textrm{DoF \eqref{eq:vemdof1} is single-valued for $F\in\mathcal F_h^i$, and vanishes for $F\in \mathcal F_h^{\partial}$}\}.
+&\qquad\; \textrm{DoF \eqref{eq:vemdof1} is single-valued for $F\in\mathcal F_h$, and vanishes for $F\in \mathcal F_h^{\partial}$}\}.
 \end{align*}
@@
 \subsection{Error analysis}
-\begin{theorem}
+\begin{theorem}\label{thm:errorestimateH1}
 Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:vem}.
@@
 \begin{align*}    
-\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_{h,k-1}^{\div}\nabla_h u\|_0+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0\\
+\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_{h,k-1}^{\div}\nabla u\|_0+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0\\
 &= \|\nabla u-Q_h^{k-1}\nabla u-Q_{h,k-1}^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
@@
 
-\section{Stabilization-free conforming virtual element method}
+\section{Stabilization-free conforming virtual element method}\label{sec:stabfreecfmvem}
 
@@
 
+For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
+
 \subsection{$H^1$-conforming virtual element}
@@
 \end{align}
-
-To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
-\begin{align}
-(\nabla\Pi_k^Kv, \nabla q)_K&=(\nabla v, \nabla q)_K\quad  \forall~q\in \mathbb P_k(K),\label{eq:projlocal1}\\
-\sum_{\delta\in\mathcal V(K)}(\Pi_k^Kv)(\delta)&=\sum_{\delta\in\mathcal V(K)}v(\delta).\label{eq:projlocal2}
-\end{align}
-It holds 
-\begin{equation}\label{eq:localprojprop1}
-\Pi_k^Kq=q \quad\forall~q\in\mathbb P_k(K).    
-\end{equation}
+And the space of shape functions is
+\begin{align*}
+V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
+&\qquad\qquad\qquad\qquad\qquad\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
+\end{align*}
+where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
+It holds $\mathbb P_k(K)\subseteq V_k(K)$.
+% To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
+% \begin{align}
+% (\nabla\Pi_k^Kv, \nabla q)_K&=(\nabla v, \nabla q)_K\quad  \forall~q\in \mathbb P_k(K),\label{eq:projlocal1}\\
+% \sum_{\delta\in\mathcal V(K)}(\Pi_k^Kv)(\delta)&=\sum_{\delta\in\mathcal V(K)}v(\delta).\label{eq:projlocal2}
+% \end{align}
+% It holds 
+% \begin{equation}\label{eq:localprojprop1}
+% \Pi_k^Kq=q \quad\forall~q\in\mathbb P_k(K).    
+% \end{equation}
 
@@
 % Then for  $d$-dimensional polytope $K$, define
-Now define
-\begin{align*}
-V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
-&\qquad\qquad\qquad\qquad\qquad\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
-\end{align*}
-where $\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
-It holds $\mathbb P_k(K)\subseteq V_k(K)$.
-
-For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}, and the $L^2$ projection
-\begin{equation}\label{eq:cfmvemQKPik}  
-Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv
-\end{equation}
-is also computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}. 
-We have the norm equivalence of the virtual element space (cf. \cite[Lemma 4.7]{Huang2021} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$,
+
+For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
+We have the norm equivalence of space $V_k(K)$ (cf. \cite[Lemma 4.7]{Huang2021} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$, it holds
 \begin{equation}\label{eq:cfmVknormequivalence}
@@
 
-\subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\mathbb{V}_{k}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$. 
-% Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
-\begin{lemma}
-It holds the inf-sup condition
-\begin{equation}\label{eq:cfmlocaldiscreteinfsup}    
-\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
-\end{equation}
-Consequently
+Employing the same argument as in Lemma~\ref{lem:gradVknormequivalence}, from  \eqref{eq:cfmVknormequivalence}, we get the norm equivalence
 \begin{equation}\label{eq:cfmgradVknormequivalence}  
@@
 \end{equation}
-\end{lemma}
-\begin{proof}
-Clearly the norm equivalence \eqref{eq:cfmgradVknormequivalence} follows from the local inf-sup condition~\eqref{eq:cfmlocaldiscreteinfsup}.
+
+\begin{remark}\rm
+When $k\geq2$, we can replace $Q_{K,k}^{\div}$ by the $L^2$-orthogonal projection operator onto space $\mathbb{V}_{k,k-2}^{\rm div}(K)$, where
+\begin{align*}
+\mathbb{V}_{k,k-2}^{\rm div}(K):=&\{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\} \\
+=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_e\in\mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K)\}.
+\end{align*}
+\end{remark}
+% \subsection{Local inf-sup condition and norm equivalence}
+% With the help of the macro element space $\mathbb{V}_{k}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$. 
+% % Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+% \begin{lemma}
+% It holds the inf-sup condition
+% \begin{equation}\label{eq:cfmlocaldiscreteinfsup}    
+% \|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
+% \end{equation}
+% Consequently
+% \begin{equation}\label{eq:cfmgradVknormequivalence}  
+% \|Q_{K,k}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
+% \end{equation}
+% \end{lemma}
+% \begin{proof}
+% Clearly the norm equivalence \eqref{eq:cfmgradVknormequivalence} follows from the local inf-sup condition~\eqref{eq:cfmlocaldiscreteinfsup}.
 We will focus on the proof of \eqref{eq:cfmlocaldiscreteinfsup}.
-Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
-Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$ such that
-\begin{align*}
-(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_e&=h_K^{-1}(v, q)_e  \quad\quad\,\forall~q\in\mathbb P_{k}(e) \textrm{ on each }  e\in\mathcal E(K), \\
-(\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{k-2}(K)/\mathbb P_{0}(K), \\
-(\boldsymbol{\phi}, \bs q)_K&=0  \qquad\qquad\qquad\forall~\bs q\in \curl\mathring{V}_{k+1}^{\grad}(K). 
-\end{align*}
-Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}=h_K^{-1}v|_{\partial K}$.
-By $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
+% Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
+% Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$ such that
+% \begin{align*}
+% (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_e&=h_K^{-1}(v, q)_e  \quad\quad\,\forall~q\in\mathbb P_{k}(e) \textrm{ on each }  e\in\mathcal E(K), \\
+% (\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{k-1}(K)/\mathbb R, \\
+% (\boldsymbol{\phi}, \bs q)_K&=0  \qquad\qquad\qquad\forall~\bs q\in \curl\mathring{V}_{k+1}^{\grad}(K). 
+% \end{align*}
+% Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}=h_K^{-1}v|_{\partial K}$.
+By $\div\boldsymbol{\phi}\in \mathbb P_{k-1}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-1}^Kv$.
 Apply the integration by parts to get
-\begin{align*}
-(\boldsymbol{\phi}, \nabla v)_K&=(\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K}-(\div\boldsymbol{\phi}, v)_K=(\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K}-(\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi}), v)_K \\
-&=h_K^{-1}\|v\|_{0,\partial K}^2+h_K^{-2}(Q_{k-2}^Kv, v)_K=h_K^{-1}\|v\|_{0,\partial K}^2+h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2.
-\end{align*}
-By the norm equivalence \eqref{eq:cfmVknormequivalence} and the inverse inequality, we get
-\begin{equation}\label{eq:20220528}
-\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+h_K^{-1}\|v\|_{0,\partial K}^2 + \sum_{\delta\in \mathcal V(K)}|v(\delta)|^2\lesssim (\boldsymbol{\phi}, \nabla v)_K.
-\end{equation}
-
-On the other hand, it follows from the integration by parts that
-\begin{align*}
-\|Q_0^K(\div\boldsymbol{\phi})\|_{0,K}&\lesssim h_{K}\big|Q_0^K(\div\boldsymbol{\phi})\big|\lesssim h_{K}^{-1}\big|(\div\boldsymbol{\phi},1)_{K}\big|=h_{K}^{-1}\big|(\boldsymbol{\phi}\cdot\boldsymbol{n},1)_{\partial K}\big| \\
-&\lesssim h_{K}^{-1}\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e}.
-\end{align*}
-Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence},
-we acquire
-\begin{align*}
-\|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e} \\
-&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{e\in\mathcal E^{\partial}(\mathcal T_K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e} \\
-&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +h_K^{-1/2}\|v\|_{0,\partial K}.    
-\end{align*}
-Then we obtain from the norm equivalence \eqref{eq:cfmVknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
-\begin{align*}
-\|\boldsymbol{\phi}\|_{0,K}
-&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{\delta\in \mathcal V(K)}|v(\delta)|+\sum_{e\in\mathcal E(K)}h_K^{-1/2}\|Q_{k-2}^ev\|_{0,e} \\
-&\lesssim h_K^{-1}\|v\|_{0,K}\lesssim \|\nabla v\|_{0,K}.    
-\end{align*}
-Finally we conclude \eqref{eq:cfmlocaldiscreteinfsup} from \eqref{eq:20220528} and the last inequality.
-\end{proof}
+% \begin{align*}
+% (\boldsymbol{\phi}, \nabla v)_K&=(\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K}-(\div\boldsymbol{\phi}, v)_K=(\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K}-(\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi}), v)_K \\
+% &=h_K^{-1}\|v\|_{0,\partial K}^2+h_K^{-2}(Q_{k-1}^Kv, v)_K=h_K^{-1}\|v\|_{0,\partial K}^2+h_K^{-2}\|Q_{k-1}^Kv\|_{0,K}^2.
+% \end{align*}
+% By the norm equivalence \eqref{eq:cfmVknormequivalence} and the inverse inequality, we get
+% \begin{equation}\label{eq:20220528}
+% \|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+h_K^{-1}\|v\|_{0,\partial K}^2 + \sum_{\delta\in \mathcal V(K)}|v(\delta)|^2\lesssim (\boldsymbol{\phi}, \nabla v)_K.
+% \end{equation}
+
+% On the other hand, it follows from the integration by parts that
+% \begin{align*}
+% \|Q_0^K(\div\boldsymbol{\phi})\|_{0,K}&\lesssim h_{K}\big|Q_0^K(\div\boldsymbol{\phi})\big|\lesssim h_{K}^{-1}\big|(\div\boldsymbol{\phi},1)_{K}\big|=h_{K}^{-1}\big|(\boldsymbol{\phi}\cdot\boldsymbol{n},1)_{\partial K}\big| \\
+% &\lesssim h_{K}^{-1}\sum_{e\in\mathcal E^{\partial}(K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e}.
+% \end{align*}
+% Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence},
+% we acquire
+% \begin{align*}
+% \|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{e\in\mathcal E^{\partial}(K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e} \\
+% &\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{e\in\mathcal E^{\partial}(K)}h_e^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,e} \\
+% &\lesssim h_K^{-1}\|Q_{k-1}^Kv\|_{0,K} +h_K^{-1/2}\|v\|_{0,\partial K}.    
+% \end{align*}
+% Then we obtain from the norm equivalence \eqref{eq:cfmVknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
+% \begin{align*}
+% \|\boldsymbol{\phi}\|_{0,K}
+% &\lesssim h_K^{-1}\|Q_{k-1}^Kv\|_{0,K} +\sum_{\delta\in \mathcal V(K)}|v(\delta)|+\sum_{e\in\mathcal E(K)}h_K^{-1/2}\|Q_{k-2}^ev\|_{0,e} \\
+% &\lesssim h_K^{-1}\|v\|_{0,K}\lesssim \|\nabla v\|_{0,K}.    
+% \end{align*}
+% Finally we conclude \eqref{eq:cfmlocaldiscreteinfsup} from \eqref{eq:20220528} and the last inequality.
+% \end{proof}
 
@@
 $$
+
+It is obvious that 
+\begin{equation}\label{eq:cfmahbounedness}
+a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
+\end{equation}  
+And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
+the coercivity
+\begin{equation}\label{eq:cfmahcoercivity}
+|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+\end{equation}  
+Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
 
@@
 
-It is obvious that 
-\begin{equation}\label{eq:cfmahbounedness}
-a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
-\end{equation}  
-\begin{lemma}
-It holds the coercivity
-\begin{equation}\label{eq:cfmahcoercivity}
-|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
-\end{equation}  
-\end{lemma}
-\begin{proof}
-Due to \eqref{eq:cfmgradVknormequivalence}, we have
-$$
-\sum_{K\in\mathcal T_h}\|\nabla v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
-$$
-which implies the coercivity \eqref{eq:cfmahcoercivity}.
-\end{proof}
-
-\begin{theorem}
-The stabilization free virtual element method \eqref{eq:cfmvem} is uni-solvent.
-\end{theorem}
-\begin{proof}
-Thanks to the boundedness \eqref{eq:cfmahbounedness} and the coercivity \eqref{eq:cfmahcoercivity}, we conclude the result from the Lax-Milgram lemma \cite{LaxMilgram1954}.
-\end{proof}
+% \begin{lemma}
+% It holds the coercivity
+% \begin{equation}\label{eq:cfmahcoercivity}
+% |v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+% \end{equation}  
+% \end{lemma}
+% \begin{proof}
+% Due to \eqref{eq:cfmgradVknormequivalence}, we have
+% $$
+% \sum_{K\in\mathcal T_h}\|\nabla v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+% $$
+% which implies the coercivity \eqref{eq:cfmahcoercivity}.
+% \end{proof}
+
+% \begin{theorem}
+% The stabilization free virtual element method \eqref{eq:cfmvem} is uni-solvent.
+% \end{theorem}
+% \begin{proof}
+% Thanks to the boundedness \eqref{eq:cfmahbounedness} and the coercivity \eqref{eq:cfmahcoercivity}, we conclude the result from the Lax-Milgram lemma \cite{LaxMilgram1954}.
+% \end{proof}
 
@@
 \begin{proof}
-Take any $v_h\in V_h$. By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
+Take any $v_h\in V_h$. 
+Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
+$$
+\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
+$$
+$$
+a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
+$$
+Combining the last two inequalities gives
+$$
+a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
+$$
+By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
 \begin{align*}
@@
 &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
-&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
+% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
 &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
 \end{align*}
-By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$,
-\begin{align*}
-&\quad a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\\
-&=(Q_{h,k}^{\div}\nabla v_h, Q_{h,k}^{\div}\nabla(v_h-u_h))-(\nabla u, \nabla(v_h-u_h))\\
-&\quad +\alpha(Q_hv_h, Q_h(v_h-u_h))-\alpha(u, v_h-u_h) \\
-&=(Q_{h,k}^{\div}\nabla v_h-\nabla u, \nabla(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
-&\leq \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\alpha\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
-\end{align*}
-Combining the last two inequalities gives
-$$
-|v_h-u_h|_1\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0+h\|f-Q_hf\|_0.
-$$
-Since $\mathbb P_{k-1}(K;\mathbb R^2)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
-\begin{align*}    
-\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0&\leq \|\nabla u-Q_{h,k}^{\div}\nabla u\|_0+\|Q_{h,k}^{\div}(\nabla u-\nabla v_h)\|_0\\
-&= \|\nabla u-Q_h^{k-1}\nabla u-Q_{h,k}^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
-&\quad+\|Q_{h,k}^{\div}(\nabla u-\nabla v_h)\|_0 \\
-&\leq \|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_1.
-\end{align*}
-Similarly, we have
-$$
-\|u-Q_hv_h\|_0\leq \|u-Q_hu\|_0+\|Q_h(u-v_h)\|_0\leq \|u-Q_hu\|_0+\|u-v_h\|_0.
-$$
-By combining the last three inequalities, we obtain from the Poincar\'e inequality that
-$$
-|v_h-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0,
-$$
-which together with the triangle inequality yields
-$$
-|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
-$$
+Hence we get from the triangle inequality and the last two inequalities that
+\begin{align*}  
+|u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
+&\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
+\end{align*}
 By the arbitrariness of $v_h\in V_h$, we derive
@@
 \end{proof}
+
+\section{Numerical examples}\label{sec:numericalexamps}
 

### 2022-05-30 stabfreevem.tex
update introduction

@@
 \title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
-%\author{Long Chen}%
-%\address{Department of Mathematics, University of California at Irvine, Irvine, CA 92697, USA}%
-%\email{chenlong@math.uci.edu}%
-% \author{Xuehai Huang}%
-% \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
-% \email{huang.xuehai@sufe.edu.cn}%
-
-%\thanks{The first author was supported by.}
-%\thanks{
-%The first author was supported by the National Science Foundation (NSF) DMS-1418934, and
-%in part by the Sea Poly Project of Beijing Overseas Talents and the National Natural Science Foundation of China Project 11671159.}
-% \thanks{This work was supported by the National Natural Science Foundation of China Projects 12171300 and 11771338, the Natural Science Foundation of Shanghai 21ZR1480500, and the Fundamental Research Funds for the Central Universities 2019110066.}
-
-% \subjclass[2010]{
-% %65N55;   %% Multigrid methods; domain decomposition
-% %65F10;   %%  Iterative methods for linear systems
-% 65N30;   %%  Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods;
-% 65N12;   %%  Stability and convergence of numerical methods;
-% 65N22;   %%  Solution of discretized equations
-% %65N15;   %%  Error bounds
-% }
+\author{Chunyu Chen}%
+\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
+ \email{...@xtu.edu.cn}%
+ \author{Xuehai Huang}%
+ \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
+ \email{huang.xuehai@sufe.edu.cn}%
+\author{Huayi Wei}%
+\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
+ \email{weihuayi@xtu.edu.cn}%
+
+ \thanks{The second author is the corresponding author.
+The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.}
+ \thanks{The first and third authors were supported by NSFC (11871413) and in part by projects
+of Education Department of Hunan Provincial of China (19B534, 19A500).}
+
+\makeatletter
+\@namedef{subjclassname@2020}{\textup{2020} Mathematics Subject Classification}
+\makeatother
+\subjclass[2020]{
+%65F10;   %% Iterative numerical methods for linear systems
+% 58J10;   %%  Differential complexes [See also 35Nxx]; elliptic complexes
+65N12;   %%  Stability and convergence of numerical methods for boundary value problems involving PDEs;
+% 65N15;   %%  Error bounds for boundary value problems involving PDEs
+65N22;   %%  Numerical solution of discretized equations for boundary value problems involving PDEs;
+65N30;   %%  Finite element, Rayleigh-Ritz and Galerkin methods for boundary value problems involving PDEs;
+%65N55;   %%  Multigrid methods; domain decomposition for boundary value problems involving PDEs;
+% 15A69;   %%  Multilinear algebra, tensor calculus
+% 15A72;   %%  Vector and tensor algebra, theory of invariants [See also 13A50, 14L24]
+}
 
@@
 Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions.
-
+The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
+Optimal error estimates are derived for these stabilization-free virtual element methods.
+Numerical results are provided to verify the convergence rates.
 \end{abstract}
 
-% \keywords{Nonconforming finite element Stokes complex, quad-curl problem, error analysis, decoupling, fast solver}
+\keywords{Virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis}
 
@@
 
-\tableofcontents
+% \tableofcontents
 
@@
 Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon.
-We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on smiliar stabilization-free virtual element methods for plane elasticity problem.
+We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on similar stabilization-free virtual element methods for plane elasticity problem.
 The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
@@
 This motives us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.
+
+The key to construct stabilization-free virtual element methods to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
+\begin{enumerate}[(C1)]
+\item It holds the norm equivalence 
+\begin{equation}\label{intro:gradVknormequiv} 
+\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
+\end{equation}
+on shape function space $V_k(K)$ of virtual elements;
+\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
+\end{enumerate}
+We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$.
+The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
+In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
+While only
+$$
+\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
+$$
+hold
+rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
+To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and virtual element space $V_k(K)$ is modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
+Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
+
+We first construct $H(\div)$-conforming macro finite elements based on a simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension.
+The shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$th order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition $\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element space for $k=0$, with some constraints.
+To ensure the $L^2$ projection $Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable for virtual element function $v\in V_k(K)$, we require $\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and $\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.
+Based on these considerations and the direct decomposition of an $H(\div)$-conforming macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the $L^2$ norm equivalence.
+By the way, we use the matrix-vector language to review a conforming finite element for differential $(d-2)$-form in \cite{ArnoldFalkWinther2006,Arnold2018}.
+
+% $$
+% \|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
+% $$
+
+% $\mathbb{V}_{k-1}^{\rm div}(K)$
+
+By the aid of projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming virtual element method in arbitrary dimension and a stabilization-free conforming virtual element method in two dimensions  for second order elliptic problems.
+Indeed, these stabilization-free virtual element methods can be equivalently recast as
+primal mixed virtual element methods.
+We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free virtual element methods, and derive the optimal error estimates.
+
+The idea on constructing stabilization-free virtual element methods in this paper is simple,
+and can be extended to more virtual element methods and more partial differential equations.
 
@@
 \subsection{$H(\div)$-conforming finite elements}
-For polygon $K\in \mathcal T_h$ and $k\geq2$, let 
+For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
 $$
@@
 \begin{remark}\rm
-By introducing $\boldsymbol{\phi}_h=Q_{h,k-1}^{\div}\nabla_h u_h$, the virtual element method \eqref{eq:vem} can be rewritten as the following mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k-1}^{\rm div}$ and $u_h\in V_h$ such that
+By introducing $\boldsymbol{\phi}_h=Q_{h,k-1}^{\div}\nabla_h u_h$, the virtual element method \eqref{eq:vem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k-1}^{\rm div}$ and $u_h\in V_h$ such that
 \begin{equation*}

### 2022-05-30 stabfreevem.tex
proofread section 1

@@
 the analysis is rather elaborate. 
-This motives us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.
-
-The key to construct stabilization-free virtual element methods to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
+This motivates us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.
+
+The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
-To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and virtual element space $V_k(K)$ is modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
+To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
 Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

### 2022-06-12 stabfreevem.tex
update

@@
 
+\begin{figure}[htbp]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=5cm]{./figures/convex.pdf}
+%\caption{Numberical result of example with $\mathcal T_0$.}
+\end{minipage}%
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=5cm]{./figures/nonconvex.pdf}
+%\caption{[Numberical result of example with $\mathcal T_1$].}
+\end{minipage}%
+\centering
+\caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
+$\mathcal T_1$(right).}
+\label{fig:mesh}
+\end{figure}
+
 \section{Numerical examples}\label{sec:numericalexamps}
+In this section, we solve \eqref{eq:ellipitc2ndproblem} using the conforming
+virtual element method and the nonconforming virtual element method, 
+and give numerical results to verify convergence rates.
+
+\begin{example}\label{ex}
+    Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem}
+    on rectangular domain $\Omega = (0, 1)\times(0, 1)$, take $\alpha = 2$, 
+    the exact solution and source term are:
+    $$
+    u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y)
+    $$
+\end{example}
+
+The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
+$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
+as shown in Figure \ref{fig:mesh}. The numerical results for $k = 1, 2, 5$ are 
+listed in Figure \ref{fig:ncvemrate} \ref{fig:cvemrate}, 
+where the errors use $L^2$ norm and $H^1$-like norm. Both cases confirm the
+theoretic convergence rates.
+
+\begin{figure}[htbp]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/ncvemrate_convex.png}
+%\caption{Numberical result of example with $\mathcal T_0$.}
+\end{minipage}%
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/ncvemrate_noconvex.png}
+%\caption{[Numberical result of example with $\mathcal T_1$].}
+\end{minipage}%
+\centering
+\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
+of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:ncvemrate}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/cvemrate_convex.png}
+%\caption{Numberical result of example with $\mathcal T_0$.}
+\end{minipage}%
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/cvemrate_noconvex.png}
+%\caption{[Numberical result of example with $\mathcal T_1$].}
+\end{minipage}%
+\centering
+\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
+of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:cvemrate}
+\end{figure}
 

### 2022-06-13 stabfreevem.tex
update

@@
 \address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
- \email{...@xtu.edu.cn}%
+ \email{202131510114@smail.xtu.edu.cn}%
  \author{Xuehai Huang}%
@@
 $\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
-as shown in Figure \ref{fig:mesh}. The numerical results for $k = 1, 2, 5$ are 
-listed in Figure \ref{fig:ncvemrate} \ref{fig:cvemrate}, 
+as shown in Figure \ref{fig:mesh}. We use \eqref{eq:vem} and \eqref{eq:cfmvem} 
+respectively to compute Example \ref{ex}, the numerical results for $k = 1, 2, 5$ are 
+listed in Figure \ref{fig:rate1} \ref{fig:rate2}, 
 where the errors use $L^2$ norm and $H^1$-like norm. Both cases confirm the
-theoretic convergence rates.
+theoretical convergence rates.
 
@@
 \centering
-\includegraphics[width=6cm]{./figures/ncvemrate_convex.png}
+\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
 %\caption{Numberical result of example with $\mathcal T_0$.}
@@
 \centering
-\includegraphics[width=6cm]{./figures/ncvemrate_noconvex.png}
+\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
 %\caption{[Numberical result of example with $\mathcal T_1$].}
@@
 \centering
-\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
-of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
-\label{fig:ncvemrate}
+\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla_h u_h\|_0$ 
+of $H^1$-nonconforming virtual element method on 
+$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:rate1}
 \end{figure}
@@
 \centering
-\includegraphics[width=6cm]{./figures/cvemrate_convex.png}
+\includegraphics[width=6cm]{./figures/cvem_convex.pdf}
 %\caption{Numberical result of example with $\mathcal T_0$.}
@@
 \centering
-\includegraphics[width=6cm]{./figures/cvemrate_noconvex.png}
+\includegraphics[width=6cm]{./figures/cvem_nonconvex.pdf}
 %\caption{[Numberical result of example with $\mathcal T_1$].}
@@
 \centering
-\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{div}\nabla u_h\|_0$ 
-of Example \ref{ex} on $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
-\label{fig:cvemrate}
+\caption{Error $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{div}\nabla u_h\|_0$ 
+of $H^1$-conforming virtual element method  on $\mathcal T_0$(left) and 
+$\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:rate2}
 \end{figure}

### 2022-06-16 stabfreevem.tex
update numerical examples

--- 2022-05-30 stabfreevem.tex
@@
 
+\begin{figure}[htbp]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=5cm]{./figures/convex.pdf}
+%\caption{Numberical result of example with $\mathcal T_0$.}
+\end{minipage}%
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=5cm]{./figures/nonconvex.pdf}
+%\caption{[Numberical result of example with $\mathcal T_1$].}
+\end{minipage}%
+\centering
+\caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
+$\mathcal T_1$(right).}
+\label{fig:mesh}
+\end{figure}
+
 \section{Numerical examples}\label{sec:numericalexamps}
+In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
+virtual element method \eqref{eq:cfmvem}.
+
+% \begin{example}\label{ex}
+Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$
+on rectangular domain $\Omega = (0, 1)\times(0, 1)$. 
+The exact solution and source term are given by
+$$
+u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
+$$
+% \end{example}
+
+The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
+$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
+In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
+The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ mesh are shown in Figure \ref{fig:rate1}.
+We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
+And the numerical results of the conforming virtual element method \eqref{eq:vem} are presented in Figure \ref{fig:rate2}.
+Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
+theoretical convergence rate in Theorem~\ref{thm:errorestimateH1}.
+\begin{figure}[htbp]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
+%\caption{Numberical result of example with $\mathcal T_0$.}
+\end{minipage}%
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
+%\caption{[Numberical result of example with $\mathcal T_1$].}
+\end{minipage}%
+\centering
+\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
+of nonconforming virtual element method \eqref{eq:vem} on 
+$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:rate1}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/cvem_convex.pdf}
+%\caption{Numberical result of example with $\mathcal T_0$.}
+\end{minipage}%
+\begin{minipage}[t]{0.49\linewidth}
+\centering
+\includegraphics[width=6cm]{./figures/cvem_nonconvex.pdf}
+%\caption{[Numberical result of example with $\mathcal T_1$].}
+\end{minipage}%
+\centering
+\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0$ 
+of conforming virtual element method \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
+$\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:rate2}
+\end{figure}
 

### 2022-06-16 ex_shared.tex
add sinum version

% SIAM Shared Information Template
% This is information that is shared between the main document and any
% supplement. If no supplement is required, then this information can
% be included directly in the main document.

% Packages and macros go here
\usepackage{lipsum}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithmic}

\usepackage{amssymb}
\usepackage{amsmath,amscd}
\usepackage{mathrsfs}
\usepackage{stmaryrd}
\usepackage{chemarrow}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[all]{xy}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
% \usepackage[hyperpageref]{backref}

\ifpdf
  \DeclareGraphicsExtensions{.eps,.pdf,.png,.jpg}
\else
  \DeclareGraphicsExtensions{.eps}
\fi

% theorems
% \newtheorem{theorem}{Theorem}[section]
% \newtheorem{lemma}[theorem]{Lemma}
% \newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{proposition}[theorem]{Proposition}
% \newtheorem{definition}[theorem]{Definition}
% \newtheorem{example}[theorem]{Example}
% \newtheorem{exercise}[theorem]{Exercise}
% \newtheorem{question}[theorem]{Question}
% % \newtheorem{remark}[theorem]{Remark}
% \newtheorem{assumption}[theorem]{Assumption}
% \newtheorem{alg}[theorem]{Algorithm}

\DeclareMathOperator*{\img}{img}
%\DeclareMathOperator*{\span}{span}
\newcommand{\sign}{\operatorname{sign}}
\newcommand{\curl}{\operatorname{curl}}
\renewcommand{\div}{\operatorname{div}}
%\renewcommand{\grad}{\operatorname{grad}}
\newcommand{\grad}{\operatorname{grad}}
\newcommand{\tr}{\operatorname{tr}}
% \DeclareMathOperator*{\tr}{tr}
\DeclareMathOperator*{\rot}{rot}
\DeclareMathOperator*{\var}{Var}
\newcommand{\dev}{\operatorname{dev}}
\newcommand{\sym}{\operatorname{sym}}
\newcommand{\skw}{\operatorname{skw}}
\newcommand{\spn}{\operatorname{spn}}
\newcommand{\mspn}{\operatorname{mspn}}
\newcommand{\mskw}{\operatorname{mskw}}
\newcommand{\vskw}{\operatorname{vskw}}
\newcommand{\vspn}{\operatorname{vspn}}
\newcommand{\defm}{\operatorname{def}}
\newcommand{\hess}{\operatorname{hess}}

% Add a serial/Oxford comma by default.
\newcommand{\creflastconjunction}{, and~}

% Used for creating new theorem and remark environments
\newsiamremark{remark}{Remark}
\newsiamremark{hypothesis}{Hypothesis}
\crefname{hypothesis}{Hypothesis}{Hypotheses}
\newsiamthm{claim}{Claim}

% Sets running headers as well as PDF title and authors
\headers{Stabilization-Free VEM}{C. Chen, X. Huang and H. Wei}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
\title{Stabilization-Free Virtual Element Methods\thanks{\today
\funding{The second author is the corresponding author. The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500. The first and third authors were supported by NSFC (11871413) and in part by projects
of Education Department of Hunan Provincial of China (19B534, 19A500).}}}

\author{Chunyu Chen\thanks{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China 
  (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).}
\and Xuehai Huang\thanks{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China (\email{huang.xuehai@sufe.edu.cn}).}
\and Huayi Wei\footnotemark[2]
}

\usepackage{amsopn}
\DeclareMathOperator{\diag}{diag}

%%% Local Variables: 
%%% mode:latex
%%% TeX-master: "ex_article"
%%% End:

### 2022-06-16 stabfreevem_sinum.tex
add sinum version

--- 2022-06-16 stabfreevem.tex
@@
-\documentclass[10pt]{amsart}
-%\input{/Dropbox/Math/TexDocument/mysetting.tex}
-%\input{mysetting.tex}
-
-\usepackage{amssymb}
-\usepackage[leqno]{amsmath}
-\usepackage{mathrsfs}
-\usepackage{stmaryrd}
-\usepackage{chemarrow}
-\usepackage[norelsize]{algorithm2e}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage[pdftex,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=blue,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
-%\usepackage[dvips,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=red,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
-\usepackage[all]{xy}
-\usepackage{tikz}
-\usetikzlibrary{arrows}
-
-\usepackage{multirow}
-\usepackage[hyperpageref]{backref}
-
-% comments
-%\newcommand{\LC}[1]{\textcolor{cyan}{#1}}
-\newcommand{\LC}[1]{\textcolor{red}{#1}}
-\newcommand{\XH}[1]{\textcolor{red}{#1}}
-%\usepackage[pdftex,colorlinks=true,citecolor=myBlue,linkcolor=myBlue]{hyperref}
-
-  \newcounter{mnote}
-  \setcounter{mnote}{0}
-  \newcommand{\mnote}[1]{\addtocounter{mnote}{1}
-    \ensuremath{{}^{\bullet\arabic{mnote}}}
-    \marginpar{\footnotesize\em\color{red}\ensuremath{\bullet\arabic{mnote}}#1}}
-  \let\oldmarginpar\marginpar
-    \renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%
-    {\raggedright\footnotesize #1}}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{question}[theorem]{Question}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{alg}[theorem]{Algorithm}
-
-\newcommand{\dx}{\,{\rm d}x}
-\newcommand{\dd}{\,{\rm d}}
-\newcommand{\bs}{\boldsymbol}
-\newcommand{\mcal}{\mathcal}
-
-\DeclareMathOperator*{\img}{img}
-%\DeclareMathOperator*{\span}{span}
-\newcommand{\curl}{\operatorname{curl}}
-\renewcommand{\div}{\operatorname{div}}
-%\renewcommand{\grad}{\operatorname{grad}}
-\newcommand{\grad}{\operatorname{grad}}
-\DeclareMathOperator*{\tr}{tr}
-\DeclareMathOperator*{\rot}{rot}
-\DeclareMathOperator*{\var}{Var}
-\newcommand{\dev}{\operatorname{dev}}
-\newcommand{\sym}{\operatorname{sym}}
-\newcommand{\skw}{\operatorname{skw}}
-\newcommand{\spn}{\operatorname{spn}}
-\numberwithin{equation}{section}
+% SIAM Article Template
+\documentclass[review,hidelinks,onefignum,onetabnum]{siamart220329}
+
+% Information that is shared between the article and the supplement
+% (title and author information, macros, packages, etc.) goes into
+% ex_shared.tex. If there is no supplement, this file can be included
+% directly.
+
+\input{ex_shared}
+
+% Optional PDF information
+\ifpdf
+\hypersetup{
+  pdftitle={Robust Mixed Methods for Quad-Curl Perturbation Problem},
+  pdfauthor={X. Huang and C. Zhang}
+}
+\fi
+
+% The next statement enables references to information in the
+% supplement. See the xr-hyperref package for details.
+
+% \externaldocument[][nocite]{ex_supplement}
+
+% FundRef data to be entered by SIAM
+%<funding-group specific-use="FundRef">
+%<award-group>
+%<funding-source>
+%<named-content content-type="funder-name"> 
+%</named-content> 
+%<named-content content-type="funder-identifier"> 
+%</named-content>
+%</funding-source>
+%<award-id> </award-id>
+%</award-group>
+%</funding-group>
 
 \begin{document}
-\title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
-\author{Chunyu Chen}%
-\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
- \email{202131510114@smail.xtu.edu.cn}%
- \author{Xuehai Huang}%
- \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
- \email{huang.xuehai@sufe.edu.cn}%
-\author{Huayi Wei}%
-\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
- \email{weihuayi@xtu.edu.cn}%
-
- \thanks{The second author is the corresponding author.
-The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.}
- \thanks{The first and third authors were supported by NSFC (11871413) and in part by projects
-of Education Department of Hunan Provincial of China (19B534, 19A500).}
-
-\makeatletter
-\@namedef{subjclassname@2020}{\textup{2020} Mathematics Subject Classification}
-\makeatother
-\subjclass[2020]{
-%65F10;   %% Iterative numerical methods for linear systems
-% 58J10;   %%  Differential complexes [See also 35Nxx]; elliptic complexes
-65N12;   %%  Stability and convergence of numerical methods for boundary value problems involving PDEs;
-% 65N15;   %%  Error bounds for boundary value problems involving PDEs
-65N22;   %%  Numerical solution of discretized equations for boundary value problems involving PDEs;
-65N30;   %%  Finite element, Rayleigh-Ritz and Galerkin methods for boundary value problems involving PDEs;
-%65N55;   %%  Multigrid methods; domain decomposition for boundary value problems involving PDEs;
-% 15A69;   %%  Multilinear algebra, tensor calculus
-% 15A72;   %%  Vector and tensor algebra, theory of invariants [See also 13A50, 14L24]
-}
-
+
+\maketitle
+
+% REQUIRED
 \begin{abstract}
@@
 
-\keywords{Virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis}
-
-\maketitle
-
-% \tableofcontents
+% REQUIRED
+\begin{keywords}
+virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis
+\end{keywords}
+
+% REQUIRED
+\begin{MSCcodes}
+65N12, 65N22, 65N30
+\end{MSCcodes}
 
@@
 While only
-$$
+\[
 \|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
-$$
+\]
 hold
@@
 For a piecewise smooth function $v$, define 
-$$
+\[
 \|v\|_{1,h}^2:=\sum_{K\in\mathcal T_h}\|v\|_{1,K}^2,\quad |v|_{1,h}^2:=\sum_{K\in\mathcal T_h}|v|_{1,K}^2.
-$$
+\]
 
@@
 On face $F\in\mathcal F_h$, define surface divergence
-$$
+\[
 \div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
-$$
+\]
 For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.
@@
 Set
-$$
+\[
 \mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
-$$
+\]
 
@@
 For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
-$$
-\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
-$$ 
+\[
+\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
+\] 
 be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
@@
 We also need the lowest order Raviart-Thomas (RT) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}
-$$
-\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
-$$
+\[
+\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
+\]
 Define $\mathring{\boldsymbol{V}}^{RT}(K):=\boldsymbol{V}^{RT}(K)\cap \boldsymbol{H}_0(\div, K)$.
@@
 Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
-$$
+\[
 \skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
-$$
+\]
 By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
@@
 On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
-$$
+\[
 \dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
-$$
+\]
 Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
@@
 Then
-$$
+\[
 \skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=\pm\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}).
-$$
+\]
 \end{lemma}
@@
 \end{pmatrix}$. Hence
-$$
+\[
 2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=2{\rm det}(H)\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}),
-$$
+\]
 which ends the proof.
@@
 for some $q_{ij}\in\mathbb P_{k-2}(T)$.
-Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ is the basis of $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
-$$
+Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ is the basis of antisymmetric matrice space $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
+\[
 \boldsymbol{N}_{ij}:\skw({\boldsymbol n_l\boldsymbol n_m^{\intercal}})=\delta_{il}\delta_{jm},\quad 1\leq i<j\leq d,\; 1\leq l<m\leq d.
-$$
+\]
 \end{lemma}
@@
 On the other side, assume $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$. Express $\boldsymbol{\tau}$ as 
-$$
+\[
 \boldsymbol{\tau}=\sum_{1\leq i<j\leq d}p_{ij}\boldsymbol{N}_{ij},
-$$
+\]
 where $p_{ij}=\boldsymbol{n}_i^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_j\in\mathbb P_{k}(T)$.
@@
 Thanks to DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element, we acquire from DoF \eqref{eq:-2formfemdof31} and $\div\div\boldsymbol{\tau}=0$ that $\div\boldsymbol{\tau}=\boldsymbol{0}$, which together with DoF \eqref{eq:-2formfemdof32} and decomposition \eqref{eq:Pkskwtensordecomp} gives
-$$
+\[
 (\boldsymbol{\tau}, \boldsymbol{q})_T=0  \quad \forall~\boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K).
-$$
+\]
 Applying Lemma~\ref{lem:PkKbubblecharac}, $\boldsymbol{\tau}$ has the expression as in \eqref{eq:PkKbubblecharac}.
@@
 \begin{align*}  
-\boldsymbol{V}_{k}^{d-2}(K):=\{\boldsymbol{\tau}\in\bs L^2(K;\mathbb K)&: \boldsymbol{\tau}|_{T}\in \mathbb P_{k}(T;\mathbb K) \textrm{ for each } T\in\mathcal T_K, \\
+\boldsymbol{V}_{k}^{d-2}(K):=\{\boldsymbol{\tau}\in\boldsymbol{L}^2(K;\mathbb K)&: \boldsymbol{\tau}|_{T}\in \mathbb P_{k}(T;\mathbb K) \textrm{ for each } T\in\mathcal T_K, \\
 &\;\;\textrm{ all the DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof22} are single-valued}\}.
@@
 are exact, where $\mathring{V}_{k-2}^{L^2}(K):=V_{k-2}^{L^2}(K)/\mathbb R$, and
-$$
+\[
 V_{k-2}^{L^2}(K):=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for each } T\in\mathcal T_K\}.
-$$
+\]
 \end{lemma}
@@
 Thanks to DoF \eqref{eq:-2formfemdof1}, it follows from the integration by parts that
-$$
+\[
 (\div_F(\boldsymbol{\sigma}\boldsymbol{n}), 1)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, 1)_F\quad\forall~F\in\mathcal F(\mathcal T_K),
-$$
+\]
 which together with \eqref{eq:20220324-3} and DoF \eqref{eq:-2formfemdof21} that
-$$
+\[
 (\boldsymbol{n}^{\intercal}\div\boldsymbol{\sigma}, q)_F = (\div_F(\boldsymbol{\sigma}\boldsymbol{n}), q)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F\quad\forall~q\in \mathbb P_{k-1}(F),F\in\mathcal F(\mathcal T_K).
-$$
+\]
 Therefore, due to DoF \eqref{eq:-2formfemdof31} and the fact $\div\div\boldsymbol{\sigma}=\div\boldsymbol{v}=0$,
@@
 define shape function space
-$$
+\[
 \boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
-$$
-for $k\geq 2$, and $$
+\]
+for $k\geq 2$, and 
+\[
 \boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{RT}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
-$$
+\]
 Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{RT}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$ for $k\geq2$.
@@
     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
-    (\boldsymbol{\phi}, \bs q)_K & \quad\forall~\bs q\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)=\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vdivdof3}
+    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)=\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vdivdof3}
 \end{align}
@@
 When $K$ is a simplex and $\mathcal T_K=\{K\}$, thanks to DoF \eqref{BDMdof3} for the BDM element, DoF \eqref{Vdivdof3} can be replaced by 
-$$
-(\boldsymbol{\phi}, \bs q)_K \quad\forall~\bs q\in \mathbb P_{k-3}(K;\mathbb K)\boldsymbol{x}
-$$
+\[
+(\boldsymbol{\phi}, \boldsymbol{q})_K \quad\forall~\boldsymbol{q}\in \mathbb P_{k-3}(K;\mathbb K)\boldsymbol{x}
+\]
 for $k\geq3$.
@@
 \end{equation}
-$$
+\[
 \|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
 \leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\quad\forall~T\in\mathcal T_K.
-$$
+\]
 Then let $w\in H^1(K)/\mathbb R$ be the solution of 
-$$
+\[
 \begin{cases}
@@
 \end{cases}
-$$
+\]
 The weak formulation is
-$$
+\[
 (\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)/\mathbb R.
-$$
+\]
 Obviously we have
-$$
+\[
 \|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-$$
+\]
 Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}.
@@
 Let 
-$$
+\[
 \mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
-$$
+\]
 Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
@@
     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
-    (\boldsymbol{\phi}, \bs q)_K & \quad\forall~\bs q\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
+    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
 \end{align}
@@
 Apply the integration by parts to get
-$$
+\[
 |v|_{1,K}^2=-(\Delta v,v)_K+(\partial_nv,v)_{\partial K}\leq\|\Delta v\|_{0,K}\|v\|_{0,K}+\|\partial_nv\|_{0,\partial K}\|v\|_{0,\partial K}.
-$$
+\]
 By $h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}$, i.e. (A.3)-(A.4) in \cite{ChenHuang2020ncvem}, we obtain
-$$
+\[
 |v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
-$$
+\]
 which together with the multiplicative trace inequality yields \eqref{eq:veminverse}.
@@
 which combined with the inverse inequality for polynomials implies
-$$%\label{eq:VEMnormequivalencePiK}
+\[%\label{eq:VEMnormequivalencePiK}
 h_K^2|\Pi_k^Kv|_{1,K}^2\lesssim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2. 
-$$
+\]
 Thanks to the Poincar\'e-Friedrichs inequality \cite[(2.15)]{BrennerSung2018} and \eqref{eq:projlocal2d2},
@@
 Applying the similar argument as in Lemma \ref{lem:veminverse}, we obtain
-$$
+\[
 h_K^2|v|_{1,K}^2\lesssim \|Q_k^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2.
-$$
+\]
 Then it follows from \eqref{eq:VEMnormequivalenceQK} that
-$$
+\[
 \|v\|_{0,K}^2\lesssim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2.
-$$
+\]
 The other side $\|Q_{k-2}^Kv\|_{0,K}^2+\sum\limits_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2\lesssim \|v\|_{0,K}^2$ holds from the trace inequality and the inverse inequality \eqref{eq:veminverse}.
@@
 (\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \\
-(\boldsymbol{\phi}, \bs q)_K&=0  \qquad\qquad\qquad\forall~\bs q\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K). 
+(\boldsymbol{\phi}, \boldsymbol{q})_K&=0  \qquad\qquad\qquad\forall~\boldsymbol{q}\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K). 
 \end{align*}
@@
 Then we obtain from the norm equivalence \eqref{eq:Vknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
-$$
+\[
 \|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|v\|_{0,K}\lesssim \|\nabla v\|_{0,K}.    
-$$
+\]
 Finally we conclude \eqref{eq:localdiscreteinfsup} from \eqref{eq:20220204} and the last inequality.
@@
 where the discrete bilinear form 
-$$
+\[
 a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
-$$
+\]
 
@@
 Due to \eqref{eq:gradVknormequivalence}, we have
-$$
+\[
 \sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
-$$
+\]
 which implies the coercivity \eqref{eq:ahcoercivity}.
@@
 Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
-$$
+\[
 a(u,v_h-u_h)+(f, v_h-u_h)\lesssim h^k|u|_{k+1}|v_h-u_h|_{1,h}.
-$$
+\]
 Then 
@@
 which implies
-$$
+\[
 |v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_{h,k-1}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
-$$
+\]
 Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k-1}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
@@
 Similarly, we have
-$$
+\[
 \|u-Q_hv_h\|_0\leq \|u-Q_hu\|_0+\|Q_h(u-v_h)\|_0\leq \|u-Q_hu\|_0+\|u-v_h\|_0.
-$$
+\]
 By combining the last three inequalities, we obtain
-$$
+\[
 |v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|u-v_h\|_{1,h},
-$$
+\]
 which together with the triangle inequality yields
-$$
+\[
 |u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\inf_{v_h\in V_h}\|u-v_h\|_{1,h}.
-$$
+\]
 At last, \eqref{eq:errorestimateH1} follows from the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
@@
 % (\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{k-1}(K)/\mathbb R, \\
-% (\boldsymbol{\phi}, \bs q)_K&=0  \qquad\qquad\qquad\forall~\bs q\in \curl\mathring{V}_{k+1}^{\grad}(K). 
+% (\boldsymbol{\phi}, \boldsymbol{q})_K&=0  \qquad\qquad\qquad\forall~\boldsymbol{q}\in \curl\mathring{V}_{k+1}^{\grad}(K). 
 % \end{align*}
@@
 Define the global conforming virtual element space
-$$
+\[
 V_h:=\{v_h\in H_0^1(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h\}.
-$$
+\]
 
@@
 where the discrete bilinear form 
-$$
+\[
 a_h(u_h, v_h):=(Q_{h,k}^{\div}\nabla u_h, Q_{h,k}^{\div}\nabla v_h)+\alpha(Q_hu_h, Q_hv_h).
-$$
+\]
 
@@
 Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
-$$
+\[
 \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
-$$
-$$
+\]
+\[
 a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
-$$
+\]
 Combining the last two inequalities gives
-$$
+\[
 a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
-$$
+\]
 By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
@@
 By the arbitrariness of $v_h\in V_h$, we derive
-$$
+\[
 |u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
-$$
+\]
 At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
@@
 The exact solution and source term are given by
-$$
+\[
 u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
-$$
+\]
 % \end{example}
@@
 
-\bibliographystyle{abbrv}
+% \section*{Acknowledgments}
+% We would like to acknowledge the assistance of volunteers in putting
+% together this example manuscript and supplement.
+
+\bibliographystyle{siamplain}
 \bibliography{./paper}

### 2022-06-18 stabfreevem.tex
update

@@
 \end{enumerate}
-We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$.
-The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
-In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
-While only
+We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
+inner product $(\cdot, \cdot)_K$. The norm equivalence
+\eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be
+sufficiently large compared with the virtual element space $V_k(K)$.  In
+standard virtual element methods, $Q_{k-1}^{K}\nabla v$
+\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
+\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
+are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
+$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
+$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
+space $\mathbb P_{k}(K)$.  While only
 $$
@@
 To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
-
-We first construct $H(\div)$-conforming macro finite elements based on a simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension.
-The shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$th order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition $\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element space for $k=0$, with some constraints.
-To ensure the $L^2$ projection $Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable for virtual element function $v\in V_k(K)$, we require $\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and $\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.
-Based on these considerations and the direct decomposition of an $H(\div)$-conforming macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the $L^2$ norm equivalence.
-By the way, we use the matrix-vector language to review a conforming finite element for differential $(d-2)$-form in \cite{ArnoldFalkWinther2006,Arnold2018}.
+Instead, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
+
+We first construct $H(\div)$-conforming macro finite elements based on a
+simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
+shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$th
+order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
+$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
+space for $k=0$, with some constraints. To ensure the $L^2$ projection
+$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
+for virtual element function $v\in V_k(K)$, we require
+$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
+$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
+is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
+these considerations and the direct decomposition of an $H(\div)$-conforming
+macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
+the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
+$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
+a conforming finite element for differential $(d-2)$-form in
+\cite{ArnoldFalkWinther2006,Arnold2018}.
 
@@
 virtual element method \eqref{eq:cfmvem}.
+All of the numerical examples are implemented by using the FEALPy package \cite{fealpy}
 

### 2022-06-18 stabfreevem.tex
update

@@
 The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.}
- \thanks{The first and third authors were supported by NSFC (11871413) and in part by projects
-of Education Department of Hunan Provincial of China (19B534, 19A500).}
+ \thanks{The first and third authors were supported by NSFC (11871413).}
 
@@
 simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
-shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$th
+shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
 order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
@@
 virtual element method \eqref{eq:cfmvem}.
-All of the numerical examples are implemented by using the FEALPy package \cite{fealpy}
+The numerical example is implemented by using the FEALPy package \cite{fealpy}
 

### 2022-06-19 stabfreevem.tex
proofreading

@@
 space $\mathbb P_{k}(K)$.  While only
-$$
+\[
 \|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
-$$
+\]
 hold
@@
 
-% $$
+% \[
 % \|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
-% $$
+% \]
 
@@
 For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
-For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit outward normal vector to $\partial F$.
+For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit vector outward normal to $\partial F$ but parallel to $F$.
 
@@
 For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
-$$
-\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
-$$ 
+\[
+\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
+\]
 be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
@@
 \begin{equation}\label{eq:Pkskwtensordecomp}  
-\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big).
-\end{equation}
+\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big),
+\end{equation}
+where $\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})$ means the kernel of operator $\boldsymbol{x}: \mathbb P_{k-2}(T;\mathbb K)\to\mathbb P_{k-1}(T;\mathbb R^d)$.
 \end{lemma}
@@
 for some $q_{ij}\in\mathbb P_{k-2}(T)$.
-Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ is the basis of $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
-$$
+Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ denotes the basis of $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
+\[
 \boldsymbol{N}_{ij}:\skw({\boldsymbol n_l\boldsymbol n_m^{\intercal}})=\delta_{il}\delta_{jm},\quad 1\leq i<j\leq d,\; 1\leq l<m\leq d.
-$$
+\]
 \end{lemma}
@@
 Let 
-$$
+\[
 \mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
-$$
-Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
+\]
+Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
 \begin{align}
@@
 % Due to \eqref{eq:cfmgradVknormequivalence}, we have
-% $$
+% \[
 % \sum_{K\in\mathcal T_h}\|\nabla v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
-% $$
+% \]
 % which implies the coercivity \eqref{eq:cfmahcoercivity}.
@@
 \subsection{Error analysis}
-\begin{theorem}
+\begin{theorem}\label{thm:cfmerrorestimateH1}
 Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:cfmvem}.
@@
 
-\section{Numerical examples}\label{sec:numericalexamps}
+\section{Numerical results}\label{sec:numericalexamps}
 In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
@@
 We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
-And the numerical results of the conforming virtual element method \eqref{eq:vem} are presented in Figure \ref{fig:rate2}.
+And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Figure \ref{fig:rate2}.
 Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
-theoretical convergence rate in Theorem~\ref{thm:errorestimateH1}.
+theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
 \begin{figure}[htbp]

### 2022-06-19 stabfreevem_sinum.tex
proofreading

@@
 \end{enumerate}
-We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$.
-The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
-In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
-While only
+We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
+inner product $(\cdot, \cdot)_K$. The norm equivalence
+\eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be
+sufficiently large compared with the virtual element space $V_k(K)$.  In
+standard virtual element methods, $Q_{k-1}^{K}\nabla v$
+\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
+\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
+are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
+$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
+$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
+space $\mathbb P_{k}(K)$.  While only
 \[
@@
 To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
-
-We first construct $H(\div)$-conforming macro finite elements based on a simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension.
-The shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$th order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition $\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element space for $k=0$, with some constraints.
-To ensure the $L^2$ projection $Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable for virtual element function $v\in V_k(K)$, we require $\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and $\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.
-Based on these considerations and the direct decomposition of an $H(\div)$-conforming macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the $L^2$ norm equivalence.
-By the way, we use the matrix-vector language to review a conforming finite element for differential $(d-2)$-form in \cite{ArnoldFalkWinther2006,Arnold2018}.
-
-% $$
+Instead, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
+
+We first construct $H(\div)$-conforming macro finite elements based on a
+simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
+shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
+order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
+$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
+space for $k=0$, with some constraints. To ensure the $L^2$ projection
+$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
+for virtual element function $v\in V_k(K)$, we require
+$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
+$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
+is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
+these considerations and the direct decomposition of an $H(\div)$-conforming
+macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
+the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
+$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
+a conforming finite element for differential $(d-2)$-form in
+\cite{ArnoldFalkWinther2006,Arnold2018}.
+
+% \[
 % \|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
-% $$
+% \]
 
@@
 for some $q_{ij}\in\mathbb P_{k-2}(T)$.
-Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ is the basis of antisymmetric matrice space $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
+Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ denotes the basis of $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
 \[
@@
 \]
-Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
+Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
 \begin{align}
@@
 
-\section{Numerical examples}\label{sec:numericalexamps}
+\section{Numerical results}\label{sec:numericalexamps}
 In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
 virtual element method \eqref{eq:cfmvem}.
+The numerical example is implemented by using the FEALPy package \cite{fealpy}
 

### 2023-01-19 stabfreevem_sinum.tex
typo
add referee's reports

@@
 \hypersetup{
-  pdftitle={Robust Mixed Methods for Quad-Curl Perturbation Problem},
-  pdfauthor={X. Huang and C. Zhang}
+  pdftitle={Stabilization-Free Virtual Element Methods},
+  pdfauthor={C. Chen, X. Huang and H. Wei}
 }
@@
 \begin{keywords}
-virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis
+virtual element, stabilization-free, macro finite element, norm equivalence, error analysis
 \end{keywords}

### 2023-01-25 reports/response.tex
initial response

% ----------------------------------------------------------------
% AMS-LaTeX Paper ************************************************
% **** -----------------------------------------------------------
\documentclass[10pt]{amsart}
%\textwidth 14.5cm
%\textheight 22cm
%\hoffset -1.5cm
%\voffset -2.2cm
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{color}
\usepackage{stmaryrd}
\usepackage{chemarrow}
\usepackage[all]{xy}
\usepackage[pdftex,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=blue,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}

%\usepackage{mathabx}
% ----------------------------------------------------------------
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small
% THEOREMS -------------------------------------------------------
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
%\numberwithin{equation}{section}
% MATH -----------------------------------------------------------
\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\Real}{\mathbb R}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
\newcommand{\BX}{\mathbf{B}(X)}
\newcommand{\A}{\mathcal{A}}

\newcommand{\dx}{\,{\rm d}x}
\newcommand{\dd}{\,{\rm d}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\mcal}{\mathcal}

\DeclareMathOperator*{\img}{img}
%\DeclareMathOperator*{\span}{span}
\newcommand{\sign}{\operatorname{sign}}
\newcommand{\curl}{\operatorname{curl}}
\renewcommand{\div}{\operatorname{div}}
%\renewcommand{\grad}{\operatorname{grad}}
\newcommand{\grad}{\operatorname{grad}}
\newcommand{\tr}{\operatorname{tr}}
% \DeclareMathOperator*{\tr}{tr}
\DeclareMathOperator*{\rot}{rot}
\DeclareMathOperator*{\var}{Var}
\newcommand{\dev}{\operatorname{dev}}
\newcommand{\sym}{\operatorname{sym}}
\newcommand{\skw}{\operatorname{skw}}
\newcommand{\spn}{\operatorname{spn}}
\newcommand{\mspn}{\operatorname{mspn}}
\newcommand{\mskw}{\operatorname{mskw}}
\newcommand{\vskw}{\operatorname{vskw}}
\newcommand{\vspn}{\operatorname{vspn}}
\newcommand{\defm}{\operatorname{def}}
\newcommand{\hess}{\operatorname{hess}}
% ----------------------------------------------------------------
\begin{document}

\title{\large Detailed Response to Referees}%

\date{}%
%\dedicatory{}%
%\commby{}%
% ----------------------------------------------------------------

\maketitle

The authors greatly appreciate the questions and concerns the reviewers have raised in the report, as well as the careful reading that has fixed our grammatical errors. Other than some single word typos, important changes are highlighted in colored texts in this revision.

\tableofcontents

%We thank the Referee for the valuable comments that helped us to improve the manuscript. In
%the revised version of the manuscript, all non-minor modifications are highlighted in red colour.
%Below, we address the points raised in the report.

\vskip0.5cm
\section{Response to Reviewer 1}
\begin{enumerate}[1.]

\item \textsf{The English presentation is unfortunately very dodgy and should be revised before any type of resubmission.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{An important question is whether you have in mind specific occasions where stabilization free virtual elements are superior to stabilized ones. More precisely, your procedure is sensibly more expensive and complicated than that of the standard VEM: you need a simplicial tessellation of each element; you project on BDM-type polynomial spaces; the theoretical setting itself is rather involved. If there are no apparent advantages in some specific occasion, the stabilization-free approach seems to be rather lame.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Lines 17-18; when you discuss the results in references [9,10,20], I am not quite sure that the polynomial degree of the projection depends only on the number of vertices. In fact, in an updated version of the preprint [19], it is possible to see that also the shape of the polygon plays a role in the choice of such a polynomial degree.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 22; ``arbitrary dimension'' only refers to the nonconforming version of the scheme. Please, better highlight this fact.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{I appreciate the fact that you “preview” equation (1.1) in the introduction, as it is the lynchpin of the forthcoming analysis. Yet, it would be beneficial a brief comment on the hidden constants. For instance, you should state on what such constants depend on.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Lines 41-43; you should underline that the polynomial spaces onto which you project are based on a regular simplicial tessellation of the elements of the mesh.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Lines 50-51; when you define the function $\phi$, are you sure that the normal component of the trace is a polynomial only on the faces of $K$? Don't you also need this property to be valid on the faces of the simplicial tessellation of $K$?.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 138; you may wish to recall the degrees of freedom of this space, even though they are well known.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 305; reference [21, Lemma 10] for the polynomial inverse inequality is not proper; in fact, the inverse estimate follows from standard polynomial inverse estimates on simplices (refer, e.g., to Verf{\"u}rth's book), the regularity of the element, and standard polynomial inverse estimates.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 305; reference [11, (2.18)] is also a standard scaled trace inequality (refer to any PDE textbook).}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 308-309; you also use the definition of negative norm (which I cannot find), an integration by parts, and a Cauchy-Schwarz inequality.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 310; “other side” $-\!\!\!-\!\!\!-\!\!\!>$“lower bound”.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Lines 311-312; are you sure about the definition of $\phi_1$? What about the degrees of freedom on internal faces?}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Elaborate more the equivalence (3.26).}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{You should write that the eq. in 322 is proven based on the inequality on lines 315-316.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 323; the operator $I_K^{\div}$ should be defined explicitly.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Eq. (3.28); can you elaborate more on the first inequality? Moreover, the second inequality follows from the bound on line 322; you should underline this.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{After line 336, can you state the difference between the space defined on line 336 and that on line 263?.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{The definition of the DoFs in eqs. (4.3) and (4.4) is wrong: you should first pick bases of bulk and face polynomial spaces and define the moments accordingly.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 381; the space $\mathbb P_p\backslash\mathbb P_{p-2}$ is not defined as an orthogonal complement, but rather as any completion of the smaller space into the larger one. The two definitions are equivalent if you use orthogonal polynomial bases, which I humbly think is not what you are actually doing.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{You may wish to shorten up or even remove the proof of Lemma 4.1, which is standard in the virtual element literature.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 406; “inequality”$-\!\!\!-\!\!\!>$“inequalities”; moreover, mention that you use both $H^1$-$L^2$ and $L^2$ boundary-$L^2$ bulk inverse inequalities.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 408; is [11, (2.15)] the proper reference for the Poincar\'e-Friedrichs inequality? I think is a standard result and you may wish to cite any standard PDE book.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Eq. (4.12); if you complete the sequence of identities and inequalities with $h_k^2|v|_{1,K}^2$, you get indeed a norm equivalence (and not only an upper bound).}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Lines 445 and 456; explain from where the term $Q_0^k(\div\phi)$ appears.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Provide more details on the inequality on lines 457-458.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Eq. (4.16); why do you cite [15, (4.16)]? It probably follows from [Brenner, SINUM 2003] and the definition of the nonconforming space.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 484; the first inequality is probably a “$\approx$”.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 486; “uni-solvent”$-\!\!\!-\!\!\!>$“well posed”?}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{The definition of the DoFs in eqs. (5.1), (5.2), and (5.3) is wrong: you should first pick bases of bulk and face polynomial spaces and define the moments accordingly.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{You may wish to reduce or even drop the proof or Theorem 5.3, which appears to be a standard Strang-type result for the VEM.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the numerical section, I agree that it is important to check the rate of convergence of the method.
However, the convergence does not automatically guarantee the invertibility of the local stiffness matrices, as imposing the Dirichlet boundary conditions may have a “stabilizing effect”. So, you should investigate the number of zero eigenvalues of the local stiffness matrix.\\
For instance, pick three different hexagonal elements with a fixed degree of accuracy, e.g., k = 3: the first being a regular hexagon; the second being a quasi-regular hexagon (small perturbation of the previous element); the third being a square with an edge containing two hanging nodes. Check whether the stiffness matrix always has only one zero eigenvalue, i.e., the method is indeed stabilization free.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{My feeling is that the proposed stabilization-free approach is much more expensive than the standard one. Thus, you should check the assembling time of the stabilization-free and standard VEMs, on: ($i$) a (reasonably large) sequence of meshes; ($ii$) fixing a mesh, increasing the degree of accuracy, e.g., up to $k = 10$.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Along the same avenue, you should also compare the condition number of the global matrices obtained with the two approaches in the two situations ($i$) and ($ii$) above. Furthermore, you may also wish to consider sequences of meshes with “collapsing elements” (refine a mesh and change the aspect ratio), and check the condition numbers again. As a suggestion, since the condition number should be computed scaling the diagonal of the matrix, you can empirically check such conditioning by testing the two approaches on a patch test. The conditioning can be estimated checking the growth of the error for the patch test.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Minor issues (I will not highlight all the typos but only few of them as an example):
\begin{itemize}
\item line 3; “Poisson”$-\!\!\!-\!\!\!>$“the Poisson”;
\item line 24; “space”$-\!\!\!-\!\!\!>$“the space”;
\item line 31; “space”$-\!\!\!-\!\!\!>$“that the space”;
\item line 43; “usual”$-\!\!\!-\!\!\!>$“the usual”;
\item line 49; “space”$-\!\!\!-\!\!\!>$“the space”;
\item line 68; “. And”$-\!\!\!-\!\!\!>$“and”;
\item line 81; “banach”$-\!\!\!-\!\!\!>$“Banach”;
\item line 82; “and $\mathbb K$, where $\mathbb K$”$-\!\!\!-\!\!\!>$“and $\mathbb K$”; 
\item line 105; “surface”$-\!\!\!-\!\!\!>$“the surface”;
\item line 107; “smooth”$-\!\!\!-\!\!\!>$“a smooth”;
\item line 262; “shape”$-\!\!\!-\!\!\!>$“the shape”;
\item line 347; “discrete”$-\!\!\!-\!\!\!>$“the discrete”;
\item lines 465-466; “DoF”$-\!\!\!-\!\!\!>$“DoFs”; “is”$-\!\!\!-\!\!\!>$“are”; “vanishes”$-\!\!\!-\!\!\!>$“vanish”; 
\item line 511; “inequlities”$-\!\!\!-\!\!\!>$“inequalities”;
\item line 549; “DoFs”$-\!\!\!-\!\!\!>$“the DoFs”.
\end{itemize}
}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\end{enumerate}

\section{Response to Reviewer 2}
%\smallskip \noindent {\bf Response to Reviewer 2}.

\begin{enumerate}[1.]
\item \textsf{A significantly more thorough review of the literature is required. Indeed, very little mention of other stabilization free methods are given. It is difficult to gauge how this work compares to the existing literature and where the true novelty of the work lies. For example, in the reference \cite{CicuttinErnLemaire2019} a stabilisation free method is designed by considering a HHO space of unknowns and a recon- struction in a VEM space. See \cite[Remark 5.1]{CicuttinErnLemaire2019}. How does the current article compare to this work? Moreover, the authors do not make it clear what the benefit of a “stabilization-free” VEM is.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{At equation (3.4) (and continuing below) the space $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ is considered. Is this standard notation? At first I thought $\boldsymbol{x}$ was a predefined point (e.g. the centre of $T$) and the space $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ was the set of functions that could be written as a polynomial valued anti-symmetric tensor times the predefined point $\boldsymbol{x}$. However, I think what is actually meant is $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\{f:T\to\mathbb R^d: f(\boldsymbol{x})=\boldsymbol{P}_{k-2}(\boldsymbol{x})\boldsymbol{x},\quad \forall\boldsymbol{x}\in T, \boldsymbol{P}_{k-2}\in \mathbb P_{k-2}(T;\mathbb K)\}$. The authors should clarify here.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Line 149: “$(I +\boldsymbol{x}\cdot\nabla)\boldsymbol{w} = \boldsymbol{0}$, which implies $\boldsymbol{w} = \boldsymbol{0}$”. I do not see how this follows. We have that
$$(\nabla\boldsymbol{w}(\boldsymbol{x}))\boldsymbol{x}=-\boldsymbol{w}(\boldsymbol{x})\quad\forall\boldsymbol{x}\in T.
$$
It is not clear to me how the conclusion that $\boldsymbol{w} = \boldsymbol{0}$ follows. The authors
should precise their reasoning.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the proof of Lemma 12, the authors apply a discrete trace inequality to the
quantity 
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}
$$
and cite [11, (2.18)]. However, [11, (2.18)] is a continuous trace inequality and there is no justification given for why the discrete trace inequality holds in this particular case. Moreover, it is not explained how one concludes that $\|\div\boldsymbol{\phi}\|_{-1,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}$.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the proof of Lemma 4.1, the authors claim that
$$
h_K^{\frac{1}{2}}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
$$
This is a sort of discrete trace inequality and the authors justify it by citing (A.3)-(A.4) in [15]. However, it is not apparent to me how this follows from (A.3)-(A.4). Moreover, the authors conclude that “with the multiplicative trace inequality”
$$
h_K^{\frac{1}{2}}\|v\|_{0,\partial K}\lesssim h_K^{-1}\|v\|_{0,K}.
$$
Again, this is a discrete trace inequality, and it is not specified why it is valid on the virtual space $V_k(K)$. The same goes for the arguments used in the proof of Lemma 4.3.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{When introducing the nonconforming virtual element method in Section 4, the authors should give some references for NCVEM. In particular, I don’t think the space $V_k(K)$ is the classical NCVEM space (e.g. that defined in \cite{AyusodeDiosLipnikovManzini2016}). The authors should give reference to where this space is first introduced.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{It seems that the main novelty of this work is the construction of a space
\begin{align*}
\mathbb V_{k-1}^{\div}(K):=\{\boldsymbol{\phi}&\in L^2(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \\
& \boldsymbol{\phi}\cdot\boldsymbol{n}_F\in\mathbb P^{k-1}(F)\;\forall F\in\mathcal F(K), \boldsymbol{\phi}|_T\in\mathbb P_{k-1}(T)^d\;\forall T\in\mathcal T_K
\}
\end{align*}
and a computable $L^2$ projector $Q_{K,k-1}^{\div}$ onto $\mathbb V_{k-1}^{\div}(K)$ such that
$$
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\simeq \|\nabla v\|_{0,K} \quad\forall v\in V_k(K),
$$
where $V_k(K)$ is the non-conforming space defined at line 378 (or in Section 5 the authors consider the conforming space defined at line 544). This result is stated in Lemma 4.4 and its proof relies on the norm equivalence (3.32) and the set of uni-solvent DOFs (3.29)-(3.31). However, upon reading Section 3.2 for the first time, it is difficult to grasp what it is the authors are actually trying to achieve. Are all of the spaces, definitions and lemmas in Section 3.2 really necessary to prove Lemma 4.4? If so, the authors should state the main result of Lemma 4.4 in an earlier section, and leave much of the details of Section 3.2 and the proof of Lemma 4.4 to a later section so that readers can understand what the authors are trying to achieve.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In Section 4, the authors design a stabilization free NCVEM for a reaction-diffusion problem, and in section 5 a stabilization free VEM. This seems an odd choice as one does not require a Poincar\'e inequality for the coercivity of the continuous blinear form. Indeed, if
$$
a(u, v)=(\nabla u, \nabla v)_{\Omega}+\alpha (u, v)_{\Omega}
$$
with $\alpha > 0$ then it holds trivially that
$$
\|u\|_{1,\Omega}^2\leq\max(1,\alpha^{-1})a(u,u).
$$
While things mightn't be so simple at the discrete level, it would seem more
appropriate to consider a Poisson problem.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the numerical section, the authors should compare their results to standard VEM and NCVEM to highlight any benefit their approach has.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{I suggest the authors conduct a thorough proof read of the manuscript as there are many typos, grammatical errors and poorly constructed sentences.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\end{enumerate}

\section{Response to Reviewer 3}
%\smallskip \noindent {\bf Response to Reviewer 2}.

\begin{enumerate}[1.]
\item \textsf{The paper under review presents an interesting and promising idea to avoid the stabilization term in the Virtual Element Method. The procedure adopted is very general and in principle can be used in many different settings. The paper is well written and the proofs are given with appropriate details. 
The only modification I require is a more in-depth comparison with the classical stabilized version with respect to the computational cost, in the two- and three-dimensional case, by making explicit examples in cases of interest.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\end{enumerate}

\bibliographystyle{abbrv}
\bibliography{../paper}

% ----------------------------------------------------------------
\end{document}
% ----------------------------------------------------------------

### 2023-01-31 reports/response.tex
some revisions

@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+The stabilization term in virtual element methods (VEM) brings about some problems. 
+\begin{enumerate}
+\item 
+The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
+$$
+c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
+$$
+for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.
+\item 
+The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+\item 
+For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
+\item The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
+and improper choices of the stabilization term will produce useless results.
+\item 
+Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
+\item Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
+\end{enumerate}
 
@@
 
-\item \textsf{Lines 17-18; when you discuss the results in references [9,10,20], I am not quite sure that the polynomial degree of the projection depends only on the number of vertices.
-In fact, in an updated version of the preprint [19], it is possible to see that also the shape of the polygon plays a role in the choice of such a polynomial degree.}
+\item \textsf{Lines 17-18; when you discuss the results in references \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, I am not quite sure that the polynomial degree of the projection depends only on the number of vertices.
+In fact, in an updated version of the preprint \cite{BerroneBorioMarcon2021}, it is possible to see that also the shape of the polygon plays a role in the choice of such a polynomial degree.}
 
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Yes. In \cite{BerroneBorioMarcon2021}, the polynomial degree $l$ should satisfy
+$$
+(l+1)(l+2) - \dim\mathcal{P}_l^{\textrm{ker}}(E)\geq N_E^V-1.
+$$
+And the dimension of $\mathcal{P}_l^{\textrm{ker}}(E)$ generally depends on the geometry of the polygon. While the authors prove that
+$$
+\dim\mathcal{P}_l^{\textrm{ker}}(E)\leq l(l+1)
+$$
+in \cite[Theorem 2]{BerroneBorioMarcon2021}. This means a sufficient condition for $l$ is 
+$$
+l\geq \frac{1}{2}(N_E^V-3).
+$$
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion. We have emphasized it.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion.
+We have presented a comment as follows: The hidden constants in (1.1) are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~2.2 for details.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion. We have mentioned it.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion. We have recalled it.
 

### 2023-01-31 stabfreevem_sinum.tex
some revisions

@@
 
+\newcommand{\LC}[1]{\textcolor{red}{#1}}
+% \newcommand{\XH}[1]{\textcolor{cyan}{#1}}
+\newcommand{\XH}[1]{\textcolor{red}{#1}}
+\newcommand{\revision}[1]{{\color{red!85!black}{#1}}}
+
 \begin{document}
@@
 \section{Introduction}
-
-Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon.
-We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on similar stabilization-free virtual element methods for plane elasticity problem.
-The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
+\XH{A stabilization term is usually required in the virtual element methods (VEM) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems.
+The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy
+$$
+c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
+$$
+for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.
+The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
+The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
+and improper choices of the stabilization term will produce useless results.
+Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
+}
+
+Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}.
+\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
+The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}.
+Along this line, similar stabilization-free virtual element methods are devised for plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
+The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
 the analysis is rather elaborate. 
-This motivates us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.
-
-The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
+\XH{
+% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
+This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
+}
+
+The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 \end{enumerate}
+\XH{The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.}
 We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
@@
 To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
+Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
 
@@
 
-\subsection{Mesh conditions}
+\subsection{Mesh conditions}\label{sec:meshcondition}
 We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
@@
 \[
-\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
+\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
 \]
@@
 (\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
-(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
+(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
 \end{align}
-Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.
-
-We also need the lowest order Raviart-Thomas (RT) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}
-\[
-\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
-\]
-Define $\mathring{\boldsymbol{V}}^{RT}(K):=\boldsymbol{V}^{RT}(K)\cap \boldsymbol{H}_0(\div, K)$.
+for $T\in\mathcal T_K$.
+Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.
+
+We also need the lowest order Raviart-Thomas (RT) element space~\cite{RaviartThomas1977,Nedelec1980}
+\[
+\boldsymbol{V}^{\mathrm{RT}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
+\]
+\XH{The DoFs are given by
+\[
+(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F,  \quad q\in \mathbb P_{0}(F), F\in\mathcal F(T)
+\]
+for $T\in\mathcal T_K$.}
+Define $\mathring{\boldsymbol{V}}^{\mathrm{RT}}(K):=\boldsymbol{V}^{\mathrm{RT}}(K)\cap \boldsymbol{H}_0(\div, K)$.
 
@@
 \begin{equation}\label{eq:Pkvectordecomp}  
-\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
+\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
 \end{equation}
@@
 \begin{equation}\label{eq:localBDMfemderhamcomplex}
-\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{BDM}(K)\xrightarrow{\div} V_{k-2}^{L^2}(K)\to0,    
+\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\xrightarrow{\div} V_{k-2}^{L^2}(K)\to0,    
 \end{equation}
 \begin{equation}\label{eq:localRTfemderhamcomplex}
-\boldsymbol{V}_{1}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}^{RT}(K)\xrightarrow{\div} V_{0}^{L^2}(K)\to0,    
+\boldsymbol{V}_{1}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}^{\mathrm{RT}}(K)\xrightarrow{\div} V_{0}^{L^2}(K)\to0,    
 \end{equation}
 \begin{equation}\label{eq:localBDMfemderhamcomplex0}
-\mathring{\boldsymbol{V}}_{k}^{d-2}(K)\xrightarrow{\div\skw}\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)\xrightarrow{\div} \mathring{V}_{k-2}^{L^2}(K)\to0,    
+\mathring{\boldsymbol{V}}_{k}^{d-2}(K)\xrightarrow{\div\skw}\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)\xrightarrow{\div} \mathring{V}_{k-2}^{L^2}(K)\to0,    
 \end{equation}
 \begin{equation}\label{eq:localRTfemderhamcomplex0}
-\mathring{\boldsymbol{V}}_{1}^{d-2}(K)\xrightarrow{\div\skw}\mathring{\boldsymbol{V}}^{RT}(K)\xrightarrow{\div} \mathring{V}_{0}^{L^2}(K)\to0,    
+\mathring{\boldsymbol{V}}_{1}^{d-2}(K)\xrightarrow{\div\skw}\mathring{\boldsymbol{V}}^{\mathrm{RT}}(K)\xrightarrow{\div} \mathring{V}_{0}^{L^2}(K)\to0,    
 \end{equation}
@@
 Clearly \eqref{eq:localBDMfemderhamcomplex} is a complex.
-We refer to \cite[Section 4]{ChenHuang2021divX} for the proof of $\div\boldsymbol{V}_{k-1}^{BDM}(K)=V_{k-2}^{L^2}(K)$.
-
-Next prove $\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)=\div\skw\boldsymbol{V}_{k}^{d-2}(K)$.
-For $\boldsymbol{v}\in\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$, by Theorem 1.1 in \cite{CostabelMcIntosh2010}, there exists $\boldsymbol{\tau}\in\boldsymbol{H}^1(K;\mathbb K)$ satisfying $\div\boldsymbol{\tau}=\div\skw\boldsymbol{\tau}=\boldsymbol{v}$.
+We refer to \cite[Section 4]{ChenHuang2021divX} for the proof of $\div\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)=V_{k-2}^{L^2}(K)$.
+
+Next prove $\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)=\div\skw\boldsymbol{V}_{k}^{d-2}(K)$.
+For $\boldsymbol{v}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$, by Theorem 1.1 in \cite{CostabelMcIntosh2010}, there exists $\boldsymbol{\tau}\in\boldsymbol{H}^1(K;\mathbb K)$ satisfying $\div\boldsymbol{\tau}=\div\skw\boldsymbol{\tau}=\boldsymbol{v}$.
 Let $\boldsymbol{\sigma}\in \boldsymbol{V}_{k}^{d-2}(K)$ be the nodal interpolation of $\boldsymbol{\tau}$ based on DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32}.
@@
 \[
-\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
+\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
 \]
@@
 \[
-\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{RT}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
-\]
-Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{RT}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$ for $k\geq2$.
+\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
+\]
+Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.
 
@@
 On the other side, for $\boldsymbol{\phi}\in \boldsymbol{V}_{k-1}^{\rm div}(K)$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
-$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$.
+$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$.
 Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$.
@@
 Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$.
-Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{BDM}(K)$ such that $\boldsymbol{\phi}_1\cdot\boldsymbol{n}|_{\partial K}=\boldsymbol{\phi}\cdot\boldsymbol{n}_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ in the interior of $K$ vanish.
+Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $\boldsymbol{\phi}_1\cdot\boldsymbol{n}|_{\partial K}=\boldsymbol{\phi}\cdot\boldsymbol{n}_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ in the interior of $K$ vanish.
 We have
@@
 \]
-Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}.
-Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$.
+Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}.
+Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$.
 We have
@@
 \end{equation}
-By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$.
+By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$.
 Hence
@@
 \mathbb{V}_{k,k-2}^{\rm div}(K):=&\{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\} \\
-=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_e\in\mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K)\}.
+=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_e\in\mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K)\}.
 \end{align*}

### 2023-02-01 reports/response.tex
more revision

@@
 \usepackage[pdftex,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=blue,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
+\usepackage{booktabs}
 
@@
 \item \textsf{Lines 50-51; when you define the function $\phi$, are you sure that the normal component of the trace is a polynomial only on the faces of $K$?
-Don't you also need this property to be valid on the faces of the simplicial tessellation of $K$?.}
+Don't you also need this property to be valid on the faces of the simplicial tessellation of $K$?}
 
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Base on $d$-dimensional polytope $K\in \mathcal T_h$ and its simplicial partition $\mathcal T_K$ of $K$, we define the following $H(\div)$-conforming finite element spaces in this paper:
+% For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
+\begin{align*}    
+\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}\textrm{ for } k\geq2, \\
+\boldsymbol{V}^{\mathrm{RT}}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}, \\
+\boldsymbol{V}_{k-1}^{\rm div}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\}\textrm{ for } k\geq2, \\
+\boldsymbol{V}_{0}^{\rm div}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\},
+\\
+\mathbb{V}_{k-1}^{\rm div}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \textrm{ for each } F\in\mathcal F(K)\}.
+\end{align*}
+We compare these spaces for polytope $K$ and face $F\in\mathcal F(K)$ in the following table.
+\begin{center}
+\renewcommand\arraystretch{1.3}
+\begin{tabular}[t]{|c|c|c|c|}
+% \toprule
+\hline
+$\boldsymbol{\phi}$ & $\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)/\boldsymbol{V}^{\mathrm{RT}}(K)$ & $\boldsymbol{V}_{k-1}^{\rm div}(K)$ & $\mathbb{V}_{k-1}^{\rm div}(K)$  \\
+\hline
+% \midrule 
+$(\div\boldsymbol{\phi})|_K$ & piecewise polynomial & polynomial & polynomial \\
+\hline
+$(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ & piecewise polynomial & piecewise polynomial & polynomial \\
+\hline
+% \bottomrule
+\end{tabular}
+\end{center}
+We can see that both $(\div\boldsymbol{\phi})|_K$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ are polynomials for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$.
+
+To ensure the $L^2$ projection
+$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
+for virtual element function $v\in V_k(K)$, we only require
+$(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ to be a polynomial for each $(d-1)$-dimensional face $F$ of $K$.
+But $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ can be a piecewise polynomial for interior face $F$ of the simplicial tessellation of $K$.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We add references \cite{Ciarlet1978,Verfuerth2013} in the revised manuscript.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We add reference \cite[Theorem 1.5.1.10]{Grisvard1985} in the revised manuscript.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We revise the first part of the proof of Lemma 3.12 as follows.
+
+By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
+$$
+h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
+$$ 
+where
+$$
+\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
+$$
+Then we have
+\begin{equation}\label{eq:20230201}  
+h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+\end{equation}
+For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
+$$
+h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
+$$ 
+This means
+$$
+\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$ 
+Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
+$$
+h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+It has been corrected.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We define $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ based on DoFs (3.1)-(3.3).
+To be specific, $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and all the DoFs (3.1)-(3.3) of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We revise it as follows.
+
+By the norm equivalence on each simplex $T\in\mathcal T_K$ and the vanishing DoFs~(3.1)-(3.3), we get
+\begin{align*}%\label{eq:20220324-5}
+\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
+\end{align*}
+Due to the vanishing DoF (3.2), it holds that $\div\boldsymbol{\phi}_1=Q_0^T(\div\boldsymbol{\phi}_1)$ for $T\in\mathcal T_K$.
+Then apply the integration by parts and the Cauchy-Schwarz inequality to acquire
+\begin{equation*}%\label{eq:202302011}  
+\|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
+\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
+\end{equation*}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggest. We have revised it.
 
@@
 
-\item \textsf{In the proof of Lemma 12, the authors apply a discrete trace inequality to the
+\item \textsf{In the proof of Lemma 3.12, the authors apply a discrete trace inequality to the
 quantity 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$.
+We can use the trace inequality \cite[(2.18)]{BrennerSung2018} and the inverse inequality to get
+$$
+h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
+$$ 
+Then
+$$
+\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$
+
+For the second question, it can be explained as follows:
+$$
+\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
+$$
 

### 2023-02-01 stabfreevem_sinum.tex
more revision

@@
 The corresponding norm and semi-norm are denoted respectively by
-$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. 
+$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. Denote by $L_0^2(K)$ the space of all functions in $L^2(K)$ with zero integral.
 Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
@@
 \end{align}
-for $T\in\mathcal T_K$.
+for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$.
 Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.
@@
 \begin{proof}
-By the inverse inequality \cite[Lemma 10]{Huang2020} and the trace inequality \cite[(2.18)]{BrennerSung2018}, we have
-\begin{align*}
-&\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
-&\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
-\end{align*}
-
-Next we focus on the proof of the other side.
+\XH{By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
+$$
+h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
+$$ 
+where
+$$
+\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
+$$
+Then we have
+\begin{equation}\label{eq:20230201}  
+h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+\end{equation}
+For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
+$$
+h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
+$$ 
+This means
+$$
+\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$ 
+Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
+$$
+h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$
+}
+% \begin{align*}
+% &\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
+% &\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
+% \end{align*}
+
+Next we focus on the proof of the \XH{lower bound}.
 Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$.
-Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $\boldsymbol{\phi}_1\cdot\boldsymbol{n}|_{\partial K}=\boldsymbol{\phi}\cdot\boldsymbol{n}_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ in the interior of $K$ vanish.
-We have
-\begin{equation}\label{eq:20220324-5}
-\|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
-\end{equation}
-\[
+Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and \XH{all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero}.
+\XH{By the norm equivalence on each simplex $T$ and the vanishing DoFs \eqref{BDMdof2}-\eqref{BDMdof3}, we get
+\begin{align}\label{eq:20220324-5}
+\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
+\end{align}
+Due to the vanishing DoF \eqref{BDMdof2}, it holds that $\div\boldsymbol{\phi}_1=Q_0^T(\div\boldsymbol{\phi}_1)$ for $T\in\mathcal T_K$.
+% We have
+% \begin{equation}
+% \|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
+% \end{equation}
+Then apply the integration by parts and the Cauchy-Schwarz inequality to acquire
+\begin{equation}\label{eq:202302011}
 \|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
-\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\quad\forall~T\in\mathcal T_K.
-\]
-Then let $w\in H^1(K)/\mathbb R$ be the solution of 
+\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
+\end{equation}
+}
+% for $T\in\mathcal T_K$.
+Now let $w\in H^1(K)/\mathbb R$ be the solution of 
 \[
@@
 \]
-Obviously we have
+Obviously \XH{we obtain from \eqref{eq:202302011} that}
 \[
@@
 \begin{theorem}
-The stabilization free virtual element method \eqref{eq:vem} is uni-solvent.
+The stabilization free virtual element method \eqref{eq:vem} is \XH{well-posed}.
 \end{theorem}

### 2023-02-04 reports/response.tex
answer the first reviewer

@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+The definition of the $L^2$-bounded commuting projection operator is not trivial, and can not be explicitly given shortly.
+Reference \cite{ChristiansenWinther2008} constructs such an operator in the whole paper. 
+And references \cite{ArnoldGuzman2021,FalkWinther2014} focus on the construction of local $L^2$-bounded commuting projection operators in the whole paper.
+Thus in the revised manuscript, we present the properties of $I_K^{\div}$ instead of the explicit definition.
+And we use the local $L^2$-bounded operator in \cite{ArnoldGuzman2021,FalkWinther2014} instead of that in \cite{ChristiansenWinther2008}.
+
+The modification is given as follows.
+
+Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
+\begin{equation}\label{eq:20230203}  
+\|I_K^{\div}\boldsymbol{\psi}\|_{0,K} \lesssim \|\boldsymbol{\psi}\|_{0,K}\quad\forall~\boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K),
+\end{equation}
+\[
+\div(I_K^{\div}\boldsymbol{\psi})=\div\boldsymbol{\psi} \quad \textrm{ for } \boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K) \textrm{ satisfying } \div\boldsymbol{\psi}\in V_{k-2}^{L^2}(K),
+\]
+where $
+V_{k-2}^{L^2}(K)=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for } T\in\mathcal T_K\}
+$.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We have revised them as follows.
+
+% We have
+% \begin{equation*}%\label{eq:20220324-6}
+% \div\boldsymbol{\phi}_2=-\div(I_K^{\div}(\nabla w))=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1).
+% \end{equation*}
+It follows from \eqref{eq:20230203} and (3.29) (i.e. the bound on line 322) that
+\begin{equation*}%\label{eq:20220324-7}
+\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation*}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We have compared space $\boldsymbol{V}_{k-1}^{\rm div}(K)$ and space $\mathbb{V}_{k-1}^{\rm div}(K)$ in question 7.
+Indeed, on each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We have revised DoFs (4.3) and (4.4) as
+\begin{align*}
+\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), 
+\\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K),
+\end{align*}
+where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Now we use $\mathbb P_{k-2}^{\perp}(K)$ to denote the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+One reviewer has questions on the proof of Lemma 4.1. Thus we modify the proof and keep it.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+They have been corrected.
 
@@
 
-\item \textsf{Line 408; is [11, (2.15)] the proper reference for the Poincar\'e-Friedrichs inequality? I think is a standard result and you may wish to cite any standard PDE book.}
+\item \textsf{Line 408; is [11, (2.15)] the proper reference for the Poincar\'e-Friedrichs inequality? I think it is a standard result and you may wish to cite any standard PDE book.}
 
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We have changed it to reference \cite{Necas1967}.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We have the norm equivalence
+\[
+\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2 \quad\forall~v\in V_k(K),
+\]
+and the inequality
+\[
+h_K|v|_{1,K}\lesssim \|v\|_{0,K}\quad\forall~v\in V_k(K).
+\]
+But we do not have 
+the equivalence
+\[
+h_K|v|_{1,K}\eqsim \|v\|_{0,K}\quad\forall~v\in V_k(K).
+\]
+Indeed, when $v$ is a nonzero constant, we have
+$$
+h_K|v|_{1,K}=0,\quad \|v\|_{0,K}>0.
+$$
 
@@
 
-\item \textsf{Lines 445 and 456; explain from where the term $Q_0^k(\div\phi)$ appears.}
+\item \textsf{Lines 445 and 456; explain from where the term $Q_0^K(\div\phi)$ appears.}
 
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Since $v\in L_0^2(K)$, then $Q_{0}^Kv=0$ and $v=v-Q_{0}^Kv$. Noting that $Q_{0}^K(\div\boldsymbol{\phi})$ is constant, we have
+$$
+(Q_{0}^K(\div\boldsymbol{\phi}), v)_K=(Q_{0}^K(\div\boldsymbol{\phi}), v-Q_{0}^Kv)_K=0.
+$$
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Notice that $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$.
+We get from 
+\begin{align*}
+\|\boldsymbol{\phi}\|_{0,K}%&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
+&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}
+\end{align*}
+that
+\[
+\|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}.
+\]
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion.
+Now we cite reference \cite{Brenner2003}.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We have revised DoFs (5.1), (5.2), and (5.3) as
+\begin{align*}
+v(\delta), & \quad \delta\in\mathcal V(K), \\
+\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K),
+\end{align*}
+where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
 
@@
 
-\item \textsf{You may wish to reduce or even drop the proof or Theorem 5.3, which appears to be a standard Strang-type result for the VEM.}
+\item \textsf{You may wish to reduce or even drop the proof of Theorem 5.3, which appears to be a standard Strang-type result for the VEM.}
 
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion. We have removed the proof of Theorem 5.3.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We proofread the paper carefully. All of them have been corrected.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+\begin{itemize}
+    \item 
+For virtual function $v\in V_k(K)$, apply (A.3) in \cite{ChenHuang2020ncvem} to get
+\[
+h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
+\]
+By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
+\[
+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
+\]
+Combining the last two inequalities yields
+\[
+h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
+\]
+\item The multiplicative trace inequality is
+\[
+\|v\|_{0,\partial K}\lesssim h_K^{-1/2}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \quad\forall~v\in H^1(K).
+\]
+Since $v\in V_k(K)\subset H^1(K)$, inserting the last multiplicative trace inequality into the inequality
+\[
+|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
+\]
+we get
+\begin{align*}
+|v|_{1,K}&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \\
+&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,K}^{1/2}|v|_{1,K}^{1/2}.
+\end{align*}
+Then apply the Young's inequality to acquire
+\[
+|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}.
+\]
+\end{itemize}
 

### 2023-02-04 stabfreevem_sinum.tex
answer the first reviewer

@@
 
-Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}.
+Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}.
 \XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
@@
 
-The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
+The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 inner product $(\cdot, \cdot)_K$. The norm equivalence
-\eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be
+\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
 sufficiently large compared with the virtual element space $V_k(K)$.  In
@@
 To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
+Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
 
@@
 space for $k=0$, with some constraints. To ensure the $L^2$ projection
-$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
+$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
 for virtual element function $v\in V_k(K)$, we require
@@
 In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
-A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}.
-And a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
 Some numerical results are shown in Section \ref{sec:numericalexamps}.
@@
 polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
-For a banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$, where $\mathbb{K}$ is the set of antisymmetric matrices.
+For a Banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$ being the set of antisymmetric matrices.
 Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
@@
 For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
-On face $F\in\mathcal F_h$, define surface divergence
+On the face $F\in\mathcal F_h$, define surface divergence
 \[
@@
 \]
-For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.
+For a smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.
 
@@
 For each polygon $K\in \mathcal T_h$, 
-define shape function space
+define the shape function space
 \[
@@
 Obviously \XH{we obtain from \eqref{eq:202302011} that}
-\[
+\begin{equation}\label{eq:202302031}  
 \|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\]
-Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}.
-Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$.
-We have
+\end{equation}
+\XH{Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
+\begin{equation}\label{eq:20230203}  
+\|I_K^{\div}\boldsymbol{\psi}\|_{0,K} \lesssim \|\boldsymbol{\psi}\|_{0,K}\quad\forall~\boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K),
+\end{equation}
+\[
+\div(I_K^{\div}\boldsymbol{\psi})=\div\boldsymbol{\psi} \quad \textrm{ for } \boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K) \textrm{ satisfying } \div\boldsymbol{\psi}\in V_{k-2}^{L^2}(K).
+\]
+Recall $
+V_{k-2}^{L^2}(K)=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for } T\in\mathcal T_K\}
+$.
+} Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$. \XH{We have
 \begin{equation}\label{eq:20220324-6}
-\div\boldsymbol{\phi}_2=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1),
-\end{equation}
+\div\boldsymbol{\phi}_2=-\div(I_K^{\div}(\nabla w))=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1).
+\end{equation}
+It follows from \eqref{eq:20230203} and \eqref{eq:202302031} that
 \begin{equation}\label{eq:20220324-7}
-\|\boldsymbol{\phi}_2\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\end{equation}
+\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation}}
 By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$.
@@
 \[
-\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
-\]
+\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): (\boldsymbol{\phi}\cdot\boldsymbol{n})|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
+\]
+\XH{On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.}
 Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
@@
 For later use, let $Q_{K,k-1}^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
-Introduce discrete spaces
+Introduce the discrete spaces
 \begin{align*}
@@
 The degrees of freedom are given by
+\XH{
 \begin{align}
-\frac{1}{|F|}(v, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
-\frac{1}{|K|}(v, q)_K & \quad\forall~q\in\mathbb P_{k-2}(K). \label{eq:vemdof2}
+\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:vemdof2}
 \end{align}
+where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}
 
@@
 V_k(K):=\{v\in H^1(K) &: \Delta v\in\mathbb P_{k}(K),\, \partial_nv|_F\in\mathbb P_{k-1}(F)\textrm{ for each face }F\in\mathcal F(K), \\
-&\qquad\qquad\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
-\end{align*}
-where $\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+&\qquad\qquad\qquad\quad\;\, \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in \mathbb P_{k-2}^{\perp}(K)\},
+\end{align*}
+where %$\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ 
+\XH{$\mathbb P_{k-2}^{\perp}(K)$}
+means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
 Due to \eqref{eq:localproj2dprop1}, it holds $\mathbb P_k(K)\subseteq V_k(K)$.
@@
 \begin{proof}
-Apply the integration by parts to get
+\XH{
+By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
+\[
+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
+\]
+Then apply (A.3) in \cite{ChenHuang2020ncvem} to get
+\[
+h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
+\]
+Employing the integration by parts and the Cauchy-Schwarz inequality, we have
 \[
@@
 \]
-By $h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}$, i.e. (A.3)-(A.4) in \cite{ChenHuang2020ncvem}, we obtain
+Combining the last two inequalities gives
+% By $h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}$, i.e. (A.3)-(A.4) in \cite{ChenHuang2020ncvem}, we obtain
 \[
@@
 \]
-which together with the multiplicative trace inequality yields \eqref{eq:veminverse}.
+which together with the multiplicative trace inequality and the Young's inequality yields \eqref{eq:veminverse}.}
 \end{proof}
@@
 \end{align*}
-which combined with the inverse inequality for polynomials implies
+which combined with \XH{both $H^1$-$L^2$ and $L^2$ boundary-$L^2$ bulk inverse inequalities} for polynomials implies
 \[%\label{eq:VEMnormequivalencePiK}
@@
 \]
-Thanks to the Poincar\'e-Friedrichs inequality \cite[(2.15)]{BrennerSung2018} and \eqref{eq:projlocal2d2},
+Thanks to the Poincar\'e-Friedrichs inequality \XH{\cite{Necas1967}} %\cite[(2.15)]{BrennerSung2018} 
+and \eqref{eq:projlocal2d2},
 \begin{align*}  
@@
 Since $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
-Apply the integration by parts to get
+Apply the integration by parts \XH{and the fact $v=v-Q_{0}^Kv\in L_0^2(K)$} to get
 \begin{align*}
@@
 \|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
-&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
-&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}^2.    
-\end{align*}
+&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{align*}
+\XH{Noting that $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$, we have
+\[
+\|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}.
+\]}
 Then we obtain from the norm equivalence \eqref{eq:Vknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
@@
 V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
-&\qquad\; \textrm{DoF \eqref{eq:vemdof1} is single-valued for $F\in\mathcal F_h$, and vanishes for $F\in \mathcal F_h^{\partial}$}\}.
-\end{align*}
-We have the discrete Poincar\'e inequality (cf. \cite[(4.16)]{ChenHuang2020ncvem})
+&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
+\end{align*}
+We have the discrete Poincar\'e inequality \XH{\cite{Brenner2003}}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
 \begin{equation}\label{eq:vempoincareineqlty}
@@
 \[
-\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\XH{\eqsim} \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
 \]
@@
 \end{align*}
-Summing the last two inequlities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
+Summing the last two inequalities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
 \begin{align*}
@@
 The degrees of freedom are given by
-\begin{align}
-v(\delta) & \quad\forall~\delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
-\frac{1}{|e|}(v, q)_e & \quad\forall~q\in\mathbb P_{k-2}(e), e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
-\frac{1}{|K|}(v, q)_K & \quad\forall~q\in\mathbb P_{k-2}(K). \label{eq:cfmvemdof3}
+\XH{\begin{align}
+v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
+\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
 \end{align}
+where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}
 And the space of shape functions is
@@
 
-For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
+For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using only the DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
 We have the norm equivalence of space $V_k(K)$ (cf. \cite[Lemma 4.7]{Huang2021} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$, it holds
@@
 \subsection{Error analysis}
+Applying the standard error analysis for VEMs, we have the following error estimate for the VEM \eqref{eq:cfmvem}.
 \begin{theorem}\label{thm:cfmerrorestimateH1}
-Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:cfmvem}.
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:cfmvem}.
 Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$.
@@
 \end{theorem}
-\begin{proof}
-Take any $v_h\in V_h$. 
-Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
-\[
-\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
-\]
-\[
-a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
-\]
-Combining the last two inequalities gives
-\[
-a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
-\]
-By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
-\begin{align*}
-|v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
-&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
-% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
-&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
-\end{align*}
-Hence we get from the triangle inequality and the last two inequalities that
-\begin{align*}  
-|u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
-&\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
-\end{align*}
-By the arbitrariness of $v_h\in V_h$, we derive
-\[
-|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
-\]
-At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
-\end{proof}
+% \begin{proof}
+% Take any $v_h\in V_h$. 
+% Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
+% \[
+% \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
+% \]
+% \[
+% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
+% \]
+% Combining the last two inequalities gives
+% \[
+% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
+% \]
+% By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
+% \begin{align*}
+% |v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
+% % &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
+% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
+% \end{align*}
+% Hence we get from the triangle inequality and the last two inequalities that
+% \begin{align*}  
+% |u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
+% &\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
+% \end{align*}
+% By the arbitrariness of $v_h\in V_h$, we derive
+% \[
+% |u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
+% \]
+% At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
+% \end{proof}
 

### 2023-02-05 reports/response.tex
answer the second reviewer

@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Yes, the notation $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ means
+$$
+\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\},
+$$
+where $\boldsymbol{\tau}\boldsymbol{x}$ is the product of the matrix $\boldsymbol{\tau}$ and the independent variable $\boldsymbol{x}\in T$.
+Similar notations are used in \cite{ChenHuang2021divdiv,Chen;Huang:2020Finite}.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+The fact “$(I +\boldsymbol{x}\cdot\nabla)\boldsymbol{w} = \boldsymbol{0}$, which implies $\boldsymbol{w} = \boldsymbol{0}$” follows from \cite[(35)]{Chen;Huang:2020Finite}
+%Recall (35) in \cite{Chen;Huang:2020Finite} that
+\begin{equation}\label{eq:20230205}
+\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
+\end{equation}
+Indeed, \eqref{eq:20230205} is a direct result of the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
+$$
+\boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
+$$
+where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this suggestion. We have revised the statement as follows:
+Several $H^1$-nonconforming virtual elements are developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
+In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+Thanks for this nice suggestion. We add the following paragraph in the beginning of Section 3.
+
+In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
+\begin{equation*}%\label{eq:Vkm1divnormequiv}
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation*}
+The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
+the norm equivalence for the virtual element space
+\begin{equation*}%\label{intro:gradVknormequiv} 
+\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
+\end{equation*}
+where $V_k(K)$ is the nonconforming virtual element space in Section 4, and the conforming virtual element space in Section 5.
+Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.
 
@@
 \item \textsf{In Section 4, the authors design a stabilization free NCVEM for a reaction-diffusion problem, and in section 5 a stabilization free VEM.
-This seems an odd choice as one does not require a Poincar\'e inequality for the coercivity of the continuous blinear form.
+This seems an odd choice as one does not require a Poincar\'e inequality for the coercivity of the continuous bilinear form.
 Indeed, if
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.} 
-...
+In this paper, we consider the reaction-diffusion problem with the homogeneous Dirichlet boundary condition.
+The Poincar\'e inequality is required for the coercivity of the bilinear form.
+In the continuous level, by the Poincar\'e inequality, we have the coercivity
+\[
+\|u\|_{1,\Omega}^2\lesssim |u|_{1,\Omega}^2\leq a(u,u)\quad \forall~u\in H_0^1(\Omega).
+\]
+
+The discrete bilinear form in this paper is defined as 
+\[
+a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
+\]
+The discrete Poincar\'e inequality established in \cite{Brenner2003} works for the virtual element space $V_h$
+\[
+\|v_h\|_0\lesssim |v_h|_{1,h}\quad\forall~v_h\in V_h.
+\]
+This means that $|\cdot|_{1,h}$ is indeed a norm for space $V_h$. Hence, to show the coercivity of the discrete bilinear form $a_h(\cdot, \cdot)$, it suffices to prove
+\begin{equation}\label{eq:11}    
+|v_h|_{1,h}^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+\end{equation}
+The coercivity \eqref{eq:11} is (4.19) for the nonconforming virtual element method, and~(5.8) for the conforming virtual element method.
 

### 2023-02-05 stabfreevem_sinum.tex
answer the second reviewer

@@
 
-For $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
 For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
 
-For $d$-dimensional simplex $T$,
-let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of $\boldsymbol x$ corresponding to vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
+For a $d$-dimensional simplex $T$,
+let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of the point $\boldsymbol x$ corresponding to the vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
 Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$.
@@
 \section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
-
-In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
+\XH{
+In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
+\begin{equation*}%\label{eq:Vkm1divnormequiv}
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation*}
+The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
+the norm equivalence for the virtual element space
+\begin{equation*}%\label{intro:gradVknormequiv} 
+\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
+\end{equation*}
+where $V_k(K)$ is the nonconforming virtual element space in Section \ref{sec:stabfreencfmvem}, and the conforming virtual element space in Section \ref{sec:stabfreecfmvem}.
+Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.}
+
 \subsection{$H(\div)$-conforming finite elements}
@@
 
-By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have the decomposition
+By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
 \begin{equation}\label{eq:Pkvectordecomp}  
-\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
-\end{equation}
+\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x},
+\end{equation}
+\XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
+\XH{Recall (35) in \cite{Chen;Huang:2020Finite} that
+\begin{equation}\label{eq:20230205}
+\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
+\end{equation}
+Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
+$$
+\boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
+$$
+where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.}
 
@@
 \end{equation*}
-we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which implies $\boldsymbol{w}=\boldsymbol{0}$.
+we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which \XH{together with \eqref{eq:20230205}} implies $\boldsymbol{w}=\boldsymbol{0}$.
 \end{proof}
@@
 \subsection{$H^1$-nonconforming virtual element}
-
-Recall the $H^1$-nonconforming virtual element in \cite{ChenHuang2020ncvem,Huang2020,AyusodeDiosLipnikovManzini2016}.
+\XH{Several $H^1$-nonconforming virtual elements are developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
+In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.}
 The degrees of freedom are given by
@@
 \end{equation}
+\XH{Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.}
 % Introduce discrete spaces
@@
 V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
-&\qquad\qquad\qquad\qquad\qquad\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
+&\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\XH{\mathbb P_{k-2}^{\perp}(K)}\},
 \end{align*}

### 2023-02-06 reports/response.tex
answer the first two questions of reviewer 2

@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-The stabilization term in virtual element methods (VEM) brings about some problems. 
+The stabilization term in virtual element methods (VEM) brings about some problems, which motivate us to develop stabilization-free VEMs. 
 \begin{enumerate}
@@
 It is difficult to gauge how this work compares to the existing literature and where the true novelty of the work lies.
-For example, in the reference \cite{CicuttinErnLemaire2019} a stabilisation free method is designed by considering a HHO space of unknowns and a recon- struction in a VEM space.
+For example, in the reference \cite{CicuttinErnLemaire2019} a stabilisation free method is designed by considering a HHO space of unknowns and a reconstruction in a VEM space.
 See \cite[Remark 5.1]{CicuttinErnLemaire2019}.
-How does the current article compare to this work?
-Moreover, the authors do not make it clear what the benefit of a “stabilization-free” VEM is.}
+How does the current article compare to this work?}
 
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+\begin{itemize}
+    \item In addition to stabilization-free VEMs in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023,MengWangBuMei2022}, we add the reference \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and the references
+\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.
+    \item Next we compare the mixed-order HHO method in \cite{CicuttinErnLemaire2019} and the virtual element method.
+
+Recall the nonconforming virtual element in \cite{AyusodeDiosLipnikovManzini2016}.
+The local virtual element space is
+\[
+W_k(K):=\{v\in H^1(K) : \Delta v\in\mathbb P_{k-2}(K),\, \partial_nv|_F\in\mathbb P_{k-1}(F)\textrm{ for }F\in\mathcal F(K)\}.
+\]
+The degrees of freedom are given by
+\begin{align}
+\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:vemdof2}
+\end{align}
+where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
+Then define the global virtual element space  
+\begin{align*}
+W_h&:=\{v_h\in L^2(\Omega): v_h|_K\in W_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
+&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
+\end{align*}
+By Remark 5.4 in \cite{CicuttinErnLemaire2019}, the mixed-order HHO method for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
+\begin{equation}\label{eq:2023111}    
+\sum_{K\in\mathcal T_h}(\nabla u_h, \nabla v_h)_K=\sum_{K\in\mathcal T_h}(f, Q_{k-2}^Kv_h)_K\quad\forall~v_h\in W_h.
+\end{equation}
+In Remark 5.1 in \cite{CicuttinErnLemaire2019}, the authors claim that the stabilization is no longer needed for the mixed-order HHO method, i.e. the method \eqref{eq:2023111}.
+However, $(\nabla_h u_h, \nabla_h v_h)$ is not computable, % based on the degrees of freedom \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, 
+and the method \eqref{eq:2023111} is not the standard nonconforming VEM in \cite{AyusodeDiosLipnikovManzini2016}. 
+% For the practical computation, a basis of $W_k(K)$ has to be solved approximately as shown in \cite[Remark 4.1]{CicuttinErnLemaire2019}. 
+% The method \eqref{eq:2023111} is not the standard nonconforming virtual element method in \cite{AyusodeDiosLipnikovManzini2016}.
+% However, the bilinear form $\displaystyle\sum_{K\in\mathcal T_h}(\nabla u_h, \nabla v_h)_K$ is not computable based on the degrees of freedom \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, since some non-polynomial functions are included in the space $W_k(K)$.
+For the practical computation, a basis of $W_k(K)$ has to be solved approximately as shown in 
+Remark 4.1 in \cite{CicuttinErnLemaire2019}, which will always produce errors. 
+When a basis of $W_k(K)$ is solved approximately (can't be solved exactly), the approximation of the space $W_h$ is no more a virtual element space, and the method \eqref{eq:2023111} is no more a virtual element method.
+See Remark 4.6.
+\end{itemize}
+
+\medskip
+
+\item \textsf{Moreover, the authors do not make it clear what the benefit of a “stabilization-free” VEM is.}
+
+\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+The stabilization term in virtual element methods (VEM) brings about some problems, which motivate us to develop stabilization-free VEMs. 
+\begin{enumerate}
+\item 
+The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
+$$
+c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
+$$
+for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.
+\item 
+The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+\item 
+For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
+\item The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
+and improper choices of the stabilization term will produce useless results.
+\item 
+Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
+\item Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
+\end{enumerate}
 

### 2023-02-06 stabfreevem_sinum.tex
answer the first two questions of reviewer 2

@@
 The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}.
-Along this line, similar stabilization-free virtual element methods are devised for plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
+Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
+\XH{By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and
+\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.}
+
 The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
@@
 \end{remark}
+\XH{
+\begin{remark}\rm
+The stabilization-free mixed-order HHO method for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
+\begin{equation}\label{eq:2023111}    
+(\nabla_h u_h, \nabla_h v_h)=\sum_{K\in\mathcal T_h}(f, Q_{k-2}^Kv_h)_K\quad\forall~v_h\in W_h,
+\end{equation}
+where
+\begin{align*}
+W_h&:=\{v_h\in L^2(\Omega): v_h|_K\in W_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
+&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}
+\end{align*}  
+with $W_k(K):=\{v\in H^1(K) : \Delta v\in\mathbb P_{k-2}(K),\, \partial_nv|_F\in\mathbb P_{k-1}(F)\textrm{ for }F\in\mathcal F(K)\}$.
+However, $(\nabla_h u_h, \nabla_h v_h)$ is not computable, % based on the degrees of freedom \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, 
+and the method \eqref{eq:2023111} is not the standard nonconforming VEM in \cite{AyusodeDiosLipnikovManzini2016}.
+For the practical computation, a basis of $W_k(K)$ has to be solved approximately as shown in \cite[Remark 4.1]{CicuttinErnLemaire2019}, then the approximation of the space $W_h$ is no more a virtual element space.
+\end{remark}
+}
 

### 2023-03-10 stabfreevem_sinum.tex

@@
 hold
-rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
+rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
 To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
@@
 The corresponding norm and semi-norm are denoted respectively by
-$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. Denote by $L_0^2(K)$ the space of all functions in $L^2(K)$ with zero integral.
+$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. 
 Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
@@
 \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
-\XH{Recall (35) in \cite{Chen;Huang:2020Finite} that
+\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
 \begin{equation}\label{eq:20230205}
@@
 \end{equation}
-Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
-$$
-\boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
-$$
-where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.}
+% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
+% $$
+% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
+% $$
+% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.
+}
 
@@
 In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
-The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ mesh are shown in Figure \ref{fig:rate1}.
+The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Figure \ref{fig:rate1}.
 We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.

### 2023-03-11 reports/response.tex
updater

@@
 $$
-in \cite[Theorem 2]{BerroneBorioMarcon2021}. This means a sufficient condition for $l$ is 
+in \cite[Theorem 2]{BerroneBorioMarcon2021}. This means that a sufficient condition for $l$ is 
 $$
@@
 To ensure the $L^2$ projection
-$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
+$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
 for virtual element function $v\in V_k(K)$, we only require
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-One reviewer has questions on the proof of Lemma 4.1. Thus we modify the proof and keep it.
+One reviewer has questions on the proof of Lemma 4.1, and the proof of Lemma 4.1 is also helpful for the proof of Lemma 4.3. Thus we modify the proof and keep it.
 
@@
 Thanks for this suggestion. We have removed the proof of Theorem 5.3.
+We combine Section 5.2 and Section 5.3 in the revised manuscript.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+% One reviewer suggests removing the proof of Lemma 4.1, as it is standard in the virtual element literature.
+We agree with his suggestion, so we remove the proof of Lemma 4.1 in the revised manuscript.
+But we explain this comment in detail, and provide a complete proof of Lemma 4.1 here.
 \begin{itemize}
@@
 \end{align*}
-Then apply the Young's inequality to acquire
-\[
-|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}.
-\]
+Then apply the Young's inequality to acquire the inverse inequality
+\begin{equation*}%\label{eq:veminverse}
+|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}\quad\forall~v\in V_k(K).  
+\end{equation*}
 \end{itemize}
+
+% \vskip0.2cm
+% \noindent\textcolor{cyan}{The complete proof of the inverse inequality \eqref{eq:veminverse} (i.e. Lemma 4.1) is given as follows.}
+% \vskip0.2cm
+
+% By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
+% \[
+% h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
+% \]
+% Then apply (A.3) in \cite{ChenHuang2020ncvem} to get
+% \[
+% h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
+% \]
+% Employing the integration by parts and the Cauchy-Schwarz inequality, we have
+% \[
+% |v|_{1,K}^2=-(\Delta v,v)_K+(\partial_nv,v)_{\partial K}\leq\|\Delta v\|_{0,K}\|v\|_{0,K}+\|\partial_nv\|_{0,\partial K}\|v\|_{0,\partial K}.
+% \]
+% Combining the last two inequalities gives
+% \[
+% |v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
+% \]
+% which together with the multiplicative trace inequality and the Young's inequality yields the inverse inequality \eqref{eq:veminverse}.
 

### 2023-03-11 stabfreevem_sinum.tex

@@
 \end{equation}
+}
 % Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
@@
 % where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.
-}
 
@@
 \]
-
-It is obvious that 
-\begin{equation}\label{eq:cfmahbounedness}
-a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
-\end{equation}   
-And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
-the coercivity
-\begin{equation}\label{eq:cfmahcoercivity}
-|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
-\end{equation}  
-Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
-
-\begin{remark}\rm
+The stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
+
+% It is obvious that 
+% \begin{equation}\label{eq:cfmahbounedness}
+% a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
+% \end{equation}   
+% And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
+% the coercivity
+% \begin{equation}\label{eq:cfmahcoercivity}
+% |v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+% \end{equation}  
+% Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
+
+% \begin{remark}\rm
 By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the virtual element method \eqref{eq:cfmvem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
@@
 \end{equation*} 
-\end{remark}
+% \end{remark}
 
@@
 
-\subsection{Error analysis}
+% \subsection{Error analysis}
 Applying the standard error analysis for VEMs, we have the following error estimate for the VEM \eqref{eq:cfmvem}.
@@
 In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
-The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Figure \ref{fig:rate1}.
+The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}.
 We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
-And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Figure \ref{fig:rate2}.
+And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Fig.~\ref{fig:rate2}.
 Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the

### 2023-03-12 reports/response.tex
update numerical results

@@
 \usepackage{booktabs}
+\usepackage{subfigure}
+\usepackage{makecell}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+We try our best to proofread the manuscript carefully.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+For the convenience of narration, we abbreviate the standard conforming virtual emelemt
+method, the standard non-conforming virtual emelemt method, 
+the stabilization-free conforming virtual element method,
+and the stabilization-free non-conforming virtual element method as CVEM, NCVEM, SFCVEM, and SFNCVEM, respectively. 
+We implement all the experiments on a PC with AMD Ryzen
+5 3500U CPU and 64-bit Ubuntu 22.04 operating system.
+
+We construct three different hexagons shown in Fig.
+\ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods.
+Our numerical results show that, on each different hexagon, both SFNCVEM and SFCVEM have only one zero eigenvalue.
+In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig.
+\ref{fig:hexagon}, by which we can see that these quantities are comparable for four virtual element methods.
+\begin{figure}[htbp]
+\subfigure[Regular hexagon.]{
+\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics*[width=1in]{../figures/hexagon0.pdf}
+\end{minipage}}%% 
+\;\;% \quad
+\subfigure[Quasi-regular hexagon generated by regular
+    hexagon with a small perturbation.]
+{\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics*[width=1in]{../figures/hexagon1.pdf}
+\end{minipage}}
+\;\;% \quad
+\subfigure[Square with two hanging nodes.]
+{\begin{minipage}[t]{0.35\linewidth}
+\centering
+\includegraphics*[width=0.9in]{../figures/hexagon2.pdf}
+\end{minipage}}
+\caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
+    hexagon with a small perturbation (Middle), 
+and the square with two hanging nodes (Right).}
+\label{fig:hexagon}
+\end{figure}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the regular hexagon.}
+\label{tab:comparison0}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+NCVEM & 975.5693189 & 0.309674737 & 3150.303211 \\ \hline
+CVEM & 1012.488116 & 0.297206358 & 3406.683909 \\ \hline
+SFNCVEM & 992.5956147 & 0.318932029 & 3112.248147 \\ \hline
+SFCVEM & 1011.173331 & 0.298509692 & 3387.405362 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
+\label{tab:comparison1}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+NCVEM   & 935.2883848 & 0.279027715 & 3351.955143 \\ \hline
+CVEM    & 1014.672395 & 0.257370621 & 3942.456177 \\ \hline
+SFNCVEM & 997.4831245 & 0.282126359 & 3535.589964 \\ \hline
+SFCVEM  & 1047.876056 & 0.258970708 &
+4046.311124 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
+\label{tab:comparison2}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+ NCVEM   & 941.8571938&	0.21069027	&4470.340249 \\ \hline
+ CVEM    & 1046.755495&	0.200435123	&5222.4155 \\ \hline
+ SFNCVEM & 986.5963357&	0.212761106	&4637.108513 \\ \hline
+ SFCVEM  & 1061.651989&	0.202074633	&5253.761808 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+The only difference between the standard VEMs and the stabilization-free VEMs is the
+stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
+four different VEMs in detail by varying the degree $k$ and the mesh size $h$
+respectively. We use the mesh in Fig.~\ref{fig:mesh} for this experiment.
+\begin{figure}[htbp]
+\centering
+\includegraphics*[width=4.7cm]{../figures/convex.pdf}
+\caption{Convex polygon mesh.}
+\label{fig:mesh}
+\end{figure}
+The results presented in Tables
+\ref{tab:ptime} and \ref{tab:ttime} show that NCVEM, CVEM and SFNCVEM have similar assembling time. 
+However, SFCVEM requires more time due to the projection onto the one-order higher polynomial space.
+\begin{table}[htbp]
+\caption{Time consumed in assembling stiffness matrix of four VEMs with
+ $h=0.2$ and different $k$.}
+\label{tab:ptime}
+\centering
+\begin{tabular}{c|cccc}
+\hline
+$k$ & 2 & 4 & 8 & 10 \\
+\hline
+SFCVEM & 0.053684235 & 0.144996881 & 1.468627453 & 2.603836536 \\
+SFNCVEM & 0.022516727 & 0.065697193 & 0.806378841 & 1.554260015 \\
+CVEM & 0.021185875 & 0.059809923 & 0.600241184 & 1.160929918 \\
+NCVEM & 0.0213027 & 0.061014891 & 0.596506596 & 1.129639149 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\caption{Time consumed in assembling stiffness matrix of four VEMs with $k = 5$ and different $h$.}
+\label{tab:ttime}
+\centering
+\begin{tabular}{c|cccc}
+\hline
+$h$ &    1	& 0.25 & 0.0625 & 0.03125\\
+\hline
+SFCVEM & 0.039689541 & 0.199015379	& 1.74412179	& 4.75462532\\
+SFNCVEM & 0.018287182 & 0.100006819	& 0.81251812	& 2.465409517\\
+CVEM & 0.018686771 & 0.087426662	& 0.781031132	& 1.983617783\\
+NCVEM & 0.018309593 & 0.096345425	& 0.767129898	& 2.159288645\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+\begin{figure}[htbp]
+\centering
+\subfigure{\includegraphics[width=1in]{../figures/hexagon0.pdf}}
+    % \caption{Type I:5 tetrahedra}
+%%
+\subfigure{\includegraphics[width=1in]{../figures/hexagon3.pdf}}
+     %\caption{Type II: 24 tetrahedra}
+%%
+\subfigure{\includegraphics[width=1in]{../figures/hexagon4.pdf}}
+     %\caption{Trirectangular tetrahedron}
+%%
+\caption{The hexagons $H_0, H_1, H_2$.}
+  \label{fig:collapsehexagon} %% label for entire figure
+\end{figure} 
+We design two experiments to check the condition number of the stiffness
+matrices of the four VEMs.
+
+Firstly, we refer to the ``collapsing polygons'' experiment in
+\cite{Mascotto2018} and consider a sequence of hexagons
+$\{H_i\}_{i=0}^{\infty}$, where the vertices of $H_i$ are given by
+$A_i = (1, 0)$, $B_i = (0.5, a_i)$, $C_i = (-0.5, a)$, $D_i=(-1, 0)$, 
+$E_i = (-0.5, -a_i)$, and $F_i = (0.5, -a_i)$,
+where $a_i = \frac{\sqrt{3}}{2^{i+1}}$. The hexagons $H_0$, $H_1$ and $H_2$ are drawn
+in Fig.~\ref{fig:collapsehexagon}. 
+% We construct the virtual element space on $H_i$ and calculate the condition number
+% of the stiffness matrix of four methods. 
+As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber}, the condition numbers of stiffness
+matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.
+
+\begin{figure}[htbp]
+\subfigure[$k = 8$]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics*[width=2in]{../figures/collapsing_condition_number_8.pdf}
+\end{minipage}}%% 
+\quad \quad
+\subfigure[$k = 10$]
+{\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics*[width=2in]{../figures/collapsing_condition_number_10.pdf}
+\end{minipage}}
+\caption{The condition number of stiffness matrix of four VEMs on
+$\{H_i\}_{i=0}^{12}$.}
+\label{fig:collapsehexagon_conditionnumber}
+\end{figure}
+
+% \begin{figure}[htbp]
+% \centering
+% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_8.pdf}}
+% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_10.pdf}}
+% \caption{The condition number of stiffness matrix of four VEMs on
+% $\{H_i\}_{i=0}^{12}$, Left : $k = 8$, Right : $k = 10$.}
+%   \label{fig:collapsehexagon_conditionnumber0} %% label for entire figure
+% \end{figure}
+
+Secondly, we do the patch test for the Laplace equation, i.e.
+problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous.
+Take the exact solution $u=1+x+y$.
+%We adopt meshes in Fig.
+\ref{fig:polymesh}.
+% $$
+% \left\{\begin{aligned}
+% -\Delta u & = 0 \quad x \in \Omega\\
+% u & = g \quad x \in \partial \Omega
+% \end{aligned}\right.
+% $$
+% where $\Omega = (0, 1)^2, \ u = g = 1+x+y$. 
+Let $h_x$ and $h_y$ be mesh size in the $x$-direction and
+$y$-direction respectively.
+We examine the behavior of error $\|u - u_h\|_0$ of the four VEMs in the
+following three cases:
+\begin{enumerate}[(1)]
+\item Mesh in Fig.~\ref{fig:mesh}: Fix $h_x=h_y=0.2$ but vary $k= 1, 2, \ldots, 10$;
+\item Mesh in Fig.~\ref{fig:mesh}: Fix $k=3$ but vary $h_x=h_y=2^{-i}$ for $i=1,\ldots, 5$;
+\item Mesh in Fig.~\ref{fig:polymesh}: Fix $k=3$ and $h_x=0.2$, but vary $h_y=2^{-i}$ for $i=1,\ldots, 8$.
+\end{enumerate}
+\begin{figure}[htbp]
+\centering
+% \subfigure{\includegraphics[width=2in]{./figures/poly_mesh.pdf}}
+\subfigure{\includegraphics[width=2in]{../figures/mesh_hy.pdf}}
+\caption{The mesh of domain $(0, 1)\times(0, 1)$ with
+$h_x=0.2, h_y = 0.03125$.}
+% \caption{The meshes of domain $(0, 1)\times(0, 1)$. Left: $h = 0.1$. Right:
+% $h_x=0.2, h_y = 0.03125$.}
+  \label{fig:polymesh} %% label for entire figure
+\end{figure}
+The errors of four methods shown in Fig. \ref{fig:patchtest} are similar. 
+Since the error in the patch test
+grows as the condition number of the stiffness matrix grows, 
+the condition numbers of the stiffness matrix obtained by
+four methods are similar.
+\begin{figure}[htbp]
+\centering
+\subfigure{\includegraphics[width=1.7in]{../figures/patch_test_p.pdf}}
+%%
+\subfigure{\includegraphics[width=1.7in]{../figures/patch_test_h.pdf}}
+%%
+\subfigure{\includegraphics[width=1.7in]{../figures/patch_test_hy.pdf}}
+  \label{fig:patchtest} %% label for entire figure
+\caption{The $L^2$ error of patch test.}
+\end{figure}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+In the revised manuscript, we have provided many numerical experiments to compare our virtual element methods to the standard VEM and NCVEM.
+We also explain the benefit of the stabilization-free VEMs in the first paragraph in the introduction.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-...
+In the revised manuscript, we have provided many numerical experiments to compare our virtual element methods to the classical stabilized VEMs in two dimensions.
+The comparison in three dimensions will be provided in future work.
 

### 2023-03-12 stabfreevem_sinum.tex
update numerical results

@@
 
+% \begin{figure}[htbp]
+% \centering
+% \begin{minipage}[t]{0.49\linewidth}
+% \centering
+% \includegraphics[width=5cm]{./figures/convex.pdf}
+% %\caption{Numberical result of example with $\mathcal T_0$.}
+% \end{minipage}%
+% \begin{minipage}[t]{0.49\linewidth}
+% \centering
+% \includegraphics[width=5cm]{./figures/nonconvex.pdf}
+% %\caption{[Numberical result of example with $\mathcal T_1$].}
+% \end{minipage}%
+% \centering
+% \caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
+% $\mathcal T_1$(right).}
+% \label{fig:mesh}
+% \end{figure}
+
+\section{Numerical results}\label{sec:numericalexamps}
+In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
+virtual element method \eqref{eq:cfmvem}, which are abbreviated as SFNCVEM and SFCVEM respectively.
+For the convenience of narration, we also abbreviate the standard conforming virtual element
+method in \cite{BeiraoBrezziCangianiManziniEtAl2013} and non-conforming virtual element method  in \cite{CangianiManziniSutton2017} as CVEM and NCVEM respectively. 
+We implement all the experiments by using the FEALPy package \cite{fealpy} on a PC with AMD Ryzen
+5 3500U CPU and 64-bit Ubuntu 22.04 operating system.
+Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$.
+
+\subsection{Verification of convergence}
+% \begin{example}\label{ex}
+Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$.
+The exact solution and source term are given by
+\[
+u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
+\]
+% \end{example}
+
+The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
+$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$ in Fig. \ref{fig:mesh}, respectively. 
+In both SFNCVEM and SFCVEM, we choose $k = 1, 2, 5$.
+The numerical results of the SFNCVEM on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}.
+We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
+And the numerical results of the SFCVEM are presented in Fig.~\ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
+theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
 \begin{figure}[htbp]
+\subfigure[Convex polygon mesh $\mathcal T_0$.]{
+\begin{minipage}[t]{0.425\linewidth}
+\centering
+\includegraphics*[width=4.7cm]{./figures/convex.pdf}
+\end{minipage}}%% 
+\quad \quad
+\subfigure[Non-convex polygon mesh 
+$\mathcal T_1$.]
+{\begin{minipage}[t]{0.425\linewidth}
+\centering
+\includegraphics*[width=4.7cm]{./figures/nonconvex.pdf}
+\end{minipage}}
+\caption{Convex polygon mesh and non-convex polygon mesh.}
+\label{fig:mesh}
+\end{figure}
+\begin{figure}[htbp]
 \centering
@@
 \centering
-\includegraphics[width=5cm]{./figures/convex.pdf}
+\includegraphics[width=5.5cm]{./figures/ncvem_convex.pdf}
 %\caption{Numberical result of example with $\mathcal T_0$.}
@@
 \centering
-\includegraphics[width=5cm]{./figures/nonconvex.pdf}
-%\caption{[Numberical result of example with $\mathcal T_1$].}
-\end{minipage}%
-\centering
-\caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
-$\mathcal T_1$(right).}
-\label{fig:mesh}
-\end{figure}
-
-\section{Numerical results}\label{sec:numericalexamps}
-In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
-virtual element method \eqref{eq:cfmvem}.
-The numerical example is implemented by using the FEALPy package \cite{fealpy}
-
-% \begin{example}\label{ex}
-Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$
-on rectangular domain $\Omega = (0, 1)\times(0, 1)$. 
-The exact solution and source term are given by
-\[
-u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
-\]
-% \end{example}
-
-The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
-$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
-In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
-The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}.
-We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
-And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Fig.~\ref{fig:rate2}.
-Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
-theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
-\begin{figure}[htbp]
-\centering
-\begin{minipage}[t]{0.49\linewidth}
-\centering
-\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
-%\caption{Numberical result of example with $\mathcal T_0$.}
-\end{minipage}%
-\begin{minipage}[t]{0.49\linewidth}
-\centering
-\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
+\includegraphics[width=5.5cm]{./figures/ncvem_nonconvex.pdf}
 %\caption{[Numberical result of example with $\mathcal T_1$].}
@@
 \centering
-\includegraphics[width=6cm]{./figures/cvem_convex.pdf}
+\includegraphics[width=5.5cm]{./figures/cvem_convex.pdf}
 %\caption{Numberical result of example with $\mathcal T_0$.}
@@
 \centering
-\includegraphics[width=6cm]{./figures/cvem_nonconvex.pdf}
+\includegraphics[width=5.5cm]{./figures/cvem_nonconvex.pdf}
 %\caption{[Numberical result of example with $\mathcal T_1$].}
@@
 
+\subsection{The invertibility of the local stiffness matrices}
+
+We construct three different hexagons shown in Fig.
+\ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods.
+Our numerical results show that, on each different hexagon, both SFNCVEM and SFCVEM have only one zero eigenvalue.
+In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig.
+\ref{fig:hexagon}, by which we can see that these quantities are comparable for four virtual element methods.
+% \begin{figure}[htbp]
+% \centering
+% \subfigure{\includegraphics[width=1.4in]{./figures/hexagon0.pdf}}
+%     % \caption{Type I:5 tetrahedra}
+% %%
+% \subfigure{\includegraphics[width=1.4in]{./figures/hexagon1.pdf}}
+%      %\caption{Type II: 24 tetrahedra}
+% %%
+% \subfigure{\includegraphics[width=1.2in]{./figures/hexagon2.pdf}}
+%      %\caption{Trirectangular tetrahedron}
+% %%
+% \caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
+%     hexagon with a small perturbation (Middle), 
+% and the square with two hanging nodes (Right)}
+%   \label{fig:hexagon0} %% label for entire figure
+% \end{figure}
+\begin{figure}[htbp]
+\subfigure[Regular hexagon.]{
+\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics*[width=1in]{./figures/hexagon0.pdf}
+\end{minipage}}%% 
+\;\;% \quad
+\subfigure[Quasi-regular hexagon generated by regular
+    hexagon with a small perturbation.]
+{\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics*[width=1in]{./figures/hexagon1.pdf}
+\end{minipage}}
+\;\;% \quad
+\subfigure[Square with two hanging nodes.]
+{\begin{minipage}[t]{0.35\linewidth}
+\centering
+\includegraphics*[width=0.9in]{./figures/hexagon2.pdf}
+\end{minipage}}
+\caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
+    hexagon with a small perturbation (Middle), 
+and the square with two hanging nodes (Right).}
+\label{fig:hexagon}
+\end{figure}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the regular hexagon.}
+\label{tab:comparison0}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+NCVEM & 975.5693189 & 0.309674737 & 3150.303211 \\ \hline
+CVEM & 1012.488116 & 0.297206358 & 3406.683909 \\ \hline
+SFNCVEM & 992.5956147 & 0.318932029 & 3112.248147 \\ \hline
+SFCVEM & 1011.173331 & 0.298509692 & 3387.405362 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
+\label{tab:comparison1}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+NCVEM   & 935.2883848 & 0.279027715 & 3351.955143 \\ \hline
+CVEM    & 1014.672395 & 0.257370621 & 3942.456177 \\ \hline
+SFNCVEM & 997.4831245 & 0.282126359 & 3535.589964 \\ \hline
+SFCVEM  & 1047.876056 & 0.258970708 &
+4046.311124 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
+\label{tab:comparison2}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+ NCVEM   & 941.8571938&	0.21069027	&4470.340249 \\ \hline
+ CVEM    & 1046.755495&	0.200435123	&5222.4155 \\ \hline
+ SFNCVEM & 986.5963357&	0.212761106	&4637.108513 \\ \hline
+ SFCVEM  & 1061.651989&	0.202074633	&5253.761808 \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Comparison of assembling time}
+The only difference between the standard VEMs and the stabilization-free VEMs is the
+stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
+four different VEMs in detail by varying the degree $k$ and the mesh size $h$
+respectively. We use the mesh in Fig.~\ref{fig:mesh}(a) for this experiment.
+The results presented in Tables
+\ref{tab:ptime} and \ref{tab:ttime} show that NCVEM, CVEM and SFNCVEM have similar assembling time. 
+However, SFCVEM requires more time due to the projection onto the one-order higher polynomial space.
+\begin{table}[htbp]
+\caption{Time consumed in assembling stiffness matrix of four VEMs with
+ $h=0.2$ and different $k$.}
+\label{tab:ptime}
+\centering
+\begin{tabular}{c|cccc}
+\hline
+$k$ & 2 & 4 & 8 & 10 \\
+\hline
+SFCVEM & 0.053684235 & 0.144996881 & 1.468627453 & 2.603836536 \\
+SFNCVEM & 0.022516727 & 0.065697193 & 0.806378841 & 1.554260015 \\
+CVEM & 0.021185875 & 0.059809923 & 0.600241184 & 1.160929918 \\
+NCVEM & 0.0213027 & 0.061014891 & 0.596506596 & 1.129639149 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\caption{Time consumed in assembling stiffness matrix of four VEMs with $k = 5$ and different $h$.}
+\label{tab:ttime}
+\centering
+\begin{tabular}{c|cccc}
+\hline
+$h$ &    1	& 0.25 & 0.0625 & 0.03125\\
+\hline
+SFCVEM & 0.039689541 & 0.199015379	& 1.74412179	& 4.75462532\\
+SFNCVEM & 0.018287182 & 0.100006819	& 0.81251812	& 2.465409517\\
+CVEM & 0.018686771 & 0.087426662	& 0.781031132	& 1.983617783\\
+NCVEM & 0.018309593 & 0.096345425	& 0.767129898	& 2.159288645\\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Condition number of the stiffness
+matrix}
+\begin{figure}[htbp]
+\centering
+\subfigure{\includegraphics[width=1in]{./figures/hexagon0.pdf}}
+    % \caption{Type I:5 tetrahedra}
+%%
+\subfigure{\includegraphics[width=1in]{./figures/hexagon3.pdf}}
+     %\caption{Type II: 24 tetrahedra}
+%%
+\subfigure{\includegraphics[width=1in]{./figures/hexagon4.pdf}}
+     %\caption{Trirectangular tetrahedron}
+%%
+\caption{The hexagons $H_0, H_1, H_2$.}
+  \label{fig:collapsehexagon} %% label for entire figure
+\end{figure} 
+We design two experiments to check the condition number of the stiffness
+matrices of the four VEMs.
+
+Firstly, we refer to the ``collapsing polygons'' experiment in
+\cite{Mascotto2018} and consider a sequence of hexagons
+$\{H_i\}_{i=0}^{\infty}$, where the vertices of $H_i$ are given by
+$A_i = (1, 0)$, $B_i = (0.5, a_i)$, $C_i = (-0.5, a)$, $D_i=(-1, 0)$, 
+$E_i = (-0.5, -a_i)$, and $F_i = (0.5, -a_i)$,
+where $a_i = \frac{\sqrt{3}}{2^{i+1}}$. The hexagons $H_0$, $H_1$ and $H_2$ are drawn
+in Fig.~\ref{fig:collapsehexagon}. 
+% We construct the virtual element space on $H_i$ and calculate the condition number
+% of the stiffness matrix of four methods. 
+As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber}, the condition numbers of stiffness
+matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.
+
+\begin{figure}[htbp]
+\subfigure[$k = 8$]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics*[width=2in]{./figures/collapsing_condition_number_8.pdf}
+\end{minipage}}%% 
+\quad \quad
+\subfigure[$k = 10$]
+{\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics*[width=2in]{./figures/collapsing_condition_number_10.pdf}
+\end{minipage}}
+\caption{The condition number of stiffness matrix of four VEMs on
+$\{H_i\}_{i=0}^{12}$.}
+\label{fig:collapsehexagon_conditionnumber}
+\end{figure}
+
+% \begin{figure}[htbp]
+% \centering
+% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_8.pdf}}
+% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_10.pdf}}
+% \caption{The condition number of stiffness matrix of four VEMs on
+% $\{H_i\}_{i=0}^{12}$, Left : $k = 8$, Right : $k = 10$.}
+%   \label{fig:collapsehexagon_conditionnumber0} %% label for entire figure
+% \end{figure}
+
+Secondly, we do the patch test for the Laplace equation, i.e.
+problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous.
+Take the exact solution $u=1+x+y$.
+%We adopt meshes in Fig.
+\ref{fig:polymesh}.
+% $$
+% \left\{\begin{aligned}
+% -\Delta u & = 0 \quad x \in \Omega\\
+% u & = g \quad x \in \partial \Omega
+% \end{aligned}\right.
+% $$
+% where $\Omega = (0, 1)^2, \ u = g = 1+x+y$. 
+Let $h_x$ and $h_y$ be mesh size in the $x$-direction and
+$y$-direction respectively.
+We examine the behavior of error $\|u - u_h\|_0$ of the four VEMs in the
+following three cases:
+\begin{enumerate}[(1)]
+\item Mesh in Fig.~\ref{fig:mesh}(a): Fix $h_x=h_y=0.2$ but vary $k= 1, 2, \ldots, 10$;
+\item Mesh in Fig.~\ref{fig:mesh}(a): Fix $k=3$ but vary $h_x=h_y=2^{-i}$ for $i=1,\ldots, 5$;
+\item Mesh in Fig.~\ref{fig:polymesh}: Fix $k=3$ and $h_x=0.2$, but vary $h_y=2^{-i}$ for $i=1,\ldots, 8$.
+\end{enumerate}
+\begin{figure}[htbp]
+\centering
+% \subfigure{\includegraphics[width=2in]{./figures/poly_mesh.pdf}}
+\subfigure{\includegraphics[width=2in]{./figures/mesh_hy.pdf}}
+\caption{The mesh of domain $(0, 1)\times(0, 1)$ with
+$h_x=0.2, h_y = 0.03125$.}
+% \caption{The meshes of domain $(0, 1)\times(0, 1)$. Left: $h = 0.1$. Right:
+% $h_x=0.2, h_y = 0.03125$.}
+  \label{fig:polymesh} %% label for entire figure
+\end{figure}
+The errors of four methods shown in Fig. \ref{fig:patchtest} are similar. 
+Since the error in the patch test
+grows as the condition number of the stiffness matrix grows, 
+the condition numbers of the stiffness matrix obtained by
+four methods are similar.
+\begin{figure}[htbp]
+\centering
+\subfigure{\includegraphics[width=1.8in]{./figures/patch_test_p.pdf}}
+%%
+\subfigure{\includegraphics[width=1.8in]{./figures/patch_test_h.pdf}}
+%%
+\subfigure{\includegraphics[width=1.8in]{./figures/patch_test_hy.pdf}}
+  \label{fig:patchtest} %% label for entire figure
+\caption{The $L^2$ error of patch test.}
+\end{figure}
+
 % \section*{Acknowledgments}

### 2023-03-14 reports/response.tex
proofread

@@
 
-The authors greatly appreciate the questions and concerns the reviewers have raised in the report, as well as the careful reading that has fixed our grammatical errors.
+The authors greatly appreciate the questions and concerns the reviewers have raised in the reports, as well as the careful reading. 
+We have revised our manuscript in terms of your suggestions and polished the writing throughout. 
 Other than some single word typos, important changes are highlighted in colored texts in this revision.
@@
 \item 
-The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
 \item 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-Base on $d$-dimensional polytope $K\in \mathcal T_h$ and its simplicial partition $\mathcal T_K$ of $K$, we define the following $H(\div)$-conforming finite element spaces in this paper:
+Base on a $d$-dimensional polytope $K\in \mathcal T_h$ and its simplicial partition $\mathcal T_K$ of $K$, we define the following $H(\div)$-conforming finite element spaces in this paper:
 % For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
@@
 Thanks for this suggestion. We have removed the proof of Theorem 5.3.
-We combine Section 5.2 and Section 5.3 in the revised manuscript.
+We merge Section 5.2 and Section 5.3 into one section in the revised manuscript.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-For the convenience of narration, we abbreviate the standard conforming virtual emelemt
-method, the standard non-conforming virtual emelemt method, 
+For the convenience of narration, we abbreviate the standard conforming virtual element
+method, the standard non-conforming virtual element method, 
 the stabilization-free conforming virtual element method,
@@
 \ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods.
-Our numerical results show that, on each different hexagon, both SFNCVEM and SFCVEM have only one zero eigenvalue.
+Our numerical results show that, on all the three hexagons, both SFNCVEM and SFCVEM have only one zero eigenvalue.
 In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig.
-\ref{fig:hexagon}, by which we can see that these quantities are comparable for four virtual element methods.
+\ref{fig:hexagon}, from which we can see that these quantities are comparable for four virtual element methods.
 \begin{figure}[htbp]
@@
 \centering
-\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
+\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon.}
 \label{tab:comparison1}
@@
 \centering
-\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
+\caption{Comparison of eigenvalues and condition numbers on the square with two hanging nodes.}
 \label{tab:comparison2}
@@
 % of the stiffness matrix of four methods. 
-As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber}, the condition numbers of stiffness
+As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber} for $k=8$ and $k=10$, the condition numbers of stiffness
 matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.
@@
 
-Secondly, we do the patch test for the Laplace equation, i.e.
-problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous.
-Take the exact solution $u=1+x+y$.
-%We adopt meshes in Fig.
-\ref{fig:polymesh}.
+Secondly, we do the patch test for the Laplace equation with a nonhomogeneous Dirichlet boundary condition. Take the exact solution $u=1+x+y$. %We adopt meshes in Fig. \ref{fig:polymesh}.
 % $$
@@
 \end{figure}
-The errors of four methods shown in Fig. \ref{fig:patchtest} are similar. 
+The errors of the four methods shown in Fig.~\ref{fig:patchtest} are similar. 
 Since the error in the patch test
@@
 the condition numbers of the stiffness matrix obtained by
-four methods are similar.
+four methods are comparable.
 \begin{figure}[htbp]
@@
 \subfigure{\includegraphics[width=1.7in]{../figures/patch_test_hy.pdf}}
+\caption{The $L^2$ error of patch test.}
   \label{fig:patchtest} %% label for entire figure
-\caption{The $L^2$ error of patch test.}
 \end{figure}
@@
 Similar notations are used in \cite{ChenHuang2021divdiv,Chen;Huang:2020Finite}.
+In the revised manuscript, we define the notation $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}$ below DoFs (3.1)-(3.3).
 
@@
 
-The discrete bilinear form in this paper is defined as 
+The discrete bilinear form of the stabilization-free NCVEM in this paper is defined as 
 \[
@@
 \end{equation}
-The coercivity \eqref{eq:11} is (4.19) for the nonconforming virtual element method, and~(5.8) for the conforming virtual element method.
+The coercivity \eqref{eq:11} is (4.20) for the nonconforming virtual element method.
+%, and~(5.8) for the conforming virtual element method.
 
@@
 In the revised manuscript, we have provided many numerical experiments to compare our virtual element methods to the classical stabilized VEMs in two dimensions.
-The comparison in three dimensions will be provided in future work.
+The comparison in three dimensions will be presented in future work.
 

### 2023-03-14 ex_shared.tex
proofreading
update numerical results
proofread

@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage{subfigure}
+\usepackage{booktabs}
+\usepackage{makecell}
 % \usepackage[colorlinks=true, allcolors=blue]{hyperref}
@@
 \title{Stabilization-Free Virtual Element Methods\thanks{\today
-\funding{The second author is the corresponding author.
+\funding{%The second author is the corresponding author. 
 The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.
-The first and third authors were supported by NSFC (11871413) and in part by projects
-of Education Department of Hunan Provincial of China (19B534, 19A500).}}}
+The first and third authors were supported by NSFC (11871413).}}}
 
@@
   (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).}
-\and Xuehai Huang\thanks{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China (\email{huang.xuehai@sufe.edu.cn}).}
+\and Xuehai Huang\thanks{Corresponding author. School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China (\email{huang.xuehai@sufe.edu.cn}).}
 \and Huayi Wei\footnotemark[2]

### 2023-03-14 stabfreevem_sinum.tex
proofread

@@
 \begin{abstract}
-Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions.
+Stabilization-free virtual element methods (VEMs) in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
-Optimal error estimates are derived for these stabilization-free virtual element methods.
-Numerical results are provided to verify the convergence rates.
+Optimal error estimates are derived for these stabilization-free VEMs.
+Numerical experiments are provided to test the stabilization-free VEMs.
 \end{abstract}
@@
 \section{Introduction}
-\XH{A stabilization term is usually required in the virtual element methods (VEM) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems.
+\XH{A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems.
 The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy
@@
 for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.
-The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
 For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
@@
 
-Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}.
+Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}.
 \XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
@@
 $Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
-for virtual element function $v\in V_k(K)$, we require
+for virtual element function $v\in V_k(K)$, we require that
 $\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
@@
 macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
-the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
+the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
 $L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
@@
 
-By the aid of projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming virtual element method in arbitrary dimension and a stabilization-free conforming virtual element method in two dimensions  for second order elliptic problems.
-Indeed, these stabilization-free virtual element methods can be equivalently recast as
-primal mixed virtual element methods.
-We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free virtual element methods, and derive the optimal error estimates.
-
-The idea on constructing stabilization-free virtual element methods in this paper is simple,
-and can be extended to more virtual element methods and more partial differential equations.
+By the aid of the projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming VEM in arbitrary dimension and a stabilization-free conforming VEM in two dimensions  for second order elliptic problems.
+Indeed, these stabilization-free VEMs can be equivalently recast as
+primal mixed VEMs.
+We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free VEMs, and derive the optimal error estimates.
+Numerical experiments are provided to test these VEMs.
+
+The idea on constructing stabilization-free VEMs in this paper is simple,
+and can be extended to more VEMs and more partial differential equations.
 
@@
 In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
-A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+A stabilization-free nonconforming VEM in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming VEM in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
 Some numerical results are shown in Section \ref{sec:numericalexamps}.
@@
 Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
-For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
+Let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of a tensor $\boldsymbol{\tau}$.
 Denote by $\#S$ the number of elements in a finite set $S$.
 
-For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
-For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
-
-For a $d$-dimensional simplex $T$,
+Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
+
+Given a $d$-dimensional simplex $T$,
 let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of the point $\boldsymbol x$ corresponding to the vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
@@
 For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
-For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
-On the face $F\in\mathcal F_h$, define surface divergence
+For a smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
+On the face $F\in\mathcal F_h$, define the surface divergence
 \[
@@
 \]
-For a smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.
+Define the surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$ for a smooth function $v$.
 
@@
 $C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
-which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.
+which may take different values at different appearances. Let $A\eqsim B$ mean $A\lesssim B$ and $B\lesssim A$.
 
@@
 \subsection{$H(\div)$-conforming finite elements}
-For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
+For a $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
 \[
@@
 \end{align}
-for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$.
+for $T\in\mathcal T_K$.
+Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, \XH{and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable}.
 Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.
@@
 \begin{equation}\label{eq:Pkvectordecomp}  
-\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x},
-\end{equation}
-\XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
+\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
+\end{equation}
+% \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
 \XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
@@
 By $\skw\nabla\boldsymbol{v}=\boldsymbol{0}$, we get $\skw\nabla\boldsymbol{w}=\boldsymbol{0}$. 
-Apply Lemma~\ref{lem:skwgrad} to derive $\boldsymbol{w}=\boldsymbol{0}$. Thus $\boldsymbol{v}=\nabla q\in\nabla\mathbb P_k(T)$.
+Apply Lemma~\ref{lem:skwgrad} to derive $\boldsymbol{w}=\boldsymbol{0}$. Thus, $\boldsymbol{v}=\nabla q\in\nabla\mathbb P_k(T)$.
 \end{proof}
@@
 \end{equation}
-where $\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})$ means the kernel of operator $\boldsymbol{x}: \mathbb P_{k-2}(T;\mathbb K)\to\mathbb P_{k-1}(T;\mathbb R^d)$.
+where $\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x}):=\{\boldsymbol{\tau}\in\mathbb P_{k-2}(T;\mathbb K): \boldsymbol{\tau}\boldsymbol{x}=\boldsymbol{0}\}$.
 \end{lemma}
@@
 \]
-Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
+Hence, $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
 \end{proof}
@@
 \end{align*}
-By direct computation, $H\begin{pmatrix}
+By a direct computation, $H\begin{pmatrix}
 0 & 1 \\
@@
 \begin{proof}
-For $1\leq l\leq d$ but $l\neq i, j$, by the definition of $\boldsymbol{N}_{ij}$, it holds $\boldsymbol{N}_{ij}\boldsymbol{n}_l=\boldsymbol{0}$. Hence for $
+For $1\leq l\leq d$ but $l\neq i, j$, by the definition of $\boldsymbol{N}_{ij}$, it holds $\boldsymbol{N}_{ij}\boldsymbol{n}_l=\boldsymbol{0}$. Hence, for $
 \boldsymbol{\tau}=\sum\limits_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
@@
 where $p_{ij}=\boldsymbol{n}_i^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_j\in\mathbb P_{k}(T)$.
-Therefore $p_{ij}|_{F_i}=p_{ij}|_{F_j}=0$, which ends the proof.
+Therefore, $p_{ij}|_{F_i}=p_{ij}|_{F_j}=0$, which ends the proof.
 \end{proof}
@@
 % for $T\in\mathcal T_K$.
-Now let $w\in H^1(K)/\mathbb R$ be the solution of 
+Now let $w\in H^1(K)\cap L_0^2(K)$ be the solution of 
 \[
@@
 \[
-(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)/\mathbb R.
+(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)\cap L_0^2(K).
 \]
@@
 \end{align*}
-Finally \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.
+Finally, \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.
 \end{proof}
@@
 
-In this section we will develop a stabilization-free nonconforming virtual element method for the second order elliptic problem in arbitrary dimension
+In this section we will develop a stabilization-free nonconforming VEM for the second order elliptic problem in arbitrary dimension
 \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 \subsection{$H^1$-nonconforming virtual element}
-\XH{Several $H^1$-nonconforming virtual elements are developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
+\XH{Several $H^1$-nonconforming virtual elements have been developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
 In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.}
@@
 
-For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using only DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, and the $L^2$ projection
+For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, and the $L^2$ projection
 \begin{equation}\label{eq:QKPik}  
@@
 \end{equation}
-is also computable using only DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}.
+is also computable using DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}.
 
@@
 
-Finally \eqref{eq:VEMnormequivalenceQK} holds from \eqref{eq:QKPik} and \eqref{eq:VEMnormequivalencePiK}.
+Finally, \eqref{eq:VEMnormequivalenceQK} holds from \eqref{eq:QKPik} and \eqref{eq:VEMnormequivalencePiK}.
 \end{proof}
@@
 \subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$, which is vitally important to design stabilization-free virtual element methods.
+With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design stabilization-free virtual element methods.
 % Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
@@
 \end{equation}
-Consequently
+Consequently,
 \begin{equation}\label{eq:gradVknormequivalence}  
@@
 \]
-Finally we conclude \eqref{eq:localdiscreteinfsup} from \eqref{eq:20220204} and the last inequality.
+Finally, we conclude \eqref{eq:localdiscreteinfsup} from \eqref{eq:20220204} and the last inequality.
 \end{proof}
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization-free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:vem}
@@
 \begin{remark}\rm
-By introducing $\boldsymbol{\phi}_h=Q_{h,k-1}^{\div}\nabla_h u_h$, the virtual element method \eqref{eq:vem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k-1}^{\rm div}$ and $u_h\in V_h$ such that
+By introducing $\boldsymbol{\phi}_h=Q_{h,k-1}^{\div}\nabla_h u_h$, the VEM \eqref{eq:vem} can be rewritten as the following primal mixed VEM: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k-1}^{\rm div}$ and $u_h\in V_h$ such that
 \begin{equation*}
@@
 \begin{theorem}
-The stabilization free virtual element method \eqref{eq:vem} is \XH{well-posed}.
+The stabilization-free VEM \eqref{eq:vem} is \XH{well-posed}.
 \end{theorem}
@@
 \begin{theorem}\label{thm:errorestimateH1}
-Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:vem}.
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:vem}.
 Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$.
@@
 
-In this section we will develop a stabilization-free conforming virtual element method for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+In this section we will develop a stabilization-free conforming VEM for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
+For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload the notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
 
@@
 
-Recall the $H^1$-conforming virtual element in \cite{Huang2021,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
 The degrees of freedom are given by
@@
 
-For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using only the DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
-We have the norm equivalence of space $V_k(K)$ (cf. \cite[Lemma 4.7]{Huang2021} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$, it holds
+For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using the DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
+We have the norm equivalence of space $V_k(K)$ (cf. \cite[Lemma 4.7]{ChenHuangWei2022} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$, it holds
 \begin{equation}\label{eq:cfmVknormequivalence}
@@
 Employing the same argument as in Lemma~\ref{lem:gradVknormequivalence}, from  \eqref{eq:cfmVknormequivalence}, we get the norm equivalence
-\begin{equation}\label{eq:cfmgradVknormequivalence}  
+\begin{equation*}%\label{eq:cfmgradVknormequivalence}  
 \|Q_{K,k}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
-\end{equation}
+\end{equation*}
 
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization-free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:cfmvem}
@@
 \]
-The stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
+The stabilization-free VEM \eqref{eq:cfmvem} is uni-solvent.
 
@@
 % \begin{remark}\rm
-By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the virtual element method \eqref{eq:cfmvem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
+By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the VEM \eqref{eq:cfmvem} can be rewritten as the following primal mixed VEM: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
 \begin{equation*}
@@
 Then
-\begin{equation}\label{eq:cfmerrorestimateH1}
+\begin{equation*}%\label{eq:cfmerrorestimateH1}
 |u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
-\end{equation}
+\end{equation*}
 \end{theorem}
@@
 \section{Numerical results}\label{sec:numericalexamps}
-In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
+\XH{In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
 virtual element method \eqref{eq:cfmvem}, which are abbreviated as SFNCVEM and SFCVEM respectively.
@@
 5 3500U CPU and 64-bit Ubuntu 22.04 operating system.
-Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$.
+Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$. }
 
@@
 % \begin{example}\label{ex}
-Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$.
+Consider the second order elliptic problem~\eqref{eq:ellipitc2ndproblem} with $\alpha = 2$.
 The exact solution and source term are given by
@@
 $\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$ in Fig. \ref{fig:mesh}, respectively. 
-In both SFNCVEM and SFCVEM, we choose $k = 1, 2, 5$.
+We choose $k = 1, 2, 5$ in both SFNCVEM and SFCVEM.
 The numerical results of the SFNCVEM on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}.
@@
 \caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
-of nonconforming virtual element method \eqref{eq:vem} on 
+of nonconforming VEM \eqref{eq:vem} on 
 $\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
@@
 \caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0$ 
-of conforming virtual element method \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
+of conforming VEM \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
 $\mathcal T_1$(right) with $k=1, 2, 5$.}
@@
 
-We construct three different hexagons shown in Fig.
+\XH{We construct three different hexagons shown in Fig.
 \ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods.
-Our numerical results show that, on each different hexagon, both SFNCVEM and SFCVEM have only one zero eigenvalue.
+Our numerical results show that, on all the three hexagons, both SFNCVEM and SFCVEM have only one zero eigenvalue.
 In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig.
-\ref{fig:hexagon}, by which we can see that these quantities are comparable for four virtual element methods.
+\ref{fig:hexagon}, from which we can see that these quantities are comparable for four virtual element methods.
 % \begin{figure}[htbp]
@@
 \end{tabular}
-\end{table}
+\end{table}}
 
 \subsection{Comparison of assembling time}
-The only difference between the standard VEMs and the stabilization-free VEMs is the
+\XH{The only difference between the standard VEMs and the stabilization-free VEMs is the
 stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
@@
 \end{tabular}
-\end{table}
+\end{table}}
 
@@
 matrix}
-\begin{figure}[htbp]
+\XH{\begin{figure}[htbp]
 \centering
@@
 matrices of the four VEMs. 
-
+}
+
+\XH{
 Firstly, we refer to the ``collapsing polygons'' experiment in
@@
 % of the stiffness matrix of four methods. 
-As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber}, the condition numbers of stiffness
+As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber} for $k=8$ and $k=10$, the condition numbers of stiffness
 matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.
-
 \begin{figure}[htbp]
@@
 \end{figure}
+}
 
@@
 
-Secondly, we do the patch test for the Laplace equation, i.e.
+\XH{Secondly, we do the patch test for the Laplace equation, i.e.
 problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous.
@@
 \subfigure{\includegraphics[width=1.8in]{./figures/patch_test_hy.pdf}}
+\caption{The $L^2$ error of patch test.}
 \label{fig:patchtest} %% label for entire figure
-\caption{The $L^2$ error of patch test.}
 \end{figure}
-
-% \section*{Acknowledgments}
-% We would like to acknowledge the assistance of volunteers in putting
-% together this example manuscript and supplement.
+}
+
+\section*{Acknowledgement}
+The authors appreciate the anonymous reviewers for valuable suggestions and careful comments, which significantly improved an early version of this work.
 

### 2023-05-31 stabfreevem_sinum.tex
upload referees' reports

@@
 \section{Introduction}
-\XH{A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems.
+A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems.
 The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy
@@
 Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
-}
-
-Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}.
-\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
+
+Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
+Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
 The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}.
 Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
-\XH{By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and
-\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.}
+By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and
+\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.
 
@@
 the analysis is rather elaborate. 
-\XH{
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
 This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
-}
 
@@
 \end{enumerate}
-\XH{The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.}
+The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
 We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
@@
 To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
+Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
 
@@
 \section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
-\XH{
 In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
@@
 where $V_k(K)$ is the nonconforming virtual element space in Section \ref{sec:stabfreencfmvem}, and the conforming virtual element space in Section \ref{sec:stabfreecfmvem}.
-Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.}
+Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.
 
@@
 for $T\in\mathcal T_K$.
-Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, \XH{and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable}.
+Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.
 Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.
@@
 \]
-\XH{The DoFs are given by
+The DoFs are given by
 \[
@@
 \]
-for $T\in\mathcal T_K$.}
+for $T\in\mathcal T_K$.
 Define $\mathring{\boldsymbol{V}}^{\mathrm{RT}}(K):=\boldsymbol{V}^{\mathrm{RT}}(K)\cap \boldsymbol{H}_0(\div, K)$.
@@
 % \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
-\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
+Recall that \cite[(35)]{Chen;Huang:2020Finite}
 \begin{equation}\label{eq:20230205}
@@
 \end{equation}
-}
 % Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
@@
 \end{equation*}
-we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which \XH{together with \eqref{eq:20230205}} implies $\boldsymbol{w}=\boldsymbol{0}$.
+we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which together with \eqref{eq:20230205} implies $\boldsymbol{w}=\boldsymbol{0}$.
 \end{proof}
@@
 \begin{proof}
-\XH{By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
+By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
 $$
@@
 $$
-}
 % \begin{align*}
@@
 
-Next we focus on the proof of the \XH{lower bound}.
+Next we focus on the proof of the lower bound.
 Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$.
-Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and \XH{all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero}.
-\XH{By the norm equivalence on each simplex $T$ and the vanishing DoFs \eqref{BDMdof2}-\eqref{BDMdof3}, we get
+Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero.
+By the norm equivalence on each simplex $T$ and the vanishing DoFs \eqref{BDMdof2}-\eqref{BDMdof3}, we get
 \begin{align}\label{eq:20220324-5}
@@
 \end{equation}
-}
 % for $T\in\mathcal T_K$.
@@
 \]
-Obviously \XH{we obtain from \eqref{eq:202302011} that}
+Obviously we obtain from \eqref{eq:202302011} that
 \begin{equation}\label{eq:202302031}  
@@
 \end{equation}
-\XH{Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
+Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
 \begin{equation}\label{eq:20230203}  
@@
 V_{k-2}^{L^2}(K)=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for } T\in\mathcal T_K\}
-$.
-} Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$. \XH{We have
+$. Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$. We have
 \begin{equation}\label{eq:20220324-6}
@@
 \|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\end{equation}}
+\end{equation}
 By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$.
@@
 \]
-\XH{On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.}
+On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
 Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
@@
 \subsection{$H^1$-nonconforming virtual element}
-\XH{Several $H^1$-nonconforming virtual elements have been developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
-In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.}
+Several $H^1$-nonconforming virtual elements have been developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
+In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.
 The degrees of freedom are given by
-\XH{
 \begin{align}
@@
 \end{align}
-where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}
+where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
 
@@
 where %$\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ 
-\XH{$\mathbb P_{k-2}^{\perp}(K)$}
+$\mathbb P_{k-2}^{\perp}(K)$
 means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
@@
 \begin{proof}
-\XH{
 By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
@@
 \]
-which together with the multiplicative trace inequality and the Young's inequality yields \eqref{eq:veminverse}.}
+which together with the multiplicative trace inequality and the Young's inequality yields \eqref{eq:veminverse}.
 \end{proof}
@@
 \end{align*}
-which combined with \XH{both $H^1$-$L^2$ and $L^2$ boundary-$L^2$ bulk inverse inequalities} for polynomials implies
+which combined with both $H^1$-$L^2$ and $L^2$ boundary-$L^2$ bulk inverse inequalities for polynomials implies
 \[%\label{eq:VEMnormequivalencePiK}
@@
 \]
-Thanks to the Poincar\'e-Friedrichs inequality \XH{\cite{Necas1967}} %\cite[(2.15)]{BrennerSung2018} 
+Thanks to the Poincar\'e-Friedrichs inequality \cite{Necas1967} %\cite[(2.15)]{BrennerSung2018} 
 and \eqref{eq:projlocal2d2},
@@
 Since $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
-Apply the integration by parts \XH{and the fact $v=v-Q_{0}^Kv\in L_0^2(K)$} to get
+Apply the integration by parts and the fact $v=v-Q_{0}^Kv\in L_0^2(K)$ to get
 \begin{align*}
@@
 \end{align*}
-\XH{Noting that $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$, we have
+Noting that $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$, we have
 \[
 \|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}.
-\]}
+\]
 Then we obtain from the norm equivalence \eqref{eq:Vknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
@@
 \end{align*}
-We have the discrete Poincar\'e inequality \XH{\cite{Brenner2003}}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
+We have the discrete Poincar\'e inequality \cite{Brenner2003}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
 \begin{equation}\label{eq:vempoincareineqlty}
@@
 \end{equation}
-\XH{Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.}
+Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.
 % Introduce discrete spaces
@@
 \end{remark}
-\XH{
+
 \begin{remark}\rm
@@
 \end{remark}
-}
 
@@
 \[
-\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\XH{\eqsim} \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\eqsim \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
 \]
@@
 \begin{theorem}
-The stabilization-free VEM \eqref{eq:vem} is \XH{well-posed}.
+The stabilization-free VEM \eqref{eq:vem} is well-posed.
 \end{theorem}
@@
 The degrees of freedom are given by
-\XH{\begin{align}
+\begin{align}
 v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
@@
 \end{align}
-where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.}
+where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
 And the space of shape functions is
@@
 V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
-&\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\XH{\mathbb P_{k-2}^{\perp}(K)}\},
+&\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
 \end{align*}
@@
 \section{Numerical results}\label{sec:numericalexamps}
-\XH{In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
+In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
 virtual element method \eqref{eq:cfmvem}, which are abbreviated as SFNCVEM and SFCVEM respectively.
@@
 5 3500U CPU and 64-bit Ubuntu 22.04 operating system.
-Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$. }
+Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$.
 
@@
 
-\XH{We construct three different hexagons shown in Fig.
+We construct three different hexagons shown in Fig.
 \ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods.
@@
 \end{tabular}
-\end{table}}
+\end{table}
 
 \subsection{Comparison of assembling time}
-\XH{The only difference between the standard VEMs and the stabilization-free VEMs is the
+The only difference between the standard VEMs and the stabilization-free VEMs is the
 stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
@@
 \end{tabular}
-\end{table}}
+\end{table}
 
@@
 matrix}
-\XH{\begin{figure}[htbp]
+\begin{figure}[htbp]
 \centering
@@
 matrices of the four VEMs.
-}
-
-\XH{
+
 Firstly, we refer to the ``collapsing polygons'' experiment in
@@
 \end{figure}
-}
 
@@
 
-\XH{Secondly, we do the patch test for the Laplace equation, i.e.
+Secondly, we do the patch test for the Laplace equation, i.e.
 problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous.

### 2023-06-17 reports/response1.tex
initial response

% ----------------------------------------------------------------
% AMS-LaTeX Paper ************************************************
% **** -----------------------------------------------------------
\documentclass[10pt]{amsart}
%\textwidth 14.5cm
%\textheight 22cm
%\hoffset -1.5cm
%\voffset -2.2cm
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{color}
\usepackage{stmaryrd}
\usepackage{chemarrow}
\usepackage[all]{xy}
\usepackage[pdftex,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=blue,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{makecell}

%\usepackage{mathabx}
% ----------------------------------------------------------------
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small
% THEOREMS -------------------------------------------------------
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
%\numberwithin{equation}{section}
% MATH -----------------------------------------------------------
\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\Real}{\mathbb R}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
\newcommand{\BX}{\mathbf{B}(X)}
\newcommand{\A}{\mathcal{A}}

\newcommand{\dx}{\,{\rm d}x}
\newcommand{\dd}{\,{\rm d}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\mcal}{\mathcal}

\DeclareMathOperator*{\img}{img}
%\DeclareMathOperator*{\span}{span}
\newcommand{\sign}{\operatorname{sign}}
\newcommand{\curl}{\operatorname{curl}}
\renewcommand{\div}{\operatorname{div}}
%\renewcommand{\grad}{\operatorname{grad}}
\newcommand{\grad}{\operatorname{grad}}
\newcommand{\tr}{\operatorname{tr}}
% \DeclareMathOperator*{\tr}{tr}
\DeclareMathOperator*{\rot}{rot}
\DeclareMathOperator*{\var}{Var}
\newcommand{\dev}{\operatorname{dev}}
\newcommand{\sym}{\operatorname{sym}}
\newcommand{\skw}{\operatorname{skw}}
\newcommand{\spn}{\operatorname{spn}}
\newcommand{\mspn}{\operatorname{mspn}}
\newcommand{\mskw}{\operatorname{mskw}}
\newcommand{\vskw}{\operatorname{vskw}}
\newcommand{\vspn}{\operatorname{vspn}}
\newcommand{\defm}{\operatorname{def}}
\newcommand{\hess}{\operatorname{hess}}
% ----------------------------------------------------------------
\begin{document}

\title{\large Detailed Response to Referees}%

\date{}%
%\dedicatory{}%
%\commby{}%
% ----------------------------------------------------------------

\maketitle

The authors greatly appreciate the questions and concerns the reviewers have raised in the reports, as well as the careful reading. 
We have revised our manuscript in terms of your suggestions and polished the writing throughout. 
Other than some single word typos, important changes are highlighted in colored texts in this revision.

\tableofcontents

%We thank the Referee for the valuable comments that helped us to improve the manuscript. In
%the revised version of the manuscript, all non-minor modifications are highlighted in red colour.
%Below, we address the points raised in the report.

\vskip0.5cm
\section{Response to Reviewer 1}
\begin{enumerate}[1.]

\item \textsf{I still disagree with the nomenclature ``stabilization free''. I agree that you pass from bilinear forms
\begin{equation}\label{eq1}
a_h^K(u_h, v_h):= a^K(\Pi^{\nabla}u_h, \Pi^{\nabla}v_h) + S^K((I-\Pi^{\nabla})u_h, (I-\Pi^{\nabla})v_h)
\end{equation}
to discrete bilinear forms
$$
a_h^K(u_h, v_h):= a^K(\Pi^{?}u_h, \Pi^{?}v_h),
$$
where $\Pi^{?}$ is a projection operator into polynomial-type spaces. \vskip0.1cm
\noindent However, the dimension of the space onto which you project is (correctly) much larger than the dimension of the standard polynomial space that guarantees consistency.  \vskip0.1cm
\noindent 
Furthermore, $\Pi^{?}$ is computed using the degrees of freedom of the space. To me, this means that you found a new (and clever) stabilization of the method and analysed it. But the method is not stabilization free.  \vskip0.1cm
\noindent 
In fact, my strong opinion is that also the methods in [14, 15, 25] are not really stabilization free (in these references, $\Pi^{?}$ is a projection operator onto the space of polynomials of very high polynomial degree).
}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We try our best to proofread the manuscript carefully.

\medskip

\item \textsf{along the same lines, you pinpoint in the introduction several reasons why the stabilization term in \eqref{eq1} is bad. Let me comment on some of them:
\begin{itemize}
\item \textbf{condition number}: I agree that it depends on the choice of $S^K(\cdot, \cdot)$, but it equally depends on the $\Pi^{?}$ you employ, which in turns depends on the tessellations of the elements;
\item \textbf{eigenvalue problems}: I am aware of reference [17], I am not sure whether your approach solves all the issues therein discussed; at least, this is not so apparent from the numerical and theoretical results;
\item \textbf{a posteriori error estimates}: I totally agree that, e.g., for residual error estimators, the reliability and efficiency bounds depend on the stability constants $\alpha_*$ and $\alpha^*$ in
$$
\alpha_*|v_h|^2\leq S^K(v_h,v_h)\leq \alpha^*|v_h|^2.
$$
I also agree on the fact that this is kind of hideous (the dependence on the degree of accuracy or bad geometries may results in bad behaviours of such constants). However, with your approach you do not solve this issue. In fact, you still have inf-sup type constants that I expect to appear in all a posteriori bounds. I equally expect the need of using polynomial inverse estimates on tessellations, which means again dependence on $\Pi^{?}$.
\end{itemize}
What I am trying to convince you is that:
\begin{itemize}
\item I like your way of stabilizing the method as it gives a practical ``recipe'', which on simple benchmarks appears competitive with respect to other existing approaches;
\item I also think you may convince the engineering community to use your approach (as engineers are often scared of choosing parameters and so on);
\item however, the critiques you mention in the introduction about the standard VEM take place also in your framework!
\end{itemize}
.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\medskip

\item \textsf{in the introduction, lines 29-30, you mention paper [15] claiming that it ``outperforms the standard method [14]''. This is clear, as the standard ``dofi-dofi'' stabilization cannot work well for anisotropic diffusion problems (and I am pretty sure that other simple variants would work very well). So, the claim is wrong and should be replaced by ``outperforms the standard VEM with a specific choice of the stabilization that is not designed for anisotropic diffusion'' or something like that.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\medskip

\item \textsf{lines 425-426. I still disagree with the choice of the enhancing constraint. Your definition is most likely not correct. You do not have to impose that constraint for polynomials orthogonal to $\mathbb P_{p-2}(K)$ but rather any completion of that space into $\mathbb P_p(K)$. In fact, I would simply take the scaled monomial completion. And I can put my fingers on the fact that this is what you implement.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\medskip

\item \textsf{eq. (4.13). As the inf-sup constant plays the role of the ``stability constants'' you should underline its dependence on the polynomial degree, and the regularity of the mesh and the corresponding subtriangulation.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\medskip

\item \textsf{I would also state Theorem 4.9 with explicit constants in eq. (4.21). Notably, I would make it explicit the dependence of the inf-sup constant. In other words, write Theorem 4.9 as a standard Strang-type result and then show the convergence estimates.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\medskip

\item \textsf{I appreciate the numerical results and I now think that they are very convincing of one fact: your approach is not worse than the standard VEM approach. At the same time, you are not that better either. So, I would mitigate a bit your philosophical message in the introduction, saying that more benefits of your approach will be the study of future works. I think your paper is good. You should not (and need not) to oversell what you did.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\end{enumerate}

\section{Response to Reviewer 3}
%\smallskip \noindent {\bf Response to Reviewer 2}.

\begin{enumerate}[1.]
\item \textsf{The authors cite the unpublished paper [15] (S. Berrone, A. Borio, and F. Marcon. Lowest order stabilization free virtual element method for the Poisson equation. arXiv preprint arXiv:2103.16896, 2021) as another way to achieve a stabilization-free VEM; in response 3 to reviewer 1 the paper [15] is further commented. Unfortunately even the updated version is wrong, since estimate (45) giving a bound for the dimension of $P_l^\text{ker}(E)$ is false (there is a counterexample); this is the reason why [15] is still unpublished. Hence there is actually no proof at all that the method of [15] will produce a non-singular stiffness matrix. These considerations have no effects on the present paper, but nevertheless these facts must be reported in an appropriate way. \vskip0.1cm
\noindent 
I take the opportunity to encourage the authors NOT to cite unpublished results as they were true; the peer review process should still play a role in the scientific world!}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}

\end{enumerate}

\bibliographystyle{abbrv}
\bibliography{../paper}

% ----------------------------------------------------------------
\end{document}
% ----------------------------------------------------------------

### 2023-06-18 reports/response1.tex
revise the paper based on the reports

@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
-We try our best to proofread the manuscript carefully.
+Thanks for this comment. We replace ``Stabilization-Free Virtual Element Methods'' by 
+``Virtual Element Methods Without Extrinsic Stabilization'' in the revised manuscript.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+Yes. By the numerical results on the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
+matrix,
+the VEMs without extrinsic stabilization are competitive with respect to other existing VEMs.
+Now we emphasize that
+\begin{itemize}
+\item
+In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
+\item 
+Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
+%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
+\end{itemize}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+The theoretical part in [15] still has some problems as pointed out by another referee, and [15] is unpublished. We decide to remove the citation of paper [15] and papers depending on [15].
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+Any completion of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ can be used for the enhancing constraint.
+But we use the orthogonal complement space $\mathbb P_{k-2}^{\perp}(K)$ of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+With the orthogonal complement space $\mathbb P_{k-2}^{\perp}(K)$ for the enhancing constraint, it holds the following identity for the $L^2$ projection
+\begin{equation}\label{eq:QKPik}  
+Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv.
+\end{equation}
+Then we can compute the $L^2$ projection $Q_k^Kv$ by the right hand side of \eqref{eq:QKPik}.
+The identity \eqref{eq:QKPik} is not true for other choices of complement spaces.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+Thanks for this suggestion. We have emphasized it Lemma 4.4.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+Thanks for this suggestion. We rewrite Theorem 4.9 and its proof.
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+Yes. The performance of our VEMs and other existing VEMs is similar for simple benchmarks.
+Now we emphasize that
+\begin{itemize}
+\item
+In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
+\item 
+Since there is no additional stabilization term, our VEMs will be preferred in the engineering community. 
+%More benefits of the VEMs without extrinsic stabilization will be the study of future works.
+\end{itemize}
 
@@
 \smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
+Thanks for this suggestion. Now we remove the citation of paper [15], and the references depending on [15].
 

### 2023-06-18 stabfreevem_sinum.tex
revise the paper based on the reports

@@
 \begin{abstract}
-Stabilization-free virtual element methods (VEMs) in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
+Virtual element methods (VEMs) \XH{without extrinsic stabilization} in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
-Optimal error estimates are derived for these stabilization-free VEMs.
-Numerical experiments are provided to test the stabilization-free VEMs.
+Optimal error estimates are derived for these VEMs.
+Numerical experiments are provided to test the VEMs \XH{without extrinsic stabilization}.
 \end{abstract}
@@
 \begin{keywords}
-virtual element, stabilization-free, macro finite element, norm equivalence, error analysis
+virtual element, stabilization, macro finite element, norm equivalence, error analysis
 \end{keywords}
@@
 \section{Introduction}
-A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems.
+An additional stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form~\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+% , while the stabilization term also brings about some problems. 
 The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
@@
 for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.
-The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
-For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
+% The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization term dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
 The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
@@
 Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
-
-Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
-Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
-The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}.
+\XH{
+In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and reduces its practicality.}
+
+% Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
+% Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
+% The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}.
 Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
-By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and
-\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.
-
-The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
-the analysis is rather elaborate. 
+
+% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
+% the analysis is rather elaborate. 
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
-
-The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
+We intend to construct VEMs \XH{without extrinsic stabilization} in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
+The key to construct VEMs \XH{without extrinsic stabilization} is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
-To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
+\XH{To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.}
+% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
+% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
 
@@
 
-By the aid of the projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming VEM in arbitrary dimension and a stabilization-free conforming VEM in two dimensions  for second order elliptic problems.
-Indeed, these stabilization-free VEMs can be equivalently recast as
+By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM \XH{without extrinsic stabilization} in arbitrary dimension and a conforming VEM \XH{without extrinsic stabilization} in two dimensions  for second order elliptic problems.
+Indeed, these VEMs can be equivalently recast as
 primal mixed VEMs.
-We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free VEMs, and derive the optimal error estimates.
-Numerical experiments are provided to test these VEMs.
-
-The idea on constructing stabilization-free VEMs in this paper is simple,
+We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs \XH{without extrinsic stabilization}, and derive the optimal error estimates.
+
+\XH{Numerical experiments are provided to test the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
+matrix for the VEMs without extrinsic stabilization, which appear competitive with respect to other existing VEMs.}
+
+The idea on constructing VEMs \XH{without extrinsic stabilization} in this paper is simple,
 and can be extended to more VEMs and more partial differential equations.
+\XH{Since there is no additional stabilization term, these VEMs will be preferred in the engineering community.
+More benefits of the VEMs without extrinsic stabilization will be the study of future works.}
+By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
+\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for weak Galerkin finite element methods \XH{without extrinsic stabilization}.
 
@@
 In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
-A stabilization-free nonconforming VEM in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming VEM in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+A nonconforming VEM \XH{without extrinsic stabilization} in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM \XH{without extrinsic stabilization} in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
 Some numerical results are shown in Section \ref{sec:numericalexamps}.
@@
 
-\section{Stabilization-free nonconforming virtual element method}\label{sec:stabfreencfmvem}
+\section{Nonconforming virtual element method \XH{without extrinsic stabilization}}\label{sec:stabfreencfmvem}
 
@@
 
-In this section we will develop a stabilization-free nonconforming VEM for the second order elliptic problem in arbitrary dimension
+In this section we will develop a nonconforming VEM \XH{without extrinsic stabilization} for the second order elliptic problem in arbitrary dimension
 \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 \subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design stabilization-free virtual element methods.
+With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design virtual element methods \XH{without extrinsic stabilization}.
 % Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
@@
 \begin{equation}\label{eq:localdiscreteinfsup}    
-\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
-\end{equation}
+\|\nabla v\|_{0,K}\XH{\leq C_e}\sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K),
+\end{equation}
+\XH{where the constant $C_e\geq1$ is independent of the mesh size $h_K$, but depends on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$.}
 Consequently,
@@
 \begin{equation}\label{eq:vempoincareineqlty}
-\|v_h\|_0\lesssim |v_h|_{1,h} \quad\forall~v_h\in V_h.
-\end{equation}
+\|v_h\|_0\XH{\leq C_p} |v_h|_{1,h} \quad\forall~v_h\in V_h,
+\end{equation}
+\XH{where the constant $C_p$ is independent of the mesh size.}
 Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization-free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method \XH{without extrinsic stabilization} for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:vem}
@@
 \begin{remark}\rm
-The stabilization-free mixed-order HHO method for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
+The mixed-order HHO method \XH{without extrinsic stabilization} for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
 \begin{equation}\label{eq:2023111}    
@@
 \begin{equation}\label{eq:ahcoercivity}
-|v_h|_{1,h}^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+|v_h|_{1,h}^2\XH{\leq C_e^2} a_h(v_h, v_h)\quad\forall~v_h\in V_h.
 \end{equation}  
@@
 \[
-\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\eqsim \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\XH{\leq C_e^2} \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq \XH{C_e^2}a_h(v_h, v_h)\quad\forall~v_h\in V_h,
 \]
@@
 \begin{theorem}
-The stabilization-free VEM \eqref{eq:vem} is well-posed.
+The VEM \eqref{eq:vem} is well-posed.
 \end{theorem}
@@
 \begin{theorem}\label{thm:errorestimateH1}
-Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:vem}.
-Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$.
-Then
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:vem}. \XH{It holds that
+\begin{align}
+\label{eq:errorestimateH1abs}
+|u-u_h|_{1,h}&\leq C_e^2(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\alpha C_p\|u-Q_hu\|_0) \\
+\notag
+&\quad + \inf_{v_h\in V_h}\big((C_e^2+1)|u-v_h|_{1,h}+\alpha C_p\|u-v_h\|_0\big)\\
+\notag
+&\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
+\end{align}}
+Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
 \begin{equation}\label{eq:errorestimateH1}
@@
 \begin{proof}
-Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
-\[
-a(u,v_h-u_h)+(f, v_h-u_h)\lesssim h^k|u|_{k+1}|v_h-u_h|_{1,h}.
-\]
-Then 
-\begin{align*}
-&\quad \,a(u,v_h-u_h)-(f, Q_h(v_h-u_h)) \\
-&=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h) \\
-&=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
-&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h}.
-\end{align*}
-By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
+Take any $v_h\in V_h$. 
+\XH{By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
 \begin{align*}
@@
 &=(Q_{h,k-1}^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
-&\lesssim (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
-\end{align*}
-Summing the last two inequalities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
-\begin{align*}
-|v_h-u_h|_{1,h}^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
-&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h} \\
-&\quad + (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
-\end{align*}
-which implies
-\[
-|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_{h,k-1}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
-\]
+&\leq (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\alpha C_p\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
+\end{align*}
+Apply the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} to get
+\begin{equation*}
+C_e^{-2}|v_h-u_h|_{1,h}^2\leq a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)).
+\end{equation*}
+Combining the last two inequalities yields
+\begin{align*}
+|v_h-u_h|_{1,h}&\leq C_e^2(\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\alpha C_p\|u-Q_hv_h\|_0) \\
+&\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
+\end{align*}
 Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k-1}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
@@
 \]
-By combining the last three inequalities, we obtain
-\[
-|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|u-v_h\|_{1,h},
-\]
-which together with the triangle inequality yields
-\[
-|u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\inf_{v_h\in V_h}\|u-v_h\|_{1,h}.
-\]
-At last, \eqref{eq:errorestimateH1} follows from the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
+Then we obtain from the last three inequalities that
+\begin{align*}
+|v_h-u_h|_{1,h}&\leq C_e^2\big(\|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_{1,h}+\alpha C_p(\|u-Q_hu\|_0+\|u-v_h\|_0)\big) \\
+&\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
+\end{align*}
+Thus, we acquire \eqref{eq:errorestimateH1abs} from the last inequality and the triangle inequality.}
+
+\XH{Next we derive estimate \eqref{eq:errorestimateH1}. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
+\[
+a(u, w_h)+(f, w_h)\lesssim h^k|u|_{k+1}|w_h|_{1,h}\quad\forall~w_h\in V_h.
+\]
+Then 
+\begin{align*}
+a(u, w_h)-(f, Q_hw_h) 
+&=a(u, w_h)+(f, w_h)+(f-Q_hf, w_h) \\
+&=a(u, w_h)+(f, w_h)+(f-Q_hf, w_h-Q_h^0w_h) \\
+&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|w_h|_{1,h}.
+\end{align*}
+At last, \eqref{eq:errorestimateH1} follows from \eqref{eq:errorestimateH1abs} and the approximation of $V_h$ \cite{ChenHuang2020ncvem}.}
+% Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
+% \[
+% a(u,v_h-u_h)+(f, v_h-u_h)\lesssim h^k|u|_{k+1}|v_h-u_h|_{1,h}.
+% \]
+% Then 
+% \begin{align*}
+% &\quad \,a(u,v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+% &=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h) \\
+% &=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
+% &\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h}.
+% \end{align*}
+% By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
+% \begin{align*}
+% &\quad a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\\
+% &=(Q_{h,k-1}^{\div}\nabla_h v_h, Q_{h,k-1}^{\div}\nabla_h(v_h-u_h))-(\nabla u, \nabla_h(v_h-u_h))\\
+% &\quad +\alpha(Q_hv_h, Q_h(v_h-u_h))-\alpha(u, v_h-u_h) \\
+% &=(Q_{h,k-1}^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
+% &\lesssim (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
+% \end{align*}
+% Summing the last two inequalities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
+% \begin{align*}
+% |v_h-u_h|_{1,h}^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+% &\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h} \\
+% &\quad + (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
+% \end{align*}
+% which implies
+% \[
+% |v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_{h,k-1}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
+% \]
+% Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k-1}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
+% \begin{align*}    
+% \|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_{h,k-1}^{\div}\nabla u\|_0+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0\\
+% &= \|\nabla u-Q_h^{k-1}\nabla u-Q_{h,k-1}^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
+% &\quad+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0 \\
+% &\leq \|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_{1,h}.
+% \end{align*}
+% Similarly, we have
+% \[
+% \|u-Q_hv_h\|_0\leq \|u-Q_hu\|_0+\|Q_h(u-v_h)\|_0\leq \|u-Q_hu\|_0+\|u-v_h\|_0.
+% \]
+% By combining the last three inequalities, we obtain
+% \[
+% |v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|u-v_h\|_{1,h},
+% \]
+% which together with the triangle inequality yields
+% \[
+% |u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\inf_{v_h\in V_h}\|u-v_h\|_{1,h}.
+% \]
+% At last, \eqref{eq:errorestimateH1} follows from the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
 \end{proof}
 
-\section{Stabilization-free conforming virtual element method}\label{sec:stabfreecfmvem}
-
-In this section we will develop a stabilization-free conforming VEM for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+\section{Conforming virtual element method \XH{without extrinsic stabilization}}\label{sec:stabfreecfmvem}
+
+In this section we will develop a conforming VEM \XH{without extrinsic stabilization} for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization-free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method \XH{without extrinsic stabilization} for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:cfmvem}
@@
 \]
-The stabilization-free VEM \eqref{eq:cfmvem} is uni-solvent.
+The VEM \eqref{eq:cfmvem} is uni-solvent.
 
@@
 \section{Numerical results}\label{sec:numericalexamps}
-In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
+In this section, we will numerically test the nonconforming virtual element method \eqref{eq:vem} and the conforming
 virtual element method \eqref{eq:cfmvem}, which are abbreviated as SFNCVEM and SFCVEM respectively.
@@
 \subsection{Comparison of assembling time}
-The only difference between the standard VEMs and the stabilization-free VEMs is the
+The only difference between the standard VEMs and the VEMs \XH{without extrinsic stabilization} is the
 stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
@@
 As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber} for $k=8$ and $k=10$, the condition numbers of stiffness
-matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.
+matrices of the VEMs \XH{without extrinsic stabilization} are smaller than those of the standard methods when $i$ is large.
 \begin{figure}[htbp]

### 2023-06-24 ex_shared.tex
revise the paper based on the reports
update funding and reference file

@@
 % Sets running headers as well as PDF title and authors
-\headers{Stabilization-Free VEM}{C. Chen, X. Huang and H. Wei}
+\headers{VEM Without Extrinsic Stabilization}{C. Chen, X. Huang and H. Wei}
 
@@
 % is automatically inserted before the title.
-\title{Stabilization-Free Virtual Element Methods\thanks{\today
+\title{Virtual Element Methods Without Extrinsic Stabilization\thanks{\today
 \funding{%The second author is the corresponding author. 
-The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.
-The first and third authors were supported by NSFC (11871413).}}}
+The second author was supported by the National Natural Science Foundation of
+China {\color{red} (NSFC) (Grant No. 12171300)}, and the Natural Science Foundation of Shanghai
+{\color{red}(Grant No. 21ZR1480500)}. The first and third authors were supported by the National Natural
+Science Foundation of China (NSFC) (Grant No. 12261131501, 11871413), and the construction of innovative provinces in Hunan Province (Grant No. 2021GK1010)}}}
 

### 2023-06-29 reports/response1.tex
typo
adjust mesh assumption (A2)

@@
 The authors greatly appreciate the questions and concerns the reviewers have raised in the reports, as well as the careful reading. 
-We have revised our manuscript in terms of your suggestions and polished the writing throughout. 
+We have revised our manuscript in terms of your suggestions. 
 Other than some single word typos, important changes are highlighted in colored texts in this revision.
@@
 \item
-In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and reduces its practicality.
+In existing VEMs, the additional stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is not easy and will reduce its practicality.
 \item 

### 2023-06-29 stabfreevem_sinum.tex
adjust mesh assumption (A2)

@@
 \XH{
-In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and reduces its practicality.}
+In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.}
 
@@
 hold
-rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
+rather than the norm equivalence \eqref{intro:gradVknormequiv}, then an additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
 \XH{To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.}
@@
 $L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
-a conforming finite element for differential $(d-2)$-form in
+a conforming finite element for the differential $(d-2)$-form in
 \cite{ArnoldFalkWinther2006,Arnold2018}.
@@
 
- \item[(A2)] There exists a quasi-uniform simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
+ \item[(A2)] \XH{There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
+For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$.
+Assume simplicial partition $\mathcal T_K$ is quasi-uniform.}
 \end{itemize}
@@
 
-For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$.
-Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively.
-Set
+% For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
+Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
 \[

### 2023-08-13 ex_shared.tex
remove \XH

@@
 The second author was supported by the National Natural Science Foundation of
-China {\color{red} (NSFC) (Grant No. 12171300)}, and the Natural Science Foundation of Shanghai
-{\color{red}(Grant No. 21ZR1480500)}. The first and third authors were supported by the National Natural
+China (NSFC) (Grant No. 12171300), and the Natural Science Foundation of Shanghai
+(Grant No. 21ZR1480500). The first and third authors were supported by the National Natural
 Science Foundation of China (NSFC) (Grant No. 12261131501, 11871413), and the construction of innovative provinces in Hunan Province (Grant No. 2021GK1010)}}}

### 2023-08-13 stabfreevem_sinum.tex
remove \XH

@@
 \begin{abstract}
-Virtual element methods (VEMs) \XH{without extrinsic stabilization} in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
+Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
 Optimal error estimates are derived for these VEMs.
-Numerical experiments are provided to test the VEMs \XH{without extrinsic stabilization}.
+Numerical experiments are provided to test the VEMs without extrinsic stabilization.
 \end{abstract}
@@
 Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
-\XH{
-In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.}
+In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.
 
@@
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs \XH{without extrinsic stabilization} in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
-The key to construct VEMs \XH{without extrinsic stabilization} is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
+We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
+The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 rather than the norm equivalence \eqref{intro:gradVknormequiv}, then an additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
-\XH{To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.}
+To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
 % $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
@@
 
-By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM \XH{without extrinsic stabilization} in arbitrary dimension and a conforming VEM \XH{without extrinsic stabilization} in two dimensions  for second order elliptic problems.
+By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM without extrinsic stabilization in arbitrary dimension and a conforming VEM without extrinsic stabilization in two dimensions  for second order elliptic problems.
 Indeed, these VEMs can be equivalently recast as
 primal mixed VEMs.
-We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs \XH{without extrinsic stabilization}, and derive the optimal error estimates.
-
-\XH{Numerical experiments are provided to test the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
-matrix for the VEMs without extrinsic stabilization, which appear competitive with respect to other existing VEMs.}
-
-The idea on constructing VEMs \XH{without extrinsic stabilization} in this paper is simple,
+We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs without extrinsic stabilization, and derive the optimal error estimates.
+
+Numerical experiments are provided to test the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
+matrix for the VEMs without extrinsic stabilization, which appear competitive with respect to other existing VEMs.
+
+The idea on constructing VEMs without extrinsic stabilization in this paper is simple,
 and can be extended to more VEMs and more partial differential equations.
-\XH{Since there is no additional stabilization term, these VEMs will be preferred in the engineering community.
-More benefits of the VEMs without extrinsic stabilization will be the study of future works.}
+Since there is no additional stabilization term, these VEMs will be preferred in the engineering community. More benefits of the VEMs without extrinsic stabilization will be the study of future works.
 By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
-\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for weak Galerkin finite element methods \XH{without extrinsic stabilization}.
+\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for weak Galerkin finite element methods without extrinsic stabilization.
 
@@
 In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
-A nonconforming VEM \XH{without extrinsic stabilization} in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM \XH{without extrinsic stabilization} in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+A nonconforming VEM without extrinsic stabilization in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM without extrinsic stabilization in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
 Some numerical results are shown in Section \ref{sec:numericalexamps}.
@@
 
- \item[(A2)] \XH{There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
+ \item[(A2)] There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
 For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$.
-Assume simplicial partition $\mathcal T_K$ is quasi-uniform.}
+Assume simplicial partition $\mathcal T_K$ is quasi-uniform.
 \end{itemize}
@@
 \end{equation}
-% \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
+% {where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
 Recall that \cite[(35)]{Chen;Huang:2020Finite}
@@
 
-\section{Nonconforming virtual element method \XH{without extrinsic stabilization}}\label{sec:stabfreencfmvem}
+\section{Nonconforming virtual element method without extrinsic stabilization}\label{sec:stabfreencfmvem}
 
@@
 
-In this section we will develop a nonconforming VEM \XH{without extrinsic stabilization} for the second order elliptic problem in arbitrary dimension
+In this section we will develop a nonconforming VEM without extrinsic stabilization for the second order elliptic problem in arbitrary dimension
 \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 \subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design virtual element methods \XH{without extrinsic stabilization}.
+With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design virtual element methods without extrinsic stabilization.
 % Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
@@
 \begin{equation}\label{eq:localdiscreteinfsup}    
-\|\nabla v\|_{0,K}\XH{\leq C_e}\sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K),
-\end{equation}
-\XH{where the constant $C_e\geq1$ is independent of the mesh size $h_K$, but depends on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$.}
+\|\nabla v\|_{0,K}\leq C_e\sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K),
+\end{equation}
+where the constant $C_e\geq1$ is independent of the mesh size $h_K$, but depends on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$.
 Consequently,
@@
 \begin{equation}\label{eq:vempoincareineqlty}
-\|v_h\|_0\XH{\leq C_p} |v_h|_{1,h} \quad\forall~v_h\in V_h,
-\end{equation}
-\XH{where the constant $C_p$ is independent of the mesh size.}
+\|v_h\|_0\leq C_p |v_h|_{1,h} \quad\forall~v_h\in V_h,
+\end{equation}
+where the constant $C_p$ is independent of the mesh size.
 Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method \XH{without extrinsic stabilization} for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method without extrinsic stabilization for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:vem}
@@
 \begin{remark}\rm
-The mixed-order HHO method \XH{without extrinsic stabilization} for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
+The mixed-order HHO method without extrinsic stabilization for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
 \begin{equation}\label{eq:2023111}    
@@
 \begin{equation}\label{eq:ahcoercivity}
-|v_h|_{1,h}^2\XH{\leq C_e^2} a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+|v_h|_{1,h}^2\leq C_e^2 a_h(v_h, v_h)\quad\forall~v_h\in V_h.
 \end{equation}  
@@
 \[
-\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\XH{\leq C_e^2} \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq \XH{C_e^2}a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\leq C_e^2 \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq C_e^2a_h(v_h, v_h)\quad\forall~v_h\in V_h,
 \]
@@
 \begin{theorem}\label{thm:errorestimateH1}
-Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:vem}. \XH{It holds that
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:vem}. It holds that
 \begin{align}
@@
 &\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
-\end{align}}
+\end{align}
 Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
@@
 Take any $v_h\in V_h$. 
-\XH{By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
+By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
 \begin{align*}
@@
 \end{align*}
-Thus, we acquire \eqref{eq:errorestimateH1abs} from the last inequality and the triangle inequality.}
-
-\XH{Next we derive estimate \eqref{eq:errorestimateH1}. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
+Thus, we acquire \eqref{eq:errorestimateH1abs} from the last inequality and the triangle inequality.
+
+Next we derive estimate \eqref{eq:errorestimateH1}. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
 \[
@@
 \end{align*}
-At last, \eqref{eq:errorestimateH1} follows from \eqref{eq:errorestimateH1abs} and the approximation of $V_h$ \cite{ChenHuang2020ncvem}.}
+At last, \eqref{eq:errorestimateH1} follows from \eqref{eq:errorestimateH1abs} and the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
 % Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
@@
 
-\section{Conforming virtual element method \XH{without extrinsic stabilization}}\label{sec:stabfreecfmvem}
-
-In this section we will develop a conforming VEM \XH{without extrinsic stabilization} for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+\section{Conforming virtual element method without extrinsic stabilization}\label{sec:stabfreecfmvem}
+
+In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method \XH{without extrinsic stabilization} for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method without extrinsic stabilization for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:cfmvem}
@@
 \subsection{Comparison of assembling time}
-The only difference between the standard VEMs and the VEMs \XH{without extrinsic stabilization} is the
+The only difference between the standard VEMs and the VEMs without extrinsic stabilization is the
 stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
@@
 As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber} for $k=8$ and $k=10$, the condition numbers of stiffness
-matrices of the VEMs \XH{without extrinsic stabilization} are smaller than those of the standard methods when $i$ is large.
+matrices of the VEMs without extrinsic stabilization are smaller than those of the standard methods when $i$ is large.
 \begin{figure}[htbp]

### 2023-08-15 stabfreevem_sinum.tex
add mesh asumption
all the faces of each polytope are simplices

@@
 \begin{abstract}
-Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
+Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices}.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
@@
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
+We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices}, in a unified way.
 The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
@@
 is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
-these considerations and the direct decomposition of an $H(\div)$-conforming
-macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
+these considerations and the direct decomposition of the $H(\div)$-conforming
+macro finite element space $\mathbb{V}_{k}^{\rm div}(K)$, we propose
 the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
@@
 
-By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM without extrinsic stabilization in arbitrary dimension and a conforming VEM without extrinsic stabilization in two dimensions  for second order elliptic problems.
+By the aid of the projector $Q_{K,k}^{\div}$, \XH{we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.}
 Indeed, these VEMs can be equivalently recast as
@@
 In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
-A nonconforming VEM without extrinsic stabilization in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM without extrinsic stabilization in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+A nonconforming VEM without extrinsic stabilization in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM without extrinsic stabilization in arbitrary dimension is devised in Section \ref{sec:stabfreecfmvem}.
 Some numerical results are shown in Section \ref{sec:numericalexamps}.
@@
 
-Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+Given a $d$-dimensional polytope $K$, \XH{let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
+Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.}
+% let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
 For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
@@
  \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter.
+\XH{All the $(d-1)$-dimensional faces of $K$ are simplices.}
 
@@
 For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$.
-Assume simplicial partition $\mathcal T_K$ is quasi-uniform.
+Assume simplicial partition $\mathcal T_K$ is quasi-uniform, \XH{and all the $(d-1)$-dimensional faces of $K$ are also faces of $\mathcal T_K$.}
 \end{itemize}
@@
 % For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
-Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
-\[
-\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
-\]
+% Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. 
+% Set 
+% \[
+% \mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
+% \]
 
@@
 \begin{equation}\label{eq:20220324-4}
-\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)-1.
+\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\XH{\mathcal F(K)}-1.
 \end{equation}
@@
 \[
-\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
+\XH{\mathbb{V}_{k-1}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
 \]
@@
 \[
-\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
-\]
-Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.
-
-In the following lemma we present a direct sum decomposition of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+\XH{\mathbb{V}_{0}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
+\]
+Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$, $\XH{\mathbb{V}_{0}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and $\XH{\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.
+
+In the following lemma we present a direct sum decomposition of space $\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$.
 
@@
 \begin{equation}\label{eq:Vdivlocaldecomp}
-\boldsymbol{V}_{k-1}^{\rm div}(K)=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
+\XH{\mathbb{V}_{k-1}^{\rm div}(K)}=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
 \end{equation}
@@
 \begin{equation*}
-\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
+\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\mathbb{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
 \end{equation*}
@@
 Since $\div:(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\to\mathbb P_{k-2}(K)$ is bijective \cite[Lemma 3.1]{ChenHuang2021divdiv}, we have $\div\skw \boldsymbol{V}_{k}^{d-2}(K)\cap(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)=\{\boldsymbol{0}\}$.
-Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \boldsymbol{V}_{k-1}^{\rm div}(K)$.
-
-On the other side, for $\boldsymbol{\phi}\in \boldsymbol{V}_{k-1}^{\rm div}(K)$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
-$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$.
+Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \XH{\mathbb{V}_{k-1}^{\rm div}(K)}$.
+
+On the other side, for $\boldsymbol{\phi}\in \XH{\mathbb{V}_{k-1}^{\rm div}(K)}$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
+$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\XH{\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$.
 Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$.
@@
 
-Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$
+Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space \XH{$\mathbb{V}_{k-1}^{\rm div}(K)$}
 \begin{align}
-    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \label{Vdivdof1}\\
+    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\XH{\mathcal F(K)}, \label{Vdivdof1}\\
     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
@@
 \begin{lemma}
-The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space \XH{$\mathbb{V}_{k-1}^{\rm div}(K)$}.
 \end{lemma}
@@
 \begin{align*}
-&\quad {k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
-&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\boldsymbol{V}_{k-1}^{\rm div}(K).
+&\quad {k+d-2\choose d-1}\#\XH{\mathcal F(K)}+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
+&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\XH{\mathbb{V}_{k-1}^{\rm div}(K)}.
 \end{align*}
@@
 
-Assume $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish.
+Assume $\boldsymbol{\phi}\in\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish.
 By the vanishing DoF~\eqref{Vdivdof1}, $\boldsymbol{\phi}\in \boldsymbol{H}_0(\div, K)$ and $\div\boldsymbol{\phi}\in L_0^2(K)$.
@@
 
-Next we consider the norm equivalence of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+Next we consider the norm equivalence of space \XH{$\mathbb{V}_{k-1}^{\rm div}(K)$}.
 
 \begin{lemma}\label{lem:Vkm1divnormequivalence}
-For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+For $\boldsymbol{\phi}\in\XH{\mathbb{V}_{k-1}^{\rm div}(K)}$, it holds the norm equivalence
 \begin{equation}\label{eq:Vkm1divnormequivalence}
-\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\XH{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 \end{equation}
-For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
+For $F\in\XH{\mathcal F(K)}$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
 $$
@@
 $$
-\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+\sum_{F\in\XH{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\XH{\mathcal F(K)}}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
 $$ 
@@
 $$
-h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\XH{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
 $$
@@
 \begin{align}\label{eq:20220324-5}
-\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
+\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\XH{\mathcal F(K)}}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
 \end{align}
@@
 \|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
-\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
+\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\XH{\mathcal F(K)}}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
 \end{equation}
@@
 \begin{equation}\label{eq:202302031}  
-\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\XH{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 \begin{equation}\label{eq:20220324-7}
-\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\XH{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 
-Let 
-\[
-\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): (\boldsymbol{\phi}\cdot\boldsymbol{n})|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
-\]
-On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
-Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
-\begin{align}
-    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
-    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
-    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
-\end{align}
-
-As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
-\begin{corollary}
-For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
-\begin{equation}\label{eq:Vkm1divnormequiv}
-\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\end{equation}
-\end{corollary}
+% Let 
+% \[
+% \mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): (\boldsymbol{\phi}\cdot\boldsymbol{n})|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
+% \]
+% On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+% Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
+% \begin{align}
+%     (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
+%     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
+%     (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
+% \end{align}
+
+% As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
+% \begin{corollary}
+% For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+% \begin{equation}\label{eq:Vkm1divnormequiv}
+% \|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+% \end{equation}
+% \end{corollary}
 
@@
 Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
-Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
+Based on DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
 \begin{align*}
@@
 \end{align*}
-Employing the norm equivalence \eqref{eq:Vkm1divnormequiv},
+Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence}, %{eq:Vkm1divnormequiv},
 we acquire
@@
 
-In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in arbitrary dimension.
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload the notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
+% For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload the notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
 
@@
 
-Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+\XH{Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+By assumption (A1), all the $(d-1)$-dimensional faces of $K$ are simplices, so we can require the shape function restricted to each face to be a polynomial when defining an $H^1$-conforming virtual element.
+To this end, let the space of shape functions be
+\begin{align*}
+V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_F\in \mathbb P_{k}(F)\;\;\forall~F\in\mathcal F(K),\\    
+&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
+\end{align*}
+where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
+It holds $\mathbb P_k(K)\subseteq V_k(K)$.
 The degrees of freedom are given by
 \begin{align}
-v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
-\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
+v(\delta), & \quad \delta\in\Delta_0(K), \label{eq:cfmvemdof1}\\
+\frac{1}{|e|}(v, \phi_i^e)_e, & \quad e\in\Delta_j(K), i=1,\ldots, \dim\mathbb P_{k-j-1}(e), j=1,\ldots, d-1, \label{eq:cfmvemdof2}\\
 \frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
 \end{align}
-where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
-And the space of shape functions is
-\begin{align*}
-V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
-&\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
-\end{align*}
-where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
-It holds $\mathbb P_k(K)\subseteq V_k(K)$.
+where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.}
+
 % To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
@@
 For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using the DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
-We have the norm equivalence of space $V_k(K)$ (cf. \cite[Lemma 4.7]{ChenHuangWei2022} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$, it holds
+Following the argument in \cite[Lemma 4.7]{ChenHuangWei2022} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017},
+we have the norm equivalence of space $V_k(K)$, that is for $v\in V_k(K)$, it holds
 \begin{equation}\label{eq:cfmVknormequivalence}
-h_K^2|v|_{1,K}^2\lesssim\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2 + \sum_{\delta\in \mathcal V(K)}h_K^2|v(\delta)|^2+\sum_{e\in\mathcal E(K)}h_K\|Q_{k-2}^ev\|_{0,e}^2.
+h_K^2|v|_{1,K}^2\lesssim\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2 + h_K\|v\|_{0,\partial K}^2.
 \end{equation}
@@
 \mathbb{V}_{k,k-2}^{\rm div}(K):=&\{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\} \\
-=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_e\in\mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K)\}.
+=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k}(F)\;\;\forall~F\in\mathcal F(K)\}.
 \end{align*}

### 2023-08-15 stabfreevem.tex
typo
update arXiv verison

@@
 \usepackage[hyperpageref]{backref}
+\usepackage{subfigure}
+\usepackage{array}
 
@@
 \begin{document}
-\title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
+\title[Stabilization-Free VEM]{Virtual Element Methods Without Extrinsic Stabilization}
 \author{Chunyu Chen}%
@@
 
- \thanks{The second author is the corresponding author.
-The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.}
- \thanks{The first and third authors were supported by NSFC (11871413).}
+ \thanks{The second author is the corresponding author. The second author was supported by the National Natural Science Foundation of
+China (NSFC) (Grant No. 12171300), and the Natural Science Foundation of Shanghai
+(Grant No. 21ZR1480500).}
+ \thanks{The first and third authors were supported by the National Natural
+Science Foundation of China (NSFC) (Grant No. 12261131501, 11871413), and the construction of innovative provinces in Hunan Province (Grant No. 2021GK1010).}
 
@@
 \begin{abstract}
-Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions.
+Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
-Optimal error estimates are derived for these stabilization-free virtual element methods.
-Numerical results are provided to verify the convergence rates.
+Optimal error estimates are derived for these VEMs.
+Numerical experiments are provided to test the VEMs without extrinsic stabilization.
 \end{abstract}
 
-\keywords{Virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis}
+\keywords{Virtual element, stabilization, macro finite element, norm equivalence, error analysis}
 
@@
 \section{Introduction}
-
-Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon.
-We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on similar stabilization-free virtual element methods for plane elasticity problem.
-The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
-the analysis is rather elaborate. 
-This motivates us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.
-
-The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
+An additional stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form~\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+% , while the stabilization term also brings about some problems. 
+The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
+$$
+c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
+$$
+for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.
+% The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
+For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization term dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal.
+The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
+and improper choices of the stabilization term will produce useless results.
+Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
+In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.
+
+% Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
+% Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
+% The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}.
+Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
+
+% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
+% the analysis is rather elaborate. 
+% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
+We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, {including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices}, in a unified way.
+The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 \end{enumerate}
+The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
 We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
 inner product $(\cdot, \cdot)_K$. The norm equivalence
-\eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be
+\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
 sufficiently large compared with the virtual element space $V_k(K)$.  In
@@
 hold
-rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
-To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
-Instead, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.
+rather than the norm equivalence \eqref{intro:gradVknormequiv}, then an additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
+To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
+% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
+% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.
 
@@
 space for $k=0$, with some constraints. To ensure the $L^2$ projection
-$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
-for virtual element function $v\in V_k(K)$, we require
+$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
+for virtual element function $v\in V_k(K)$, we require that
 $\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
@@
 is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
-these considerations and the direct decomposition of an $H(\div)$-conforming
-macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
-the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
+these considerations and the direct decomposition of the $H(\div)$-conforming
+macro finite element space $\mathbb{V}_{k}^{\rm div}(K)$, we propose
+the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
 $L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
-a conforming finite element for differential $(d-2)$-form in
+a conforming finite element for the differential $(d-2)$-form in
 \cite{ArnoldFalkWinther2006,Arnold2018}.
@@
 
-By the aid of projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming virtual element method in arbitrary dimension and a stabilization-free conforming virtual element method in two dimensions  for second order elliptic problems.
-Indeed, these stabilization-free virtual element methods can be equivalently recast as
-primal mixed virtual element methods.
-We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free virtual element methods, and derive the optimal error estimates.
-
-The idea on constructing stabilization-free virtual element methods in this paper is simple,
-and can be extended to more virtual element methods and more partial differential equations.
+By the aid of the projector $Q_{K,k}^{\div}$, {we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.}
+Indeed, these VEMs can be equivalently recast as
+primal mixed VEMs.
+We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs without extrinsic stabilization, and derive the optimal error estimates.
+
+Numerical experiments are provided to test the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
+matrix for the VEMs without extrinsic stabilization, which appear competitive with respect to other existing VEMs.
+
+The idea on constructing VEMs without extrinsic stabilization in this paper is simple,
+and can be extended to more VEMs and more partial differential equations.
+Since there is no additional stabilization term, these VEMs will be preferred in the engineering community. More benefits of the VEMs without extrinsic stabilization will be the study of future works.
+By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
+\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for weak Galerkin finite element methods without extrinsic stabilization.
 
@@
 In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed.
-A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}.
-And a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
+A nonconforming VEM without extrinsic stabilization in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM without extrinsic stabilization in arbitrary dimension is devised in Section \ref{sec:stabfreecfmvem}.
 Some numerical results are shown in Section \ref{sec:numericalexamps}.
@@
 polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
-For a banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$, where $\mathbb{K}$ is the set of antisymmetric matrices.
+For a Banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$ being the set of antisymmetric matrices.
 Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
-For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
+Let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of a tensor $\boldsymbol{\tau}$.
 Denote by $\#S$ the number of elements in a finite set $S$.
 
-For $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
-For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
-
-For $d$-dimensional simplex $T$,
-let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of $\boldsymbol x$ corresponding to vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
+Given a $d$-dimensional polytope $K$, {let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
+Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.}
+% let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
+
+Given a $d$-dimensional simplex $T$,
+let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of the point $\boldsymbol x$ corresponding to the vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
 Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$.
@@
 For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
-For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
-On face $F\in\mathcal F_h$, define surface divergence
+For a smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
+On the face $F\in\mathcal F_h$, define the surface divergence
 \[
@@
 \]
-For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.
-
-\subsection{Mesh conditions}
+Define the surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$ for a smooth function $v$.
+
+\subsection{Mesh conditions}\label{sec:meshcondition}
 We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
@@
  \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter.
-
- \item[(A2)] There exists a quasi-uniform simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
+{All the $(d-1)$-dimensional faces of $K$ are simplices.}
+
+ \item[(A2)] There exists a shape-regular simplicial mesh $\mathcal T_h^*$ such that each $K\in \mathcal T_h$ is a union of some simplexes in $\mathcal T_h^*$.
+For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$.
+Assume simplicial partition $\mathcal T_K$ is quasi-uniform, {and all the $(d-1)$-dimensional faces of $K$ are also faces of $\mathcal T_K$.}
 \end{itemize}
@@
 $C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
-which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.
-
-For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$.
-Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively.
-Set
-\[
-\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
-\]
+which may take different values at different appearances. Let $A\eqsim B$ mean $A\lesssim B$ and $B\lesssim A$.
+
+% For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
+% Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. 
+% Set 
+% \[
+% \mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
+% \]
 
@@
 \section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
-
-In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
+In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
+\begin{equation*}%\label{eq:Vkm1divnormequiv}
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation*}
+The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
+the norm equivalence for the virtual element space
+\begin{equation*}%\label{intro:gradVknormequiv} 
+\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
+\end{equation*}
+where $V_k(K)$ is the nonconforming virtual element space in Section \ref{sec:stabfreencfmvem}, and the conforming virtual element space in Section \ref{sec:stabfreecfmvem}.
+Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.
+
 \subsection{$H(\div)$-conforming finite elements}
-For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
-\[
-\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
+For a $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
+\[
+\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
 \]
@@
 (\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
-(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
+(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
 \end{align}
-Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.
-
-We also need the lowest order Raviart-Thomas (RT) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}
-\[
-\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
-\]
-Define $\mathring{\boldsymbol{V}}^{RT}(K):=\boldsymbol{V}^{RT}(K)\cap \boldsymbol{H}_0(\div, K)$.
+for $T\in\mathcal T_K$.
+Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.
+Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.
+
+We also need the lowest order Raviart-Thomas (RT) element space~\cite{RaviartThomas1977,Nedelec1980}
+\[
+\boldsymbol{V}^{\mathrm{RT}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
+\]
+The DoFs are given by
+\[
+(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F,  \quad q\in \mathbb P_{0}(F), F\in\mathcal F(T)
+\]
+for $T\in\mathcal T_K$.
+Define $\mathring{\boldsymbol{V}}^{\mathrm{RT}}(K):=\boldsymbol{V}^{\mathrm{RT}}(K)\cap \boldsymbol{H}_0(\div, K)$.
 
@@
 
-By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have the decomposition
+By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
 \begin{equation}\label{eq:Pkvectordecomp}  
-\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
-\end{equation}
+\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
+\end{equation}
+% {where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
+Recall that \cite[(35)]{Chen;Huang:2020Finite}
+\begin{equation}\label{eq:20230205}
+\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
+\end{equation}
+% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
+% $$
+% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
+% $$
+% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.
 
@@
 \end{equation*}
-we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which implies $\boldsymbol{w}=\boldsymbol{0}$.
+we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which together with \eqref{eq:20230205} implies $\boldsymbol{w}=\boldsymbol{0}$.
 \end{proof}
@@
 \begin{equation}\label{eq:20220324-4}
-\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)-1.
+\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#{\mathcal F(K)}-1.
 \end{equation}
@@
 For each polygon $K\in \mathcal T_h$, 
-define shape function space
-\[
-\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
+define the shape function space
+\[
+{\mathbb{V}_{k-1}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
 \]
@@
 \[
-\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{RT}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
-\]
-Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{RT}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$ for $k\geq2$.
-
-In the following lemma we present a direct sum decomposition of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+{\mathbb{V}_{0}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
+\]
+Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq{\mathbb{V}_{k-1}^{\rm div}(K)}$, ${\mathbb{V}_{0}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and ${\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.
+
+In the following lemma we present a direct sum decomposition of space ${\mathbb{V}_{k-1}^{\rm div}(K)}$.
 
@@
 \begin{equation}\label{eq:Vdivlocaldecomp}
-\boldsymbol{V}_{k-1}^{\rm div}(K)=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
+{\mathbb{V}_{k-1}^{\rm div}(K)}=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
 \end{equation}
@@
 Since $\div:(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\to\mathbb P_{k-2}(K)$ is bijective \cite[Lemma 3.1]{ChenHuang2021divdiv}, we have $\div\skw \boldsymbol{V}_{k}^{d-2}(K)\cap(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)=\{\boldsymbol{0}\}$.
-Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \boldsymbol{V}_{k-1}^{\rm div}(K)$.
-
-On the other side, for $\boldsymbol{\phi}\in \boldsymbol{V}_{k-1}^{\rm div}(K)$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
-$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$.
+Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq {\mathbb{V}_{k-1}^{\rm div}(K)}$.
+
+On the other side, for $\boldsymbol{\phi}\in {\mathbb{V}_{k-1}^{\rm div}(K)}$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
+$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in{\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$.
 Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$.
@@
 
-Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$
+Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space {$\mathbb{V}_{k-1}^{\rm div}(K)$}
 \begin{align}
-    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \label{Vdivdof1}\\
+    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in{\mathcal F(K)}, \label{Vdivdof1}\\
     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
@@
 \begin{lemma}
-The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space {$\mathbb{V}_{k-1}^{\rm div}(K)$}.
 \end{lemma}
@@
 \begin{align*}
-&\quad {k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
-&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\boldsymbol{V}_{k-1}^{\rm div}(K).
+&\quad {k+d-2\choose d-1}\#{\mathcal F(K)}+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
+&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim{\mathbb{V}_{k-1}^{\rm div}(K)}.
 \end{align*}
@@
 
-Assume $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish.
+Assume $\boldsymbol{\phi}\in{\mathbb{V}_{k-1}^{\rm div}(K)}$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish.
 By the vanishing DoF~\eqref{Vdivdof1}, $\boldsymbol{\phi}\in \boldsymbol{H}_0(\div, K)$ and $\div\boldsymbol{\phi}\in L_0^2(K)$.
@@
 
-Next we consider the norm equivalence of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+Next we consider the norm equivalence of space {$\mathbb{V}_{k-1}^{\rm div}(K)$}.
 
 \begin{lemma}\label{lem:Vkm1divnormequivalence}
-For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+For $\boldsymbol{\phi}\in{\mathbb{V}_{k-1}^{\rm div}(K)}$, it holds the norm equivalence
 \begin{equation}\label{eq:Vkm1divnormequivalence}
-\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 \begin{proof}
-By the inverse inequality \cite[Lemma 10]{Huang2020} and the trace inequality \cite[(2.18)]{BrennerSung2018}, we have
-\begin{align*}
-&\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
-&\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
-\end{align*}
-
-Next we focus on the proof of the other side.
+By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
+$$
+h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
+$$ 
+where
+$$
+\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
+$$
+Then we have
+\begin{equation}\label{eq:20230201}  
+h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+\end{equation}
+For $F\in{\mathcal F(K)}$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
+$$
+h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
+$$ 
+This means
+$$
+\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in{\mathcal F(K)}}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$ 
+Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
+$$
+h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+$$
+% \begin{align*}
+% &\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
+% &\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
+% \end{align*}
+
+Next we focus on the proof of the lower bound.
 Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$.
-Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{BDM}(K)$ such that $\boldsymbol{\phi}_1\cdot\boldsymbol{n}|_{\partial K}=\boldsymbol{\phi}\cdot\boldsymbol{n}_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ in the interior of $K$ vanish.
-We have
-\begin{equation}\label{eq:20220324-5}
-\|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
-\end{equation}
-\[
+Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero.
+By the norm equivalence on each simplex $T$ and the vanishing DoFs \eqref{BDMdof2}-\eqref{BDMdof3}, we get
+\begin{align}\label{eq:20220324-5}
+\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in{\mathcal F(K)}}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
+\end{align}
+Due to the vanishing DoF \eqref{BDMdof2}, it holds that $\div\boldsymbol{\phi}_1=Q_0^T(\div\boldsymbol{\phi}_1)$ for $T\in\mathcal T_K$.
+% We have
+% \begin{equation}
+% \|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
+% \end{equation}
+Then apply the integration by parts and the Cauchy-Schwarz inequality to acquire
+\begin{equation}\label{eq:202302011}
 \|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
-\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\quad\forall~T\in\mathcal T_K.
-\]
-Then let $w\in H^1(K)/\mathbb R$ be the solution of 
+\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap{\mathcal F(K)}}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
+\end{equation}
+% for $T\in\mathcal T_K$.
+Now let $w\in H^1(K)\cap L_0^2(K)$ be the solution of 
 \[
@@
 \[
-(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)/\mathbb R.
-\]
-Obviously we have
-\[
-\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\]
-Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}.
-Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)$.
-We have
+(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)\cap L_0^2(K).
+\]
+Obviously we obtain from \eqref{eq:202302011} that
+\begin{equation}\label{eq:202302031}  
+\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation}
+Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
+\begin{equation}\label{eq:20230203}  
+\|I_K^{\div}\boldsymbol{\psi}\|_{0,K} \lesssim \|\boldsymbol{\psi}\|_{0,K}\quad\forall~\boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K),
+\end{equation}
+\[
+\div(I_K^{\div}\boldsymbol{\psi})=\div\boldsymbol{\psi} \quad \textrm{ for } \boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K) \textrm{ satisfying } \div\boldsymbol{\psi}\in V_{k-2}^{L^2}(K).
+\]
+Recall $
+V_{k-2}^{L^2}(K)=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for } T\in\mathcal T_K\}
+$. Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$. We have
 \begin{equation}\label{eq:20220324-6}
-\div\boldsymbol{\phi}_2=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1),
-\end{equation}
+\div\boldsymbol{\phi}_2=-\div(I_K^{\div}(\nabla w))=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1).
+\end{equation}
+It follows from \eqref{eq:20230203} and \eqref{eq:202302031} that
 \begin{equation}\label{eq:20220324-7}
-\|\boldsymbol{\phi}_2\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\end{equation}
-By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$.
+\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation}
+By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$.
 Hence
@@
 \end{align*}
-Finally \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.
+Finally, \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.
 \end{proof}
 
-Let 
-\[
-\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
-\]
-Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
-\begin{align}
-    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
-    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
-    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
-\end{align}
-
-As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
-\begin{corollary}
-For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
-\begin{equation}\label{eq:Vkm1divnormequiv}
-\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-\end{equation}
-\end{corollary}
+% Let 
+% \[
+% \mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): (\boldsymbol{\phi}\cdot\boldsymbol{n})|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
+% \]
+% On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+% Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
+% \begin{align}
+%     (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
+%     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
+%     (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
+% \end{align}
+
+% As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
+% \begin{corollary}
+% For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+% \begin{equation}\label{eq:Vkm1divnormequiv}
+% \|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+% \end{equation}
+% \end{corollary}
 
 For later use, let $Q_{K,k-1}^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
-Introduce discrete spaces
+Introduce the discrete spaces
 \begin{align*}
@@
 
-\section{Stabilization-free nonconforming virtual element method}\label{sec:stabfreencfmvem}
+\section{Nonconforming virtual element method without extrinsic stabilization}\label{sec:stabfreencfmvem}
 
@@
 
-In this section we will develop a stabilization-free nonconforming virtual element method for the second order elliptic problem in arbitrary dimension
+In this section we will develop a nonconforming VEM without extrinsic stabilization for the second order elliptic problem in arbitrary dimension
 \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 \subsection{$H^1$-nonconforming virtual element}
-
-Recall the $H^1$-nonconforming virtual element in \cite{ChenHuang2020ncvem,Huang2020,AyusodeDiosLipnikovManzini2016}.
+Several $H^1$-nonconforming virtual elements have been developed in \cite{AyusodeDiosLipnikovManzini2016,CangianiManziniSutton2017,ChenHuang2020ncvem,Huang2020}.
+In this paper we adopt those in \cite{CangianiManziniSutton2017,ChenHuang2020ncvem}.
 The degrees of freedom are given by
 \begin{align}
-\frac{1}{|F|}(v, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
-\frac{1}{|K|}(v, q)_K & \quad\forall~q\in\mathbb P_{k-2}(K). \label{eq:vemdof2}
+\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), \label{eq:vemdof1}\\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:vemdof2}
 \end{align}
+where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
 
@@
 V_k(K):=\{v\in H^1(K) &: \Delta v\in\mathbb P_{k}(K),\, \partial_nv|_F\in\mathbb P_{k-1}(F)\textrm{ for each face }F\in\mathcal F(K), \\
-&\qquad\qquad\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
-\end{align*}
-where $\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
+&\qquad\qquad\qquad\quad\;\, \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in \mathbb P_{k-2}^{\perp}(K)\},
+\end{align*}
+where %$\mathbb P_{k}(K)/\mathbb P_{k-2}(K)$ 
+$\mathbb P_{k-2}^{\perp}(K)$
+means the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
 Due to \eqref{eq:localproj2dprop1}, it holds $\mathbb P_k(K)\subseteq V_k(K)$.
@@
 \begin{proof}
-Apply the integration by parts to get
+By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
+\[
+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
+\]
+Then apply (A.3) in \cite{ChenHuang2020ncvem} to get
+\[
+h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
+\]
+Employing the integration by parts and the Cauchy-Schwarz inequality, we have
 \[
@@
 \]
-which together with the multiplicative trace inequality yields \eqref{eq:veminverse}.
+which together with the multiplicative trace inequality and the Young's inequality yields \eqref{eq:veminverse}.
 \end{proof}
@@
 \end{align*}
-which combined with the inverse inequality for polynomials implies
+which combined with both $H^1$-$L^2$ and $L^2$ boundary-$L^2$ bulk inverse inequalities for polynomials implies
 \[%\label{eq:VEMnormequivalencePiK}
@@
 \]
-Thanks to the Poincar\'e-Friedrichs inequality \cite[(2.15)]{BrennerSung2018} and \eqref{eq:projlocal2d2},
+Thanks to the Poincar\'e-Friedrichs inequality \cite{Necas1967} %\cite[(2.15)]{BrennerSung2018} 
+and \eqref{eq:projlocal2d2},
 \begin{align*}  
@@
 \subsection{Local inf-sup condition and norm equivalence}
-With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence of space $\nabla V_k(K)$, which is vitally important to design stabilization-free virtual element methods.
+With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design virtual element methods without extrinsic stabilization.
 % Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
@@
 \begin{equation}\label{eq:localdiscreteinfsup}    
-\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
-\end{equation}
-Consequently
+\|\nabla v\|_{0,K}\leq C_e\sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K),
+\end{equation}
+where the constant $C_e\geq1$ is independent of the mesh size $h_K$, but depends on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$.
+Consequently,
 \begin{equation}\label{eq:gradVknormequivalence}  
@@
 Since $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$.
-Apply the integration by parts to get
+Apply the integration by parts and the fact $v=v-Q_{0}^Kv\in L_0^2(K)$ to get
 \begin{align*}
@@
 \|\boldsymbol{\phi}\|_{0,K}&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
-&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
-&\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}^2.    
-\end{align*}
+&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{align*}
+Noting that $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$, we have
+\[
+\|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}.
+\]
 Then we obtain from the norm equivalence \eqref{eq:Vknormequivalence} and the Poincar\'e-Friedrichs  inequality \cite[(2.14)]{BrennerSung2018} that
@@
 V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
-&\qquad\; \textrm{DoF \eqref{eq:vemdof1} is single-valued for $F\in\mathcal F_h$, and vanishes for $F\in \mathcal F_h^{\partial}$}\}.
-\end{align*}
-We have the discrete Poincar\'e inequality (cf. \cite[(4.16)]{ChenHuang2020ncvem})
+&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
+\end{align*}
+We have the discrete Poincar\'e inequality \cite{Brenner2003}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
 \begin{equation}\label{eq:vempoincareineqlty}
-\|v_h\|_0\lesssim |v_h|_{1,h} \quad\forall~v_h\in V_h.
-\end{equation}
+\|v_h\|_0\leq C_p |v_h|_{1,h} \quad\forall~v_h\in V_h,
+\end{equation}
+where the constant $C_p$ is independent of the mesh size.
+Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.
 % Introduce discrete spaces
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method without extrinsic stabilization for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:vem}
@@
 
+\begin{remark}\rm
+The mixed-order HHO method without extrinsic stabilization for the Poisson equation in~\cite{CicuttinErnLemaire2019} is equivalent to find $u_h\in W_h$ such that
+\begin{equation}\label{eq:2023111}    
+(\nabla_h u_h, \nabla_h v_h)=\sum_{K\in\mathcal T_h}(f, Q_{k-2}^Kv_h)_K\quad\forall~v_h\in W_h,
+\end{equation}
+where
+\begin{align*}
+W_h&:=\{v_h\in L^2(\Omega): v_h|_K\in W_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
+&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}
+\end{align*}  
+with $W_k(K):=\{v\in H^1(K) : \Delta v\in\mathbb P_{k-2}(K),\, \partial_nv|_F\in\mathbb P_{k-1}(F)\textrm{ for }F\in\mathcal F(K)\}$.
+However, $(\nabla_h u_h, \nabla_h v_h)$ is not computable, % based on the degrees of freedom \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, 
+and the method \eqref{eq:2023111} is not the standard nonconforming VEM in \cite{AyusodeDiosLipnikovManzini2016}.
+For the practical computation, a basis of $W_k(K)$ has to be solved approximately as shown in \cite[Remark 4.1]{CicuttinErnLemaire2019}, then the approximation of the space $W_h$ is no more a virtual element space.
+\end{remark}
+
 It follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that 
@@
 \begin{equation}\label{eq:ahcoercivity}
-|v_h|_{1,h}^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+|v_h|_{1,h}^2\leq C_e^2 a_h(v_h, v_h)\quad\forall~v_h\in V_h.
 \end{equation}  
@@
 \[
-\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
+\sum_{K\in\mathcal T_h}\|\nabla_h v_h\|_{0,K}^2\leq C_e^2 \sum_{K\in\mathcal T_h}\|Q_{K,k-1}^{\div}\nabla v_h\|_{0,K}^2\leq C_e^2a_h(v_h, v_h)\quad\forall~v_h\in V_h,
 \]
@@
 \begin{theorem}
-The stabilization free virtual element method \eqref{eq:vem} is uni-solvent.
+The VEM \eqref{eq:vem} is well-posed.
 \end{theorem}
@@
 \begin{theorem}\label{thm:errorestimateH1}
-Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:vem}.
-Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$.
-Then
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:vem}. It holds that
+\begin{align}
+\label{eq:errorestimateH1abs}
+|u-u_h|_{1,h}&\leq C_e^2(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\alpha C_p\|u-Q_hu\|_0) \\
+\notag
+&\quad + \inf_{v_h\in V_h}\big((C_e^2+1)|u-v_h|_{1,h}+\alpha C_p\|u-v_h\|_0\big)\\
+\notag
+&\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
+\end{align}
+Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
 \begin{equation}\label{eq:errorestimateH1}
@@
 \begin{proof}
-Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
-\[
-a(u,v_h-u_h)+(f, v_h-u_h)\lesssim h^k|u|_{k+1}|v_h-u_h|_{1,h}.
-\]
-Then 
-\begin{align*}
-&\quad \,a(u,v_h-u_h)-(f, Q_h(v_h-u_h)) \\
-&=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h) \\
-&=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
-&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h}.
-\end{align*}
+Take any $v_h\in V_h$. 
 By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
@@
 &=(Q_{h,k-1}^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
-&\lesssim (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
-\end{align*}
-Summing the last two inequlities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
-\begin{align*}
-|v_h-u_h|_{1,h}^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
-&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h} \\
-&\quad + (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
-\end{align*}
-which implies
-\[
-|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_{h,k-1}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
-\]
+&\leq (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\alpha C_p\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
+\end{align*}
+Apply the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} to get
+\begin{equation*}
+C_e^{-2}|v_h-u_h|_{1,h}^2\leq a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)).
+\end{equation*}
+Combining the last two inequalities yields
+\begin{align*}
+|v_h-u_h|_{1,h}&\leq C_e^2(\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\alpha C_p\|u-Q_hv_h\|_0) \\
+&\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
+\end{align*}
 Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k-1}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
@@
 \]
-By combining the last three inequalities, we obtain
-\[
-|v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|u-v_h\|_{1,h},
-\]
-which together with the triangle inequality yields
-\[
-|u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\inf_{v_h\in V_h}\|u-v_h\|_{1,h}.
-\]
-At last, \eqref{eq:errorestimateH1} follows from the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
+Then we obtain from the last three inequalities that
+\begin{align*}
+|v_h-u_h|_{1,h}&\leq C_e^2\big(\|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_{1,h}+\alpha C_p(\|u-Q_hu\|_0+\|u-v_h\|_0)\big) \\
+&\quad + C_e^2\sup_{w_h\in V_h}\frac{a(u,w_h)-(f, Q_hw_h)}{|w_h|_{1,h}}.
+\end{align*}
+Thus, we acquire \eqref{eq:errorestimateH1abs} from the last inequality and the triangle inequality.
+
+Next we derive estimate \eqref{eq:errorestimateH1}. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
+\[
+a(u, w_h)+(f, w_h)\lesssim h^k|u|_{k+1}|w_h|_{1,h}\quad\forall~w_h\in V_h.
+\]
+Then 
+\begin{align*}
+a(u, w_h)-(f, Q_hw_h) 
+&=a(u, w_h)+(f, w_h)+(f-Q_hf, w_h) \\
+&=a(u, w_h)+(f, w_h)+(f-Q_hf, w_h-Q_h^0w_h) \\
+&\lesssim h^k(|u|_{k+1}+|f|_{k-1})|w_h|_{1,h}.
+\end{align*}
+At last, \eqref{eq:errorestimateH1} follows from \eqref{eq:errorestimateH1abs} and the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
+% Take any $v_h\in V_h$. Recall the consistency error estimate in \cite[Lemma 5.5]{ChenHuang2020ncvem}
+% \[
+% a(u,v_h-u_h)+(f, v_h-u_h)\lesssim h^k|u|_{k+1}|v_h-u_h|_{1,h}.
+% \]
+% Then 
+% \begin{align*}
+% &\quad \,a(u,v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+% &=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h) \\
+% &=a(u,v_h-u_h)+(f, v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
+% &\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h}.
+% \end{align*}
+% By the definitions of $a_h(\cdot, \cdot)$ and $a(\cdot, \cdot)$, it follows from the discrete Poincar\'e inequality \eqref{eq:vempoincareineqlty} that
+% \begin{align*}
+% &\quad a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\\
+% &=(Q_{h,k-1}^{\div}\nabla_h v_h, Q_{h,k-1}^{\div}\nabla_h(v_h-u_h))-(\nabla u, \nabla_h(v_h-u_h))\\
+% &\quad +\alpha(Q_hv_h, Q_h(v_h-u_h))-\alpha(u, v_h-u_h) \\
+% &=(Q_{h,k-1}^{\div}\nabla_h v_h-\nabla u, \nabla_h(v_h-u_h))+\alpha(Q_hv_h-u,v_h-u_h)\\
+% &\lesssim (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h}.
+% \end{align*}
+% Summing the last two inequalities, we get from the coercivity \eqref{eq:ahcoercivity} and \eqref{eq:vem} that
+% \begin{align*}
+% |v_h-u_h|_{1,h}^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+% &\lesssim h^k(|u|_{k+1}+|f|_{k-1})|v_h-u_h|_{1,h} \\
+% &\quad + (\|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0+\|u-Q_hv_h\|_0)|v_h-u_h|_{1,h},
+% \end{align*}
+% which implies
+% \[
+% |v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|\nabla u-Q_{h,k-1}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0.
+% \]
+% Since $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\mathbb{V}_{k-1}^{\rm div}(K)$ for $K\in\mathcal T_h$, we have $Q_{h,k-1}^{\div}(Q_h^{k-1}\nabla u)=Q_h^{k-1}\nabla u$. Hence
+% \begin{align*}    
+% \|\nabla u-Q_{h,k-1}^{\div}\nabla_h v_h\|_0&\leq \|\nabla u-Q_{h,k-1}^{\div}\nabla u\|_0+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0\\
+% &= \|\nabla u-Q_h^{k-1}\nabla u-Q_{h,k-1}^{\div}(\nabla u-Q_h^{k-1}\nabla u)\|_0\\
+% &\quad+\|Q_{h,k-1}^{\div}(\nabla u-\nabla_h v_h)\|_0 \\
+% &\leq \|\nabla u-Q_h^{k-1}\nabla u\|_0+|u-v_h|_{1,h}.
+% \end{align*}
+% Similarly, we have
+% \[
+% \|u-Q_hv_h\|_0\leq \|u-Q_hu\|_0+\|Q_h(u-v_h)\|_0\leq \|u-Q_hu\|_0+\|u-v_h\|_0.
+% \]
+% By combining the last three inequalities, we obtain
+% \[
+% |v_h-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\|u-v_h\|_{1,h},
+% \]
+% which together with the triangle inequality yields
+% \[
+% |u-u_h|_{1,h}\lesssim h^k(|u|_{k+1}+|f|_{k-1})+\inf_{v_h\in V_h}\|u-v_h\|_{1,h}.
+% \]
+% At last, \eqref{eq:errorestimateH1} follows from the approximation of $V_h$ \cite{ChenHuang2020ncvem}.
 \end{proof}
 
-\section{Stabilization-free conforming virtual element method}\label{sec:stabfreecfmvem}
-
-In this section we will develop a stabilization-free conforming virtual element method for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+\section{Conforming virtual element method without extrinsic stabilization}\label{sec:stabfreecfmvem}
+
+In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in arbitrary dimension.
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
+% For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload the notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.
 
@@
 
-Recall the $H^1$-conforming virtual element in \cite{Huang2021,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+{Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+By assumption (A1), all the $(d-1)$-dimensional faces of $K$ are simplices, so we can require the shape function restricted to each face to be a polynomial when defining an $H^1$-conforming virtual element.
+To this end, let the space of shape functions be
+\begin{align*}
+V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_F\in \mathbb P_{k}(F)\;\;\forall~F\in\mathcal F(K),\\    
+&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
+\end{align*}
+where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
+It holds $\mathbb P_k(K)\subseteq V_k(K)$.
 The degrees of freedom are given by
 \begin{align}
-v(\delta) & \quad\forall~\delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
-\frac{1}{|e|}(v, q)_e & \quad\forall~q\in\mathbb P_{k-2}(e), e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
-\frac{1}{|K|}(v, q)_K & \quad\forall~q\in\mathbb P_{k-2}(K). \label{eq:cfmvemdof3}
+v(\delta), & \quad \delta\in\Delta_0(K), \label{eq:cfmvemdof1}\\
+\frac{1}{|e|}(v, \phi_i^e)_e, & \quad e\in\Delta_j(K), i=1,\ldots, \dim\mathbb P_{k-j-1}(e), j=1,\ldots, d-1, \label{eq:cfmvemdof2}\\
+\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
 \end{align}
-And the space of shape functions is
-\begin{align*}
-V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
-&\qquad\qquad\qquad\qquad\qquad\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k}(K)/\mathbb P_{k-2}(K)\},
-\end{align*}
-where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
-It holds $\mathbb P_k(K)\subseteq V_k(K)$.
+where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.}
+
 % To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by
@@
 
-For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using only DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
-We have the norm equivalence of space $V_k(K)$ (cf. \cite[Lemma 4.7]{Huang2021} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}), that is for $v\in V_k(K)$, it holds
+For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ and the $L^2$ projection $Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv$ are computable using the DoFs \eqref{eq:cfmvemdof1}-\eqref{eq:cfmvemdof3}.
+Following the argument in \cite[Lemma 4.7]{ChenHuangWei2022} and \cite{ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017},
+we have the norm equivalence of space $V_k(K)$, that is for $v\in V_k(K)$, it holds
 \begin{equation}\label{eq:cfmVknormequivalence}
-h_K^2|v|_{1,K}^2\lesssim\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2 + \sum_{\delta\in \mathcal V(K)}h_K^2|v(\delta)|^2+\sum_{e\in\mathcal E(K)}h_K\|Q_{k-2}^ev\|_{0,e}^2.
+h_K^2|v|_{1,K}^2\lesssim\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2 + h_K\|v\|_{0,\partial K}^2.
 \end{equation}
@@
 \mathbb{V}_{k,k-2}^{\rm div}(K):=&\{\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\} \\
-=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{BDM}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_e\in\mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K)\}.
+=&\{\boldsymbol{\phi}\in\boldsymbol{V}_{k}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K), \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k}(F)\;\;\forall~F\in\mathcal F(K)\}.
 \end{align*}
@@
 
-Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
+Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method without extrinsic stabilization for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
 \begin{equation}\label{eq:cfmvem}
@@
 \]
-
-It is obvious that 
-\begin{equation}\label{eq:cfmahbounedness}
-a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
-\end{equation}   
-And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
-the coercivity
-\begin{equation}\label{eq:cfmahcoercivity}
-|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
-\end{equation}  
-Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
-
-\begin{remark}\rm
-By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the virtual element method \eqref{eq:cfmvem} can be rewritten as the following primal mixed virtual element method: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
+The VEM \eqref{eq:cfmvem} is uni-solvent.
+
+% It is obvious that 
+% \begin{equation}\label{eq:cfmahbounedness}
+% a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
+% \end{equation}   
+% And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
+% the coercivity
+% \begin{equation}\label{eq:cfmahcoercivity}
+% |v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
+% \end{equation}  
+% Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
+
+% \begin{remark}\rm
+By introducing $\boldsymbol{\phi}_h=Q_{h,k}^{\div}\nabla u_h$, the VEM \eqref{eq:cfmvem} can be rewritten as the following primal mixed VEM: find $\boldsymbol{\phi}_h\in\mathbb{V}_{h,k}^{\rm div}$ and $u_h\in V_h$ such that
 \begin{equation*}
@@
 
-\subsection{Error analysis}
+% \subsection{Error analysis}
+Applying the standard error analysis for VEMs, we have the following error estimate for the VEM \eqref{eq:cfmvem}.
 \begin{theorem}\label{thm:cfmerrorestimateH1}
-Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:cfmvem}.
+Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the VEM \eqref{eq:cfmvem}.
 Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$.
 Then
-\begin{equation}\label{eq:cfmerrorestimateH1}
+\begin{equation*}%\label{eq:cfmerrorestimateH1}
 |u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
-\end{equation}
+\end{equation*}
 \end{theorem}
-\begin{proof}
-Take any $v_h\in V_h$. 
-Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
-\[
-\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
-\]
-\[
-a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
-\]
-Combining the last two inequalities gives
-\[
-a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
-\]
-By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
-\begin{align*}
-|v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
-&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
-% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
-&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
-\end{align*}
-Hence we get from the triangle inequality and the last two inequalities that
-\begin{align*}  
-|u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
-&\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
-\end{align*}
-By the arbitrariness of $v_h\in V_h$, we derive
-\[
-|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
-\]
-At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
-\end{proof}
-
+% \begin{proof}
+% Take any $v_h\in V_h$. 
+% Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
+% \[
+% \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
+% \]
+% \[
+% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
+% \]
+% Combining the last two inequalities gives
+% \[
+% a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
+% \]
+% By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
+% \begin{align*}
+% |v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
+% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
+% % &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
+% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
+% \end{align*}
+% Hence we get from the triangle inequality and the last two inequalities that
+% \begin{align*}  
+% |u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
+% &\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
+% \end{align*}
+% By the arbitrariness of $v_h\in V_h$, we derive
+% \[
+% |u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
+% \]
+% At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
+% \end{proof}
+
+% \begin{figure}[htbp]
+% \centering
+% \begin{minipage}[t]{0.49\linewidth}
+% \centering
+% \includegraphics[width=5cm]{./figures/convex.pdf}
+% %\caption{Numberical result of example with $\mathcal T_0$.}
+% \end{minipage}%
+% \begin{minipage}[t]{0.49\linewidth}
+% \centering
+% \includegraphics[width=5cm]{./figures/nonconvex.pdf}
+% %\caption{[Numberical result of example with $\mathcal T_1$].}
+% \end{minipage}%
+% \centering
+% \caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
+% $\mathcal T_1$(right).}
+% \label{fig:mesh}
+% \end{figure}
+
+\section{Numerical results}\label{sec:numericalexamps}
+In this section, we will numerically test the nonconforming virtual element method \eqref{eq:vem} and the conforming
+virtual element method \eqref{eq:cfmvem}, which are abbreviated as SFNCVEM and SFCVEM respectively.
+For the convenience of narration, we also abbreviate the standard conforming virtual element
+method in \cite{BeiraoBrezziCangianiManziniEtAl2013} and non-conforming virtual element method  in \cite{CangianiManziniSutton2017} as CVEM and NCVEM respectively. 
+We implement all the experiments by using the FEALPy package \cite{fealpy} on a PC with AMD Ryzen
+5 3500U CPU and 64-bit Ubuntu 22.04 operating system.
+Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$.
+
+\subsection{Verification of convergence}
+% \begin{example}\label{ex}
+Consider the second order elliptic problem~\eqref{eq:ellipitc2ndproblem} with $\alpha = 2$.
+The exact solution and source term are given by
+\[
+u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
+\]
+% \end{example}
+
+The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
+$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$ in Fig. \ref{fig:mesh}, respectively. 
+We choose $k = 1, 2, 5$ in both SFNCVEM and SFCVEM.
+The numerical results of the SFNCVEM on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}.
+We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
+And the numerical results of the SFCVEM are presented in Fig.~\ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
+theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
 \begin{figure}[htbp]
+\subfigure[Convex polygon mesh $\mathcal T_0$.]{
+\begin{minipage}[t]{0.425\linewidth}
+\centering
+\includegraphics*[width=4.7cm]{./figures/convex.pdf}
+\end{minipage}}%% 
+\quad \quad
+\subfigure[Non-convex polygon mesh 
+$\mathcal T_1$.]
+{\begin{minipage}[t]{0.425\linewidth}
+\centering
+\includegraphics*[width=4.7cm]{./figures/nonconvex.pdf}
+\end{minipage}}
+\caption{Convex polygon mesh and non-convex polygon mesh.}
+\label{fig:mesh}
+\end{figure}
+\begin{figure}[htbp]
 \centering
@@
 \centering
-\includegraphics[width=5cm]{./figures/nonconvex.pdf}
+\includegraphics[width=5.5cm]{./figures/ncvem_nonconvex.pdf}
 %\caption{[Numberical result of example with $\mathcal T_1$].}
@@
 \centering
-\caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
-$\mathcal T_1$(right).}
-\label{fig:mesh}
+\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
+of nonconforming VEM \eqref{eq:vem} on 
+$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
+\label{fig:rate1}
 \end{figure}
 
-\section{Numerical results}\label{sec:numericalexamps}
-In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
-virtual element method \eqref{eq:cfmvem}.
-The numerical example is implemented by using the FEALPy package \cite{fealpy}
-
-% \begin{example}\label{ex}
-Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$
-on rectangular domain $\Omega = (0, 1)\times(0, 1)$. 
-The exact solution and source term are given by
-\[
-u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
-\]
-% \end{example}
-
-The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
-$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
-In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
-The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ mesh are shown in Figure \ref{fig:rate1}.
-We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
-And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Figure \ref{fig:rate2}.
-Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
-theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
 \begin{figure}[htbp]
@@
 \centering
-\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
+\includegraphics[width=5.5cm]{./figures/cvem_convex.pdf}
 %\caption{Numberical result of example with $\mathcal T_0$.}
@@
 \centering
-\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
+\includegraphics[width=5.5cm]{./figures/cvem_nonconvex.pdf}
 %\caption{[Numberical result of example with $\mathcal T_1$].}
@@
 \centering
-\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
-of nonconforming virtual element method \eqref{eq:vem} on 
-$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
-\label{fig:rate1}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\begin{minipage}[t]{0.49\linewidth}
-\centering
-\includegraphics[width=6cm]{./figures/cvem_convex.pdf}
-%\caption{Numberical result of example with $\mathcal T_0$.}
-\end{minipage}%
-\begin{minipage}[t]{0.49\linewidth}
-\centering
-\includegraphics[width=6cm]{./figures/cvem_nonconvex.pdf}
-%\caption{[Numberical result of example with $\mathcal T_1$].}
-\end{minipage}%
-\centering
 \caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0$ 
-of conforming virtual element method \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
+of conforming VEM \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
 $\mathcal T_1$(right) with $k=1, 2, 5$.}
@@
 
+\subsection{The invertibility of the local stiffness matrices}
+
+We construct three different hexagons shown in Fig.
+\ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods.
+Our numerical results show that, on all the three hexagons, both SFNCVEM and SFCVEM have only one zero eigenvalue.
+In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig.
+\ref{fig:hexagon}, from which we can see that these quantities are comparable for four virtual element methods.
+% \begin{figure}[htbp]
+% \centering
+% \subfigure{\includegraphics[width=1.4in]{./figures/hexagon0.pdf}}
+%     % \caption{Type I:5 tetrahedra}
+% %%
+% \subfigure{\includegraphics[width=1.4in]{./figures/hexagon1.pdf}}
+%      %\caption{Type II: 24 tetrahedra}
+% %%
+% \subfigure{\includegraphics[width=1.2in]{./figures/hexagon2.pdf}}
+%      %\caption{Trirectangular tetrahedron}
+% %%
+% \caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
+%     hexagon with a small perturbation (Middle), 
+% and the square with two hanging nodes (Right)}
+%   \label{fig:hexagon0} %% label for entire figure
+% \end{figure}
+\begin{figure}[htbp]
+\subfigure[Regular hexagon.]{
+\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics*[width=1in]{./figures/hexagon0.pdf}
+\end{minipage}}%% 
+\;\;% \quad
+\subfigure[Quasi-regular hexagon generated by regular
+    hexagon with a small perturbation.]
+{\begin{minipage}[t]{0.3\linewidth}
+\centering
+\includegraphics*[width=1in]{./figures/hexagon1.pdf}
+\end{minipage}}
+\;\;% \quad
+\subfigure[Square with two hanging nodes.]
+{\begin{minipage}[t]{0.35\linewidth}
+\centering
+\includegraphics*[width=0.9in]{./figures/hexagon2.pdf}
+\end{minipage}}
+\caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
+    hexagon with a small perturbation (Middle), 
+and the square with two hanging nodes (Right).}
+\label{fig:hexagon}
+\end{figure}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the regular hexagon.}
+\label{tab:comparison0}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+NCVEM & 975.5693189 & 0.309674737 & 3150.303211 \\ \hline
+CVEM & 1012.488116 & 0.297206358 & 3406.683909 \\ \hline
+SFNCVEM & 992.5956147 & 0.318932029 & 3112.248147 \\ \hline
+SFCVEM & 1011.173331 & 0.298509692 & 3387.405362 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon.}
+\label{tab:comparison1}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+NCVEM   & 935.2883848 & 0.279027715 & 3351.955143 \\ \hline
+CVEM    & 1014.672395 & 0.257370621 & 3942.456177 \\ \hline
+SFNCVEM & 997.4831245 & 0.282126359 & 3535.589964 \\ \hline
+SFCVEM  & 1047.876056 & 0.258970708 &
+4046.311124 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\centering
+\caption{Comparison of eigenvalues and condition numbers on the square with two hanging nodes.}
+\label{tab:comparison2}
+\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
+\hline
+\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
+eigenvalue} & \textbf{Condition number} \\ \hline
+ NCVEM   & 941.8571938&	0.21069027	&4470.340249 \\ \hline
+ CVEM    & 1046.755495&	0.200435123	&5222.4155 \\ \hline
+ SFNCVEM & 986.5963357&	0.212761106	&4637.108513 \\ \hline
+ SFCVEM  & 1061.651989&	0.202074633	&5253.761808 \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Comparison of assembling time}
+The only difference between the standard VEMs and the VEMs without extrinsic stabilization is the
+stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
+four different VEMs in detail by varying the degree $k$ and the mesh size $h$
+respectively. We use the mesh in Fig.~\ref{fig:mesh}(a) for this experiment.
+The results presented in Tables
+\ref{tab:ptime} and \ref{tab:ttime} show that NCVEM, CVEM and SFNCVEM have similar assembling time. 
+However, SFCVEM requires more time due to the projection onto the one-order higher polynomial space.
+\begin{table}[htbp]
+\caption{Time consumed in assembling stiffness matrix of four VEMs with
+ $h=0.2$ and different $k$.}
+\label{tab:ptime}
+\centering
+\begin{tabular}{c|cccc}
+\hline
+$k$ & 2 & 4 & 8 & 10 \\
+\hline
+SFCVEM & 0.053684235 & 0.144996881 & 1.468627453 & 2.603836536 \\
+SFNCVEM & 0.022516727 & 0.065697193 & 0.806378841 & 1.554260015 \\
+CVEM & 0.021185875 & 0.059809923 & 0.600241184 & 1.160929918 \\
+NCVEM & 0.0213027 & 0.061014891 & 0.596506596 & 1.129639149 \\
+\hline
+\end{tabular}
+\end{table}
+\begin{table}[htbp]
+\caption{Time consumed in assembling stiffness matrix of four VEMs with $k = 5$ and different $h$.}
+\label{tab:ttime}
+\centering
+\begin{tabular}{c|cccc}
+\hline
+$h$ &    1	& 0.25 & 0.0625 & 0.03125\\
+\hline
+SFCVEM & 0.039689541 & 0.199015379	& 1.74412179	& 4.75462532\\
+SFNCVEM & 0.018287182 & 0.100006819	& 0.81251812	& 2.465409517\\
+CVEM & 0.018686771 & 0.087426662	& 0.781031132	& 1.983617783\\
+NCVEM & 0.018309593 & 0.096345425	& 0.767129898	& 2.159288645\\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Condition number of the stiffness
+matrix}
+\begin{figure}[htbp]
+\centering
+\subfigure{\includegraphics[width=1in]{./figures/hexagon0.pdf}}
+    % \caption{Type I:5 tetrahedra}
+%%
+\subfigure{\includegraphics[width=1in]{./figures/hexagon3.pdf}}
+     %\caption{Type II: 24 tetrahedra}
+%%
+\subfigure{\includegraphics[width=1in]{./figures/hexagon4.pdf}}
+     %\caption{Trirectangular tetrahedron}
+%%
+\caption{The hexagons $H_0, H_1, H_2$.}
+  \label{fig:collapsehexagon} %% label for entire figure
+\end{figure} 
+We design two experiments to check the condition number of the stiffness
+matrices of the four VEMs.
+
+Firstly, we refer to the ``collapsing polygons'' experiment in
+\cite{Mascotto2018} and consider a sequence of hexagons
+$\{H_i\}_{i=0}^{\infty}$, where the vertices of $H_i$ are given by
+$A_i = (1, 0)$, $B_i = (0.5, a_i)$, $C_i = (-0.5, a)$, $D_i=(-1, 0)$, 
+$E_i = (-0.5, -a_i)$, and $F_i = (0.5, -a_i)$,
+where $a_i = \frac{\sqrt{3}}{2^{i+1}}$. The hexagons $H_0$, $H_1$ and $H_2$ are drawn
+in Fig.~\ref{fig:collapsehexagon}. 
+% We construct the virtual element space on $H_i$ and calculate the condition number
+% of the stiffness matrix of four methods. 
+As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber} for $k=8$ and $k=10$, the condition numbers of stiffness
+matrices of the VEMs without extrinsic stabilization are smaller than those of the standard methods when $i$ is large.
+\begin{figure}[htbp]
+\subfigure[$k = 8$]{
+\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics*[width=2in]{./figures/collapsing_condition_number_8.pdf}
+\end{minipage}}%% 
+\quad \quad
+\subfigure[$k = 10$]
+{\begin{minipage}[t]{0.45\linewidth}
+\centering
+\includegraphics*[width=2in]{./figures/collapsing_condition_number_10.pdf}
+\end{minipage}}
+\caption{The condition number of stiffness matrix of four VEMs on
+$\{H_i\}_{i=0}^{12}$.}
+\label{fig:collapsehexagon_conditionnumber}
+\end{figure}
+
+% \begin{figure}[htbp]
+% \centering
+% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_8.pdf}}
+% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_10.pdf}}
+% \caption{The condition number of stiffness matrix of four VEMs on
+% $\{H_i\}_{i=0}^{12}$, Left : $k = 8$, Right : $k = 10$.}
+%   \label{fig:collapsehexagon_conditionnumber0} %% label for entire figure
+% \end{figure}
+
+Secondly, we do the patch test for the Laplace equation, i.e.
+problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous.
+Take the exact solution $u=1+x+y$.
+%We adopt meshes in Fig.
+\ref{fig:polymesh}.
+% $$
+% \left\{\begin{aligned}
+% -\Delta u & = 0 \quad x \in \Omega\\
+% u & = g \quad x \in \partial \Omega
+% \end{aligned}\right.
+% $$
+% where $\Omega = (0, 1)^2, \ u = g = 1+x+y$. 
+Let $h_x$ and $h_y$ be mesh size in the $x$-direction and
+$y$-direction respectively.
+We examine the behavior of error $\|u - u_h\|_0$ of the four VEMs in the
+following three cases:
+\begin{enumerate}[(1)]
+\item Mesh in Fig.~\ref{fig:mesh}(a): Fix $h_x=h_y=0.2$ but vary $k= 1, 2, \ldots, 10$;
+\item Mesh in Fig.~\ref{fig:mesh}(a): Fix $k=3$ but vary $h_x=h_y=2^{-i}$ for $i=1,\ldots, 5$;
+\item Mesh in Fig.~\ref{fig:polymesh}: Fix $k=3$ and $h_x=0.2$, but vary $h_y=2^{-i}$ for $i=1,\ldots, 8$.
+\end{enumerate}
+\begin{figure}[htbp]
+\centering
+% \subfigure{\includegraphics[width=2in]{./figures/poly_mesh.pdf}}
+\subfigure{\includegraphics[width=2in]{./figures/mesh_hy.pdf}}
+\caption{The mesh of domain $(0, 1)\times(0, 1)$ with
+$h_x=0.2, h_y = 0.03125$.}
+% \caption{The meshes of domain $(0, 1)\times(0, 1)$. Left: $h = 0.1$. Right:
+% $h_x=0.2, h_y = 0.03125$.}
+  \label{fig:polymesh} %% label for entire figure
+\end{figure}
+The errors of the four methods shown in Fig.~\ref{fig:patchtest} are similar. 
+Since the error in the patch test
+grows as the condition number of the stiffness matrix grows, 
+the condition numbers of the stiffness matrix obtained by
+four methods are comparable.
+\begin{figure}[htbp]
+\centering
+\subfigure{\includegraphics[width=1.8in]{./figures/patch_test_p.pdf}}
+%%
+\subfigure{\includegraphics[width=1.8in]{./figures/patch_test_h.pdf}}
+%%
+\subfigure{\includegraphics[width=1.8in]{./figures/patch_test_hy.pdf}}
+\caption{The $L^2$ error of patch test.}
+\label{fig:patchtest} %% label for entire figure
+\end{figure}
+
 \bibliographystyle{abbrv}

### 2023-08-20 stabfreevem_sinum.tex
back to original mesh conditions

--- 2023-08-13 stabfreevem_sinum.tex
@@
 \begin{abstract}
-Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions.
+Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension}.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
@@
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
+We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension},  in a unified way.
 The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
@@
 
-Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+Given a $d$-dimensional polytope $K$, \XH{let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
+Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.}
+% Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. 
 For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
@@
 
-In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in two dimensions.
+In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem}.
+
+\XH{
+We additionally impose the following condition on the mesh $\mathcal T_h$ in this section:
+\begin{itemize}
+ \item[(A3)] All the $(d-1)$-dimensional faces of $K\in \mathcal T_h$ are simplices.
+% , and all the $(d-1)$-dimensional faces of $K$ are also faces of $\mathcal T_K$.
+\end{itemize}
+}
+
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+\XH{Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+By assumption (A3), we can require the shape function restricted to each face to be a polynomial when defining an $H^1$-conforming virtual element.
+To this end, let the space of shape functions be
+\begin{align*}
+V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_F\in \mathbb P_{k}(F)\;\;\forall~F\in\mathcal F(K),\\    
+&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
+\end{align*}
+where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
+It holds $\mathbb P_k(K)\subseteq V_k(K)$.
 The degrees of freedom are given by
 \begin{align}
-v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
-\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
+v(\delta), & \quad \delta\in\Delta_0(K), \label{eq:cfmvemdof1}\\
+\frac{1}{|e|}(v, \phi_i^e)_e, & \quad e\in\Delta_j(K), i=1,\ldots, \dim\mathbb P_{k-j-1}(e), j=1,\ldots, d-1, \label{eq:cfmvemdof2}\\
 \frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
 \end{align}
-where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
-And the space of shape functions is
-\begin{align*}
-V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
-&\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
-\end{align*}
-where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
-It holds $\mathbb P_k(K)\subseteq V_k(K)$.
+where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.}
+
+% Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+% The degrees of freedom are given by
+% \begin{align}
+% v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
+% \frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
+% \frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
+% \end{align}
+% where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
+% And the space of shape functions is
+% \begin{align*}
+% V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
+% &\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
+% \end{align*}
+% where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
+% It holds $\mathbb P_k(K)\subseteq V_k(K)$.
 % To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by

### 2023-09-12 stabfreevem.tex
response to referees

@@
 \begin{abstract}
-Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices.
+Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM and a conforming VEM in arbitrary dimension.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
@@
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, {including a nonconforming VEM and a conforming VEM in arbitrary dimension under the mesh assumption that all the faces of each polytope are simplices}, in a unified way.
+We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM and a conforming VEM in arbitrary dimension,  in a unified way.
 The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
@@
 is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
-these considerations and the direct decomposition of the $H(\div)$-conforming
-macro finite element space $\mathbb{V}_{k}^{\rm div}(K)$, we propose
+these considerations and the direct decomposition of an $H(\div)$-conforming
+macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
 the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
@@
 
-By the aid of the projector $Q_{K,k}^{\div}$, {we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.}
+By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.
 Indeed, these VEMs can be equivalently recast as
@@
 
-Given a $d$-dimensional polytope $K$, {let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
-Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.}
-% let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively.
+Given a $d$-dimensional polytope $K$, let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
+Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.
+% Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. 
 For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.
@@
  \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter.
-{All the $(d-1)$-dimensional faces of $K$ are simplices.}
 
@@
 For polytope $K\in \mathcal T_h$, let $\mathcal T_K$ be the simplicial partition of $K$ induced from $\mathcal T_h^*$.
-Assume simplicial partition $\mathcal T_K$ is quasi-uniform, {and all the $(d-1)$-dimensional faces of $K$ are also faces of $\mathcal T_K$.}
+Assume simplicial partition $\mathcal T_K$ is quasi-uniform.
 \end{itemize}
@@
 % For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. 
-% Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. 
-% Set 
-% \[
-% \mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
-% \]
+Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
+\[
+\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
+\]
 
@@
 \begin{equation}\label{eq:20220324-4}
-\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#{\mathcal F(K)}-1.
+\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)-\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K)={k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)-1.
 \end{equation}
@@
 \[
-{\mathbb{V}_{k-1}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
+\boldsymbol{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\},
 \]
@@
 \[
-{\mathbb{V}_{0}^{\rm div}(K)}:=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
-\]
-Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq{\mathbb{V}_{k-1}^{\rm div}(K)}$, ${\mathbb{V}_{0}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and ${\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.
-
-In the following lemma we present a direct sum decomposition of space ${\mathbb{V}_{k-1}^{\rm div}(K)}$.
+\boldsymbol{V}_{0}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\}.
+\]
+Apparently $\mathbb P_{k-1}(K;\mathbb R^d)\subseteq\boldsymbol{V}_{k-1}^{\rm div}(K)$, $\boldsymbol{V}_{0}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_0^{\mathrm{RT}}(K)\cap\ker(\div)$, and $\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$ for $k\geq2$.
+
+In the following lemma we present a direct sum decomposition of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
 
@@
 \begin{equation}\label{eq:Vdivlocaldecomp}
-{\mathbb{V}_{k-1}^{\rm div}(K)}=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
+\boldsymbol{V}_{k-1}^{\rm div}(K)=\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus (\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{\max\{k-2,0\}}(K).
 \end{equation}
@@
 \begin{equation*}
-\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\mathbb{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
+\boldsymbol{V}_{k}^{d-2}(K)\xrightarrow{\div\skw}\boldsymbol{V}_{k-1}^{\rm div}(K)\xrightarrow{\div} \mathbb P_{\max\{k-2,0\}}(K)\to0    
 \end{equation*}
@@
 Since $\div:(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\to\mathbb P_{k-2}(K)$ is bijective \cite[Lemma 3.1]{ChenHuang2021divdiv}, we have $\div\skw \boldsymbol{V}_{k}^{d-2}(K)\cap(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)=\{\boldsymbol{0}\}$.
-Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq {\mathbb{V}_{k-1}^{\rm div}(K)}$.
-
-On the other side, for $\boldsymbol{\phi}\in {\mathbb{V}_{k-1}^{\rm div}(K)}$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
-$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in{\mathbb{V}_{k-1}^{\rm div}(K)}\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$.
+Clearly $\div\skw \boldsymbol{V}_{k}^{d-2}(K) \oplus(\boldsymbol{x}-\boldsymbol{x}_K)\mathbb P_{k-2}(K)\subseteq \boldsymbol{V}_{k-1}^{\rm div}(K)$.
+
+On the other side, for $\boldsymbol{\phi}\in \boldsymbol{V}_{k-1}^{\rm div}(K)$, by $\div\boldsymbol{\phi}\in \mathbb P_{k-2}(K)$, there exists a $q\in\mathbb P_{k-2}(K)$ such that $\div((\boldsymbol{x}-\boldsymbol{x}_K)q)=\div\boldsymbol{\phi}$, i.e.
+$\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\boldsymbol{V}_{k-1}^{\rm div}(K)\cap\ker(\div)=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$.
 Thanks to finite element complex \eqref{eq:localBDMfemderhamcomplex}, $\boldsymbol{\phi}-(\boldsymbol{x}-\boldsymbol{x}_K)q\in\div\skw \boldsymbol{V}_{k}^{d-2}(K)$.
@@
 
-Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space {$\mathbb{V}_{k-1}^{\rm div}(K)$}
+Based on the space decomposition \eqref{eq:Vdivlocaldecomp} and the degrees of freedom of BDM element, we propose the following DoFs for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$
 \begin{align}
-    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in{\mathcal F(K)}, \label{Vdivdof1}\\
+    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F^{\partial}(\mathcal T_K), \label{Vdivdof1}\\
     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vdivdof2} \\
@@
 \begin{lemma}
-The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space {$\mathbb{V}_{k-1}^{\rm div}(K)$}.
+The set of DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} is uni-solvent for space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
 \end{lemma}
@@
 \begin{align*}
-&\quad {k+d-2\choose d-1}\#{\mathcal F(K)}+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
-&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim{\mathbb{V}_{k-1}^{\rm div}(K)}.
+&\quad {k+d-2\choose d-1}\#\mathcal F^{\partial}(\mathcal T_K)+\dim\mathbb P_{\max\{k-2,0\}}(K)-1+\dim\div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K) \\
+&=\dim\div\skw\boldsymbol{V}_{k}^{d-2}(K)+\dim\mathbb P_{\max\{k-2,0\}}(K)=\dim\boldsymbol{V}_{k-1}^{\rm div}(K).
 \end{align*}
@@
 
-Assume $\boldsymbol{\phi}\in{\mathbb{V}_{k-1}^{\rm div}(K)}$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish.
+Assume $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$ and all the DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} vanish.
 By the vanishing DoF~\eqref{Vdivdof1}, $\boldsymbol{\phi}\in \boldsymbol{H}_0(\div, K)$ and $\div\boldsymbol{\phi}\in L_0^2(K)$.
@@
 
-Next we consider the norm equivalence of space {$\mathbb{V}_{k-1}^{\rm div}(K)$}.
+Next we consider the norm equivalence of space $\boldsymbol{V}_{k-1}^{\rm div}(K)$.
 
 \begin{lemma}\label{lem:Vkm1divnormequivalence}
-For $\boldsymbol{\phi}\in{\mathbb{V}_{k-1}^{\rm div}(K)}$, it holds the norm equivalence
+For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
 \begin{equation}\label{eq:Vkm1divnormequivalence}
-\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 \end{equation}
-For $F\in{\mathcal F(K)}$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
+For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
 $$
@@
 $$
-\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in{\mathcal F(K)}}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
 $$ 
@@
 $$
-h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
+h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
 $$
@@
 \begin{align}\label{eq:20220324-5}
-\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in{\mathcal F(K)}}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
+\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
 \end{align}
@@
 \|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
-\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap{\mathcal F(K)}}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
+\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
 \end{equation}
@@
 \begin{equation}\label{eq:202302031}  
-\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 \begin{equation}\label{eq:20220324-7}
-\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in{\mathcal F(K)}}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
 \end{equation}
@@
 
-% Let 
-% \[
-% \mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): (\boldsymbol{\phi}\cdot\boldsymbol{n})|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
-% \]
-% On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
-% Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
-% \begin{align}
-%     (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
-%     (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
-%     (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
-% \end{align}
-
-% As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
-% \begin{corollary}
-% For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
-% \begin{equation}\label{eq:Vkm1divnormequiv}
-% \|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
-% \end{equation}
-% \end{corollary}
+Let 
+\[
+\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): (\boldsymbol{\phi}\cdot\boldsymbol{n})|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
+\]
+On each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.
+Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
+\begin{align}
+    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
+    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
+    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
+\end{align}
+
+As an immediate result of Lemma~\ref{lem:Vkm1divnormequivalence}, we get the following norm equivalence of space $\mathbb{V}_{k-1}^{\rm div}(K)$.
+\begin{corollary}
+For $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
+\begin{equation}\label{eq:Vkm1divnormequiv}
+\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
+\end{equation}
+\end{corollary}
 
@@
 Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
-Based on DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
+Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
 \begin{align*}
@@
 \end{align*}
-Employing the norm equivalence \eqref{eq:Vkm1divnormequivalence}, %{eq:Vkm1divnormequiv},
+Employing the norm equivalence \eqref{eq:Vkm1divnormequiv},
 we acquire
@@
 
-In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem} in arbitrary dimension.
+In this section we will develop a conforming VEM without extrinsic stabilization for the second order elliptic problem \eqref{eq:ellipitc2ndproblem}.
+
+We additionally impose the following condition on the mesh $\mathcal T_h$ in this section:
+\begin{itemize}
+ \item[(A3)] All the $(d-1)$-dimensional faces of $K\in \mathcal T_h$ are simplices.
+% , and all the $(d-1)$-dimensional faces of $K$ are also faces of $\mathcal T_K$.
+\end{itemize}
+
 % \begin{equation}\label{eq:ellipitc2ndproblem}
@@
 
-{Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
-By assumption (A1), all the $(d-1)$-dimensional faces of $K$ are simplices, so we can require the shape function restricted to each face to be a polynomial when defining an $H^1$-conforming virtual element.
+Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+By assumption (A3), we can require the shape function restricted to each face to be a polynomial when defining an $H^1$-conforming virtual element.
 To this end, let the space of shape functions be
@@
 \end{align}
-where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.}
-
+where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.
+
+% Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+% The degrees of freedom are given by
+% \begin{align}
+% v(\delta), & \quad \delta\in\mathcal V(K), \label{eq:cfmvemdof1}\\
+% \frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \label{eq:cfmvemdof2}\\
+% \frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K), \label{eq:cfmvemdof3}
+% \end{align}
+% where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.
+% And the space of shape functions is
+% \begin{align*}
+% V_k(K)&:=\big\{ v\in H^1(K): \Delta v\in \mathbb P_{k}(K),  v|_{\partial K}\in H^1(\partial K),  v|_e\in \mathbb P_{k}(e)\;\;\forall~e\in\mathcal E(K),\\    
+% &\qquad\qquad\qquad\qquad\qquad\qquad\quad\;\;\; \textrm{and } (v-\Pi_k^Kv, q)_K=0\quad\forall~q\in\mathbb P_{k-2}^{\perp}(K)\},
+% \end{align*}
+% where $\Pi_k^K$ is defined by \eqref{eq:projlocal2d1}-\eqref{eq:projlocal2d2}.
+% It holds $\mathbb P_k(K)\subseteq V_k(K)$.
 % To define the space of shape functions $V_k(K)$, we introduce a local $H^1$-projector $\Pi_k^K: H^1(K)\to\mathbb P_k(K)$: given $v\in H^1(K)$, let $\Pi_k^Kv\in\mathbb P_k(K)$ be determined by

### 2023-09-12 stabfreevem_sinum.tex
response to referees

@@
 Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
-In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.
+In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and \XH{might} reduce its practicality.
 
@@
 and can be extended to more VEMs and more partial differential equations.
-Since there is no additional stabilization term, these VEMs will be preferred in the engineering community. More benefits of the VEMs without extrinsic stabilization will be the study of future works.
+Since there is no additional stabilization term, these VEMs \XH{might be of interest for} the engineering community.
+More benefits of the VEMs without extrinsic stabilization will be the study of future works.
 By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 

### 2023-09-19 stabfreevem_sinum.tex
remove \XH

--- 2023-08-20 stabfreevem_sinum.tex
@@
 \begin{abstract}
-Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension}.
+Virtual element methods (VEMs) without extrinsic stabilization in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM and a conforming VEM in arbitrary dimension.
 The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
@@
 Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.
-In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and will reduce its practicality.
+In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and might reduce its practicality.
 
@@
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, \XH{including a nonconforming VEM and a conforming VEM in arbitrary dimension},  in a unified way.
+We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM and a conforming VEM in arbitrary dimension,  in a unified way.
 The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
@@
 
-By the aid of the projector $Q_{K,k}^{\div}$, \XH{we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.}
+By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM and a conforming VEM without extrinsic stabilization for second order elliptic problems in arbitrary dimension.
 Indeed, these VEMs can be equivalently recast as
@@
 and can be extended to more VEMs and more partial differential equations.
-Since there is no additional stabilization term, these VEMs will be preferred in the engineering community. More benefits of the VEMs without extrinsic stabilization will be the study of future works.
+Since there is no additional stabilization term, these VEMs might be of interest for the engineering community.
+More benefits of the VEMs without extrinsic stabilization will be the study of future works.
 By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
@@
 
-Given a $d$-dimensional polytope $K$, \XH{let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
-Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.}
+Given a $d$-dimensional polytope $K$, let $\Delta_j(K)$ be the set of all $j$-dimensional faces of $K$ for $j=0,1,\ldots, d-1$.
+Set $\mathcal{F}(K):=\Delta_{d-1}(K)$ and $\mathcal{E}(K):=\Delta_{d-2}(K)$.
 % Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. 
@@
 
-\XH{
 We additionally impose the following condition on the mesh $\mathcal T_h$ in this section:
@@
 \end{itemize}
-}
 
@@
 
-\XH{Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
+Recall the $H^1$-conforming virtual element in \cite{ChenHuangWei2022,AhmadAlsaediBrezziMariniEtAl2013,BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
 By assumption (A3), we can require the shape function restricted to each face to be a polynomial when defining an $H^1$-conforming virtual element.
@@
 \end{align}
-where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.}
+where $\{\phi_i^e\}_{i=1}^{\dim\mathbb P_{k-j-1}(e)}$ is a basis of space $\mathbb P_{k-j-1}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of space $\mathbb P_{k-2}(K)$.
 

### 2023-09-21 stabfreevem.tex
add refs on stab-free VEMs

@@
 
+A linear VEM without extrinsic stabilization, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
+Numerical examples in \cite{BerroneBorioMarcon2022} show that the VEM in \cite{BerroneBorioMarcon2021} outperforms the standard one in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
+% The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. 
+% Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. 
+The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct VEMs without extrinsic stabilization in higher dimensions, and
+the analysis is rather elaborate. 
+This motivates us to construct VEMs without extrinsic stabilization in arbitrary dimension and arbitrary degree of polynomial in a unified way.
+
 % The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
@@
 % This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM and a conforming VEM in arbitrary dimension,  in a unified way.
+% We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM and a conforming VEM in arbitrary dimension,  in a unified way.
+
 The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that

### 2023-09-21 stabfreevem_sinum.tex
add refs on stab-free VEMs

@@
 
-% Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
-% Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
+\XH{A linear VEM without extrinsic stabilization, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
+Numerical examples in \cite{BerroneBorioMarcon2022} show that the VEM in \cite{BerroneBorioMarcon2021} outperforms the standard one in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
 % The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. 
-Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
-
-% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
-% the analysis is rather elaborate. 
-% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
-We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM and a conforming VEM in arbitrary dimension,  in a unified way.
-The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
+% Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. 
+The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct VEMs without extrinsic stabilization in higher dimensions, and
+the analysis is rather elaborate. 
+This motivates us to construct VEMs without extrinsic stabilization in arbitrary dimension and arbitrary degree of polynomial in a unified way.}
+
+% We intend to construct VEMs without extrinsic stabilization in arbitrary degree of polynomial, including a nonconforming VEM and a conforming VEM in arbitrary dimension,  in a unified way.
+
+The key to construct VEMs without extrinsic stabilization is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto $\mathbb{V}(K)$ such that
 \begin{enumerate}[(C1)]
@@
 \end{pmatrix}$. Hence
-\[
+$
 2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=2{\rm det}(H)\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}),
-\]
+$
 which ends the proof.
@@
 On the other side, assume $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$. Express $\boldsymbol{\tau}$ as 
-\[
+$
 \boldsymbol{\tau}=\sum_{1\leq i<j\leq d}p_{ij}\boldsymbol{N}_{ij},
-\]
+$
 where $p_{ij}=\boldsymbol{n}_i^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_j\in\mathbb P_{k}(T)$.
@@
 By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
-$$
+it holds that $
 h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
-$$ 
+$ 
 where

### 2023-09-22 stabfreevem_sinum.tex
add XuZhang's ref on stab-free VEM on triangles

@@
 
-\XH{A linear VEM without extrinsic stabilization, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
+A linear VEM without extrinsic stabilization, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon.
 Numerical examples in \cite{BerroneBorioMarcon2022} show that the VEM in \cite{BerroneBorioMarcon2021} outperforms the standard one in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
@@
 the analysis is rather elaborate. 
-This motivates us to construct VEMs without extrinsic stabilization in arbitrary dimension and arbitrary degree of polynomial in a unified way.}
+This motivates us to construct VEMs without extrinsic stabilization in arbitrary dimension and arbitrary degree of polynomial in a unified way.
 
@@
 More benefits of the VEMs without extrinsic stabilization will be the study of future works.
-By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
+By the way, we refer to \cite{XuZhang2023} for a VEM without extrinsic stabilization on triangular meshes, \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
 \cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for weak Galerkin finite element methods without extrinsic stabilization.

### 2023-09-27 ex_shared.tex
update

@@
 
-\author{Chunyu Chen\thanks{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China
+\author{Chunyu Chen\thanks{
+    School of Mathematics and Computational Science, Xiangtan University; National
+    Center of Applied Mathematics in Hunan, Hunan Key Laboratory for Computation
+    and Simulation in Science and Engineering Xiangtan 411105, China
   (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).}

### 2023-09-27 ex_shared.tex
update

--- 2023-08-13 ex_shared.tex
@@
 
-\author{Chunyu Chen\thanks{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China
-  (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).}
-\and Xuehai Huang\thanks{Corresponding author. School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China (\email{huang.xuehai@sufe.edu.cn}).}
+\author{Chunyu Chen
+  \thanks{
+    School of Mathematics and Computational Science, Xiangtan University;
+    National Center of  Applied Mathematics in Hunan; Hunan Key Laboratory for
+    Computation and Simulation in Science and Engineering, Xiangtan 411105, China
+    (\email{202131510114@smail.xtu.edu.cn}, \email{weihuayi@xtu.edu.cn}).
+  }
+  \and Xuehai Huang
+  \thanks{
+    Corresponding author. School of Mathematics, Shanghai University of Finance 
+    and Economics, Shanghai 200433, China
+    (\email{huang.xuehai@sufe.edu.cn}).
+  }
   \and Huayi Wei\footnotemark[2]
